### 2019-07-14 main.tex
Initial Overleaf Import

\documentclass[a4paper,11pt]{article}
 \providecommand{\tightlist}{%
     \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{graphicx}
\usepackage{jheppub} 
\usepackage{comment} 
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{slashed}
\usepackage{pgfplots}
\usepackage[T1]{fontenc}
\usepackage{fontspec}
\usepackage{booktabs, longtable}
\bibliographystyle{JHEP.bst}

\newcommand{\Shufang}[1]{{\bf\color{Maroon}  #1}}
\newcommand{\Adarsh}[1]{{\bf\color{RoyalBlue} AP: #1}}
\newcommand{\ap}[1]{\textcolor{RoyalBlue}{#1}}
\renewcommand{\H}{\widetilde{H}^0}
\renewcommand{\B}{\widetilde{B}^0}
\newcommand{\N}{\widetilde{\chi}^0}
\newcommand{\image}[2]{\parbox{#1\textwidth}{\includegraphics[width=#1\textwidth]{images/#2.pdf}}}
\newcommand{\met}{{\slashed{E}_T}}

\title{Higgs Assisted Razor Search for Higgsinos at 100 TeV}
\author[a]{Adarsh Pyarelal}
\author[b]{and Shufang Su}
\affiliation[a]{School of Information, University of Arizona, Tucson, AZ 85718 , USA}
\affiliation[b]{Department of Physics, University of Arizona, Tucson, AZ 85718, USA}

% e-mail addresses: one for each author, in the same order as the authors
\emailAdd{adarsh@email.arizona.edu}
\emailAdd{shufang@email.arizona.edu}

\abstract{% 
  A 100 TeV proton-proton collider will be an extremely effective 
  way to probe the electroweak sector of the Minimal Supersymmetric 
  Standard Model (MSSM). In this paper, we describe a search strategy  
  for discovering pair-produced Higgsino-like NLSPs  at a 100 TeV 
  hadron collider that decay to Bino-like LSPs via intermediate Z and 
  SM Higgs bosons that in turn decay to a pair of leptons and a pair of 
  $b$-quarks respectively: $\N_{2,3}\N_{3,2}
  \rightarrow (Z\N)(h\N)\rightarrow 
  bbll+\N\N$. In addition, we examine 
  the potential for machine learning techniques to boost the power of 
  our searches. Using this analysis, Higgsinos up to 1.3 TeV can be 
  discovered for Binos  up to 0.9 TeV using 3000 fb$^{-1}$ of data,  
  Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
  to 1.3 TeV at 95\% C.L. \\

  \noindent \Shufang{Abstract need to be more detailed.  Let's worry about this after we
  get the draft done.   } \\
}

\begin{document} 
\maketitle
\flushbottom

\section{Introduction}

The existence of dark matter provides unambiguous evidence of new 
physics beyond the Standard Model (SM) of particle physics. Indeed, 
given that there is far more dark matter in the Universe than there 
is baryonic matter, determining its precise nature is one of the most 
exciting challenges in particle physics today.  One promising group 
of candidate for dark matter is the class of stable particles known as 
weakly interacting massive particles (WIMPs). These particles arise 
naturally in many extensions of the SM that are motivated by the need to
stabilize the electroweak scale. One of the most studied extensions
to the SM is the Minimal Supersymmetric Standard Model
(MSSM), which predicts a `supersymmetric partner', or \emph{superpartner}, 
for each SM particle\footnote{For a detailed review of the MSSM, see 
Ref. \citep{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the 
lightest supersymmetric partner (LSP) is predicted to be absolutely 
stable, making it a good candidate for dark matter. The identity of 
the LSP is determined by the mass hierarchy of the superpartners, 
which in turn depends on how supersymmetry is broken.
However, taking into account experimental constraints and phenomenological 
considerations, the lightest of the  MSSM particles known as the 
neutralinos emerges as the most attractive candidate for the LSP \citep{Bertone:2004pz}.

% Why go beyond the MSSM?
Though a natural MSSM spectrum has the potential to tame the hierarchy
problem, it is under siege from recent data from the Large Hadron
Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
A compelling alternative scenario comes in the form of
split supersymmetry (split SUSY) \citep{Wells:2003tf,
ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
superpartners are the fermionic ones, on the
scale of 1-10 TeV, while the scalar superpartners can be much heavier,
on the scale of 100 - 1000 TeV. In exchange for accepting some level of
fine-tuning, we obtain numerous benefits, including the suppression of
flavor-changing neutral currents and greater compatibility with data
from CP-violation experiments.  The low lying 
fermionic superpartners consist of neutralinos and charginos (collectively known as Electroweakinos), and gluinos. The current LHC search limits on gluinos are already around xxx TeV~\cite{}.  The limits on Electroweakinos, howeer, are still relatively weak: around xxx $-$ xxx GeV~\cite{}, depending on the decay modes of the parent electroweakinos.  \Shufang{add ref for gluno limit and electroweakino limits.  Fill in the number.} In this paper, we will focus on the discovery potential of the neutralinos and charginos at the 100 TeV $pp$ collider.

% Point to review papers for enumeration of studies
The decay patterns of the Electroweakinos (Winos, Binos, and Higgsinos)
depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
roughly determine the masses of the Bino, Winos, and Higgsinos, respectively.
In this paper, we consider the Higgsino NLSP and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
One of the motivations for studying Higgsinos is that the parameter $\mu$ 
that governs its mass plays an important role in electroweak symmetry breaking 
\citep{Acharya:2014pua}. Finding Higgsinos has traditionally been more challenging 
than finding Winos, due to their lower production rate. This, however, can 
be remedied by the increased  production cross sections and luminosities 
at a 100 TeV collider.

Since the Bino is the only supersymmetric particle lighter than the Higgsino in the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%. 
Search for Higgsinos with intermediate gauge boson and  multi-lepton final states have been studied in Ref.~\cite{Gori:2014oua}. \Shufang{Add more details for that study.  Which channel, search resutls, etc.  This would be our comparison for our analyses.}  In this paper we attempt to exploit the relatively high branching ratio of 
the SM Higgs boson to \emph{b} quarks, and study the decay mode $\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.

% Why a 100 TeV collider?
A 100 TeV collider would open up an immense number of physics
opportunities not afforded to a 14 TeV collider, including exploring the
most interesting regions of the split SUSY parameter space
\citep{Arkani-Hamed:2015vfh}.
% Status of 100 TeV planning
Such a collider would be a natural next step after the LHC, and is being
actively discussed in the particle physics community, with two major
proposals being the FCC-hh by CERN \citep{FCC-hh}, and the SppC  
in China \citep{CEPC}.  As the next energy frontier machine, it is of 
crucial importance to fully explore the physics potential of a 100 TeV $pp$
collider, especially for new particles that are either too heavy or too rare 
to be produced at the LHC~\citep{Arkani-Hamed:2015vfh,Contino:2016spe,Golling:2016gvc,Mangano:2016jyj}.
In particular, studies have already been performed on the prospects of
discovering neutralino dark matter for compressed \cite{Low:2014cba, diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus}
and well-separated \cite{Gori:2014oua,Acharya:2014pua}
neutralino spectra.

We use razor variables~\citep{Rogan:2010kb} in our study, which were originally designed
for searches involving two heavy, mass-degenerate pair-produced
particles, each of which decays into a visible and invisible set of
particles. This topology matches that of our search channel, making this
set of variables a natural choice for our analysis.

At a 100 TeV collider, the backgrounds are going to be even larger than
at the LHC.  An ancillary goal of this paper is to investigate the
potential for machine learning (ML) techniques to augment our analysis.
With the advent of more powerful computers and simultaneous advances in
the field of statistical learning in recent years, the usage of ML is
rising in experimental particle physics - in fact, the discovery of the
SM Higgs boson in 2012 was done with the help of neural networks
\citep{Aad:2012tfa} and boosted decision trees (BDT)
\citep{Chatrchyan:2012xdj}.

The rest of the paper is structured as follows. In Sec.~\ref{sec:model}, we describe our model and search channel in more
detail, and list the existing experimental constraints on it. In Sec.~\ref{sec:analysis}, we describe our analysis strategies 
for both traditional cut-and-count analyses and analyses
performed using BDT. In Sec.~\ref{sec:results},
we present the results of our analyses, i.e. the expected discovery and exclusion
reaches. Finally, we conclude with the implications in Sec.~\ref{sec:conclusion}.

\section{The neutralino sector of the MSSM}
\label{sec:model}

The neutralino sector of MSSM consists of four mass eigenstates
($\N_1,\N_2,\N_3,\N_4$), which
are mixtures of the Bino, Wino, and two neutral Higgsinos: 
($\B,\widetilde{W}^0,\H_u,\H_d$). In the basis of these gauge eigenstates, the mass
matrix of the neutralinos can be written as

\newcommand{\cb}{ c_\beta}
\newcommand{\cw}{ c_W}
\newcommand{\sinb}{ s_\beta}
\newcommand{\sw}{ s_W}
\newcommand{\mz}{ m_Z}

\[\mathbf{M}_{\widetilde{N}}=
\begin{pmatrix}
  M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
  0 & M_2 & \cb\cw\mz & \sinb\cw\mz \\
  -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
  \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
\end{pmatrix},\]
\Shufang{Check.  I think this matrix goes with ($\B,\widetilde{W}^0,\H_d,\H_u$).}
\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$ for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the
vacuum expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm GeV})^2$. The parameters $M_1$, $M_2$,
and $\mu$ are the mass parameters of Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as $\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.

In the limit of $\mz \ll |\mu\pm M_1|, |\mu\pm M_2|,$ the mass eigenstates
are, to good approximation, a nearly pure Bino, $\B$, with mass $M_1$,
a nearly pure Wino, $\widetilde{W}^0$, with mass $M_2$, and nearly pure Higgsinos
$\H_{1,2} = (\H_u \pm \H_d)/\sqrt{2}$, with mass
$|\mu|$.

The optimal search strategy for finding Electroweakinos is highly dependent on
the their mass spectrums \citep{Han:2013kza}.   Phenomenological collider studies on finding
Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
\Shufang{Say a few words about typical search strategy there.}.
Well-separated spectra have been studied in \citep{Gori:2014oua,
Acharya:2014pua} using
multi-lepton channels, of the form 
\begin{equation}
pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
\widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2l/3l +  
\met,
\end{equation}
\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
$\widetilde{\chi}_1^0$ is the lightest neutralino. These searches work well since
the large mass difference between the Electroweakinos can lead to energetic
leptons that can be easily identified. Among the multi-lepton searches for
Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$ have the best reach, due to the relatively high production cross-section of
chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
and QCD backgrounds obtained by requiring three leptons.   The cross sections for trilepton process can be find in Table~\ref{tab:xsections}. Multilepton searches
with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
due to the lower pair-production cross-section of neutral Higgsinos, combined
with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
multilepton searches, the channel with \emph{Zh} (originally suggested in
\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
competitor to the \emph{WZ} channel.

\begin{table}
  \centering
  \begin{tabular}{l|rr}
    \toprule
    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{2}$ & $\N_2\N_3$\\
    \midrule
    Pair production cross section & 60 fb & 16 fb\\
    Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
    Applying \emph{BR}$(W\rightarrow l\nu)$, \emph{BR}$(Z\rightarrow ll)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
    \bottomrule
  \end{tabular}
  \caption{Comparison of cross-sections for
    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{2})$ and
    $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
    TeV \emph{pp} collider. The pair-production cross sections are taken from
    \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
    evaluated in the limit where the Goldstone equivalence theorem applies, so
    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_{1}^0)\approx$
    BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_1^0)\approx 50\% $,
    and the branching ratios to the SM final states are taken from
    \citep{Olive:2016xmw}.  \Shufang{Specify M1 as well and use the actual Br.} \Shufang{rewrite the entry.  Why chi2pm? Should not it be chi1pm?}}
  \label{tab:xsections}
\end{table}

For pair produced Higgsinos $\tilde\chi_2^0\tilde\chi_3^0$ in a scenario with
decoupled Winos and  sfermions, the \emph{Zh} mode has the greatest
branching ratio.  After multiplying all the branching fractions, the signal cross
sections of

\begin{align}
pp\rightarrow \widetilde{\chi}_{2}^{0}\widetilde{\chi}_{3}^{0}\rightarrow
(Z\widetilde{\chi}_1^{0})(h\widetilde{\chi}_1^{0})\rightarrow
bb\ell\ell \chi_1^0\chi_1^0.
\end{align}
become comparable  to trilepton processes, as shown in    table \ref{tab:xsections}.    The signal contains two
\emph{b}-jets, two same flavor, opposite sign leptons, and missing transverse
energy. The main backgrounds for this process are: $t\overline{t}$, \emph{tbW} with
the $b$ and $W$ not coming from a \emph{t}, and \emph{bbWW} with no intermediate
$s$-channel top quarks.

\begin{comment}
\begin{figure}%
  \centering
  \image{0.21}{signal}
  \image{0.21}{tt}
  \image{0.27}{tbW}
  \image{0.27}{bbWW}
  \caption{From left to right, the representative Feynman diagrams of the signal
    process, the dominant \emph{tt} background, \emph{tbW} without a top quark in the
    \emph{s}-channel, and \emph{bbWW} without a top quark in the \emph{s}-channel. (Generated
    using \cite{Ellis:2016jkw}.) \Shufang{Use $\chi_i^0$ etc.}}%
  \label{fig:feynman_diagrams}
\end{figure}
\end{comment}

In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section for the Higgsino-like NLSPs.  The cross section varies between 200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of $\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as cauculated in SUSY-HIT. \Shufang{Add ref for SUSYHIT.}  While one of the Higgsinos mostly decays to $Z$, the other Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative discovery channel for Higgsinos.

\begin{figure}[h]
  \centering
  \includegraphics[width=0.49\textwidth]{images/higgsino_production_xsection.png}
  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
  \caption{Higgsino pair production cross section, as a function of $|\mu|$. The
  cross-sections are calculated using Prospino2, with $M_1 = 25$ GeV. However, it
  should be noted that the dependence on $M_1$ is very weak.  \Shufang{Could you make the two plot same aspect ratios?}}
  \label{fig:xsection_plot}
\end{figure}

Searches for pair produced nearly mass-degenerate Higgsinos  have been performed 
at ATLAS and CMS for various decay  topologies. While the identity of the 
LSP in these searches is a gravitino  instead of a Bino,   the limits are still  relevant, since both  our analysis  and the experimental ones consider that  
the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the 
LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP and Bino LSP case.}

The most stringent limits are obtained by ATLAS in \cite{Aaboud:2018htj},
where Higgsinos with masses between 130 and 230 GeV and between 290 and 880 
GeV are excluded using a search channel with a final state containing 3+ 
\emph{b}-jets. \Shufang{you mean more than 3 b jets?} The CMS analysis
in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
$4b+\slashed{E}_T, 2l + 2j + \slashed{E}_T, 3l/4l + \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
to exclude Higgsino-like neutralino masses up to 650-750 GeV, depending on the assumed branching 
fraction of the neutralino decays. Finally, the $4l$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
to set a lower bound of 295 GeV on the Higgsino mass  \cite{Aaboud:2018zeb}.
\Shufang{So the only available limit is with gravitino LSP?  Then it does not apply.}
\Shufang{There is no  WZ+MET limit on Higgsinos NLSP?}

%ATLAS 1806.04030, (hh/hZ/ZZ/) --> 4b
% CMS 1801.03957, combination of channels
% 4b + MET, 2l + 2j + MET, >3l + MET, diphoton + MET
% ATLAS, 4 leptons (hh/ZZ/hZ --> 4l)

\begin{comment}
While the majority of the existing searches for supersymmetry focus on gluino
pair production, there are a number of analyses involving electroweak pair
production of charginos and neutralinos as well, which we will attempt to briefly review here.  Searches
involving multiple leptons and missing energy $(2l/3l +\slashed{E}_T)$ in the
final state are described in
\citep{Aaboud:2018sua,Aaboud:2018jiw, ATLAS:2016uwq,Khachatryan:2014qwa,Chatrchyan:2012pka}, assuming a
wino-like NLSP and a bino-like LSP. The best reach is obtained in the $2/3l$
channel by ATLAS with 36.1 fb$^{-1}$ of data, with NLSP masses up to 600 GeV
excluded for massless LSPs \citep{Aaboud:2018sua}.

% AP: These have intermediate sleptons, so I am omitting them.
%Topologies with one or two hadronically-decaying tau leptons and missing energy
%in the final state have been studied in \citep{ATLAS:2016ety,
%Khachatryan:2016trj}, with the greatest reach obtained by ATLAS in
%\citep{ATLAS:2016ety}, using 13 TeV data - they are able to exclude wino-like
%NLSPs up to a mass of 700 GeV for a massless bino-like LSP.

Searches with a combination of leptons and jets in the final states can be found
in \citep{Aad:2014vma,Khachatryan:2015kxa,Khachatryan:2014mma}. Winos up to 465
GeV are excluded in the $2l + 0/2j$ final states in \citep{Aad:2014vma}. A
compressed mass spectrum is studied in \citep{Khachatryan:2015kxa}, with a mass
difference of about 50 GeV between winos and binos. This study uses the vector
boson fusion channel, with a final state of $2l + 2j + \slashed{E}_T$, and
excludes winos up to a mass of 170 GeV. Of particular interest to us is the
analysis in \citep{Khachatryan:2014mma}, where higgsinos can be excluded up to a
mass of 380 GeV using the $bbll + \slashed{E}_T$ final state, but cannot be
discovered in any region of the relevant parameter space. As we shall see, a 100
TeV collider will enable us to greatly improve upon these limits.
\end{comment}

\section{Analysis Details}\label{sec:analysis}

In this section, we  describe our strategies for both the traditional
cut-and-count analysis, as well as the analysis carried out with boosted
decision trees.

\subsection{Simulation}\label{simulation}

We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
\texttt{MadEvent} \citep{Alwall:2014hca}, then passed those events to Pythia 6
\citep{Sjostrand:2006za} for showering and hadronization. Finally, we used
\texttt{Delphes 3} \citep{deFavereau:2013fsa} to perform a fast, parametrized
detector simulation, with the detector card devised by the FCC-hh working
group\footnote{\url{https://github.com/HEP-FCC/FCCSW/blob/master/Sim/SimDelphesInterface/data/FCChh_DelphesCard_Baseline_v01.tcl}}.
For the backgrounds, we allowed up to one additional jet in the final state, to
approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
parameter set to 40 GeV. The Higgsino pair production cross sections were
calculated using \texttt{Prospino2} \citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
Wino, we set its mass parameter $M_2$ to 3 TeV.  \Shufang{5 TeV was used for another calculation earlier.  Be consistent here.}

Since we expect our signal process to have a dilepton resonance from an on-shell
$Z$ boson, we restricted the phase space for event generation for backgrounds to
the region where the invariant mass of dilepton pairs lies between 80 and 100
GeV. Additionally, the Bino dark matter that escapes the detector would result
in a large amount of missing transverse energy ($\met$), so we required
a minimum $\met$ of 100 GeV at the parton level for the backgrounds as
well.

At the detector simulation level, we relaxed the lepton isolation criterion in the
\texttt{Delphes} detector card from $\Delta R_{min}$ from 0.4 to 0.05. This is
motivated by the fact that due to the large mass difference between the Higgsino
NLSP and the Bino LSP in our search channel, the intermediate $Z$ bosons will be
highly boosted, and the leptons to which they decay will be highly collimated.
The value of 0.05 is consistent with what is suggested in previous 100 TeV
studies (\citep{Acharya:2014pua,Gori:2014oua,Bramante:2014tba}) and will allow
for easier comparison between different search strategies.

\subsection{Analysis using cut-and-count}
\label{event-selection}

For the cut-and-count analysis, we implemented successive one-dimensional cuts
on the variables listed below, using the MadAnalysis 5 package
\citep{Conte:2012fm}.

\begin{enumerate}
  \tightlist
  \item \emph{Trigger}: Events were selected if they had at least one lepton
    with $p_{T}^\ell >$ 100 GeV.  \Shufang{This is quite a high trigger level cut.  Is the 100 TeV lepton trigger need such a high pT? or it is a lower pT trigger, with a 100 GeV advanced cut to suppress the bg?}

  \item \emph{Identification:}

    \begin{itemize}
      \item Events contain exactly two leptons of the same flavor
        and with opposite signs (\textsc{sfos}), with $p_{T}^\ell >$ 15 GeV and
        $\vert\eta^\ell\vert <$ 2.5.
      \item Events contain at least two \emph{b}-tagged jets with
        $p_{T}^b > 30$ GeV and $\vert\eta^b\vert <$ 2.5.
    \end{itemize}

  \item \emph{Invariant mass of Z-candidate:}  $85\ {\rm GeV}<m_{\ell^{+}\ell^{-}}<95\ {\rm GeV}$.

  \item \emph{Invariant mass of h-candidate:} $75\ {\rm GeV}<m_{bb}<150\ {\rm GeV}$ for two leaving $b$-jets.

  \item \emph{Missing Tranverse Energy:}  $\met> 400$ GeV.

  \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
\begin{eqnarray}
M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\ M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)^2 - \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}，
\end{eqnarray} 
 for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.
\Shufang{Check the formula.  Unit is not correct.}
    Representative kinematic
  distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification, and
  $\slashed{E}_{T}$ cuts. The
  distribution for the \emph{bbWW} background is not shown, since it is negligible in
  comparison to the others.   We can see that the distribution of $M_R$ is peaked
  around 1 TeV for the signal, which consistent with what we would expect, since
  it corresponds to the mass difference between the NLSP and LSP.  For this mass combination, requiring $M_R >$ 800
  GeV and $M_T^R >$ 400 GeV yields the greatest significance.

\end{enumerate}

\begin{figure}[h]
\centering
\includegraphics[trim = {0.3cm 0.6cm 0.1cm 0}, clip, width=0.496\textwidth]{images/mR_copy.png}
\includegraphics[trim = {0.3cm 0.6cm 0.1cm 0}, clip, width=0.496\textwidth]{images/mTR_copy.png}
\caption{Normalized distributions of the razor kinematical variables $M_R$
  (left) and $M_T^R$ (right) for signal process with a 1 TeV Higgsino NLSP and 25 GeV Bino LSP,  as well as the dominant $tt$ and $tbW$ backgrounds,
  after the trigger, identification, and $\slashed{E}_{T}$ cuts.}
\label{fig:razor_histos}
\end{figure}

\begin{table}[h]
  \centering
  \input{tables/cutflowtable.tex}
  \caption{Representative cut flow table for the benchmark point $|\mu|=1$ TeV,
    $M_1 = 25$ GeV, for a traditional cut-and-count analysis. All cross sections
    are given in femtobarns, and the units for the missing energy, invariant
    mass, and razor variable cuts are GeV. The significance, $S/\sqrt{B}$, is
    calculated for an integrated luminosity of 3 ab$^{-1}$.    }
\label{tab:cc_cutflowtable}
\end{table}

Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
signal benchmark point with a $|\mu| =$ 1 TeV and $M_1$ = 25 GeV.   The
cross-sections of the backgrounds are averages \Shufang{What do you mean by average?}  of the cross-sections output by
MadEvent after performing the MLM matching procedure. Their small size reflects
the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
the benchmark points, we require a minimum of 5 signal events left over after
cuts. We can see that, after applying our cuts, $tt$ and $tbW$ remain as the
dominant backgrounds. The values of the razor variable cuts were chosen to
maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
of 3000 fb$^{-1}$), shown in the last column.  \Shufang{For the reach plot, does razor variable cut value changes for each grid point?}

\subsection{Analysis using gradient boosted decision trees}\label{subsec:bdt}

For each signal mass combination and each background process, we preselected
events that passed the lepton trigger, contained two SFOS leptons and two
$b$-tagged jets, and calculated a number of kinematic variables for each event. We then
placed these kinematic variables in an array, with each row corresponding to an event, and
the columns corresponding to the kinematic variables. A mixture of low-level and high level
kinematic variables was shown to have the greatest effectiveness. The kinematic variables chosen were
$m_{\ell\ell}$, $m_{bb}$, $M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic
transverse energy $THT$, \Shufang{THT?} and transverse momenta of individual final state
leptons and $b$-quarks: $p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We
then divided the events into training and test sets, with the training set
comprising 75\% of signal events and 30\% of background events. \Shufang{You mean 70\% of all signal event generated? } We used the
\texttt{scikit-learn} package  \citep{Pedregosa2011} to implement our analysis.
{\it A boosted decision tree classifier was trained with 1000 weak learners and a
learning rate of 0.025. } \Shufang{We probably don't need this details.}  After the classifier is trained, we use it to assign
scores to individual events. A more negative score indicates a more
background-like event, and a more positive score denotes a more signal-like
event. After the scores have been assigned to the events in the test sets, we
can use this score just as we would a regular kinematical variable, that is, we
apply a cut that selects events with a minimum of this score. The value of the
cut is chosen to maximize the significance for each signal benchmark point. The
distribution of scores for the specific benchmark point ($|\mu|$ = 1 TeV, $M_1$
= 25 GeV) is shown in figure \ref{fig:bdt_response}. We observe that there is an
appreciable separation between the signal and background distributions.

\begin{figure}[h]
\centering
\includegraphics[trim = {0 0.5cm 0 0},clip]{images/bdt_response_png}
\caption{Distribution of the decision function of the gradient boosted decision
tree classifier algorithm for signal ($|\mu| = 1$ TeV $M_1 = 25$ and
backgrounds. }
\label{fig:bdt_response}
\end{figure}

\begin{table}[h]
  \centering
  \input{tables/paper_bdt_cutflowtable.tex}
  \caption{Representative cut flow table for the same benchmark point and
    integrated luminosity as in table \ref{tab:cc_cutflowtable}, but using a
    boosted decision tree (BDT) analysis instead. The preselection is equivalent
    to the trigger and identification cuts listed in table
    \ref{tab:cc_cutflowtable}. As before, all the cross sections are in
  fb.  }
\label{tab:bdt_cutflowtable}
\end{table}

Table \ref{tab:bdt_cutflowtable} shows the cut efficiences for the same
representative benchmark point as in table \ref{tab:cc_cutflowtable}, but this
time for a boosted decision tree analysis. We observe that the statistical
significance we can achieve goes up from 2.4 to 8.4, a roughly four-fold
increase.  \Shufang{Do we still require 5 signal events minimum here?}

For certain values of the
cuts on kinematical variables or the score of the classifier, no events survived
for one or more of the background components. To guard against overly optimistic
estimates of the significance $S/\sqrt{B}$, we set a lower bound of 3 for the
number of MC events after cuts for each background component, corresponding to
the 95\% confidence interval for a Poisson distribution.

\begin{figure}[h]
\centering
%\includegraphics[width=0.6\textwidth]{images/combined.pdf}
\includegraphics[width=0.6\textwidth]{images/dm_100_TeV_contours.png}

\caption{ Discovery (red) and exclusion (blue) contours for the traditional
  cut-and-count analysis (solid) and boosted decision tree analysis (dashed),
  for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$. \Shufang{Shall we show the lepton search result in this figure for comparison?} }

\label{fig:contours}
\end{figure}

\section{Discovery and exclusion limits}
\label{sec:results}

Fig.~\ref{fig:contours} shows the expected reach in parameter space for
95\% C.L. exclusion and 5$\sigma$ discovery in the parameter space of $|\mu|$ vs. $M_1$ for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$. The cut-and-count strategy is able to discover
Higgsinos up to 750 GeV  and exclude them up to 1.3 TeV. \Shufang{How do you read out the numbers?}  The boosted decision
tree analysis, improves this reach - it is able to discover Higgsinos up to 1.3
TeV, and exclude them up to 1.8 TeV in favorable points in parameter space.
Similarly, Binos can be discovered up to 300 GeV and excluded up to 800 GeV with
the rectangular cut analysis, and the BDT analysis can discover them up to about
900 GeV and exclude them up to 1.3 TeV. Table \ref{tab:summary} contains a
summary of these results. Since the background left after cut is relatively low, We do not include systematic errors in these
estimates.

This improvement is substantial, but perhaps not spectacular. However, it should
be kept in mind that this is probably a conservative estimate. Since we reserve
30\% of the data for training purposes, and impose the condition that the
minimum number of MC events after cuts for the backgrounds must be 3 (see note
at the end of subsection \ref{subsec:bdt}), the true rate of background
rejection by the classifier is likely underestimated, and the expected
significance from the BDT analysis will improve. This extrapolation is
qualitatively supported by the high degree of separation between signal and
backgrounds seen in Fig.~\ref{fig:bdt_response}, and the fact that a larger
fraction of the signal events are preserved with the BDT approach compared to
the rectangular cut approach, as can be seen in Tables \ref{tab:cc_cutflowtable}
and \ref{tab:bdt_cutflowtable}.

In regions with large mass differences between the LSP and NLSP, the reach is
not as good, since the intermediate SM Higgs boson will be highly boosted, and
thus decay into a highly collimated pair of $b$-jets. The extent to which this
affects our results can be estimated from table \ref{tab:cc_cutflowtable}. We
see that requiring two $b$-tagged jets reduces our signal cross-section by
roughly 87\%. This is far more than the 28\% reduction that one might naively
expect as a result of applying the $b$-tagging efficiency of about 85\%
specified in our \texttt{Delphes} card.  \Shufang{How do you get the 28\% number? }

\begin{table}[h]
\centering
\begin{tabular}{l|rr}
\toprule
Analysis type & 5$\sigma$ (discovery)& 1.96$\sigma$ (exclusion)\\
\midrule
Rectangular cuts & (0.75, 0.30) & (1.3, 0.8)\\
BDT Analysis & (1.3, 0.90) & (1.8, 1.3)\\
\bottomrule
\end{tabular}
\caption{Discovery reaches and expected exclusion limits (in TeV) for the
parameters $(|\mu|,M_1)$ for the rectangular cuts and BDT analyses. \Shufang{Probably don't need this table.} }
\label{tab:summary}
\end{table}

\section{Conclusion}\label{sec:conclusion}

In this paper, we examined the discovery potential for a 100 TeV $pp$ collider For 
pair-produced heavy Higgsinos with Bino LSP, via 
intermediate $Z$ and $h$ bosons that decay to a pair of leptons and $b$ quarks
respectively.

We pursued two analysis strategies. One was the traditional cut-and-count methos , including razor variables
that are sensitive to the mass difference between the LSP and the NLSP. The
other strategy was to use a boosted decision tree classifier trained with a
number of low- and high-level kinematic variables, including razor variables. We expected
that the machine learning approach would be able to more efficiently determine
the optimal decision boundary between signal and background events in feature
space than the traditional   cut-and-count method.

Overall, we find that the reach of our analysis strategy is a significant
improvement over that of the LHC.  \Shufang{Did we mention the LHC reach?}  We found that the rectangular cut strategy has
the potential to discover Higgsino LSPs up to a mass of 750 GeV, and exclude
them up to a mass of 1.3 TeV. As expected, the boosted decision tree classifier
performs better, with the ability to discover Higgsino NLSPs up to 1.3 TeV and
exclude them up to a mass of 1.8 TeV. With the BDT analysis, Bino dark matter
candidates can be discovered up to 900 GeV, and excluded up to 1.3 TeV. In the
process, we highlighted the importance of generating enough Monte Carlo events
to estimate the huge backgrounds at a 100 TeV $pp$ collider.

Additionally, we found that the reach for both strategies is considerably
reduced when the difference $ |\mu|-M_1$ is high, since it results in a highly
boosted $h$ that decays to a collimated pair of $b$'s that will most likely be
identified as a single jet. This is not an insurmountable difficulty - there are
ways to deal with collimated jets, although they are beyond the scope of this
work. This issue does, however, highlight the necessity of improving isolation
performance at a 100 TeV $pp$ machine, where large mass hierarchies can result in
highly boosted/collimated decay products. For a review of currently used methods
to determine jet substructure, see \citep{Shelton:2013an}. In the future,
machine learning techniques might be profitably applied to this area as well -
for a review of developments along this line, see \citep{Schwartzman:2016jqu}.

The collimation of the $b$-jets, along with the fact that we take into account
detector effects using Delphes, result in a lower reach in the high $|\mu|$, low
$M_1$ region than the multilepton analysis in \citep{Gori:2014oua}, which is
able to exclude Higgsinos up to a mass of 2.9 TeV for massless binos. The reach
of our analysis is slightly higher in the region where the difference between
$|\mu|$ and $M_1$ is smaller. This is consistent with our usage of the razor
variable $M_R$, which is sensitive to the mass difference between the parent
Higgsino and daughter Bino.

A 100 TeV $pp$ collider represents an excellent opportunity to discover
physics beyond the Standard Model. The extremely high energies and luminosities
involved will present new challenges for particle physicists, and it is likely
that machine learning will play an important part in facing them.

\acknowledgments

We would like to thank Matt Leone and Ken Johns for helpful discussions.  The
research activities of AP and SS were supported in part by the Department of
Energy under Grant DE-FG02-13ER41976 / de-sc0009913;. An allocation of computer
time from the UA Research Computing High Performance Computing (HPC) and High
Throughput Computing (HTC) at the University of Arizona is gratefully
acknowledged.

\bibliography{references}

\end{document}

### 2019-07-14 main.tex
Removing font-related lines
Removed unicode character
Addressed some comments

@@
 \usepackage{pgfplots}
-\usepackage[T1]{fontenc}
-\usepackage{fontspec}
 \usepackage{booktabs, longtable}
@@
 \renewcommand{\H}{\widetilde{H}^0}
-\renewcommand{\B}{\widetilde{B}^0}
+\newcommand{\B}{\widetilde{B}^0}
 \newcommand{\N}{\widetilde{\chi}^0}
@@
 from CP-violation experiments.  The low lying 
-fermionic superpartners consist of neutralinos and charginos (collectively known as Electroweakinos), and gluinos.
-The current LHC search limits on gluinos are already around xxx TeV~\cite{}.
-The limits on Electroweakinos, howeer, are still relatively weak: around xxx $-$ xxx GeV~\cite{}, depending on the decay modes of the parent electroweakinos.
-\Shufang{add ref for gluno limit and electroweakino limits.
-Fill in the number.} In this paper, we will focus on the discovery potential of the neutralinos and charginos at the 100 TeV $pp$ collider.
+fermionic superpartners consist of neutralinos and charginos (collectively
+known as electroweakinos), and gluinos. The current LHC search limits on
+gluinos are already around 2.4 TeV~\cite{CMS-PAS-SUS-19-005}. \Adarsh{Should
+2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
+this limit is from the disappearing track search - does that apply for us?} The
+limits on electroweakinos,
+howeer, are still relatively weak: around xxx $-$ xxx GeV~\cite{}, depending on
+the decay modes of the parent electroweakinos.  \Shufang{add ref for 
+electroweakino limits. Fill in the number.} In this paper, we will
+focus on the discovery potential of the neutralinos and charginos at the 100
+TeV $pp$ collider.
 
 % Point to review papers for enumeration of studies
-The decay patterns of the Electroweakinos (Winos, Binos, and Higgsinos)
+The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos)
 depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
@@
 are mixtures of the Bino, Wino, and two neutral Higgsinos: 
-($\B,\widetilde{W}^0,\H_u,\H_d$). In the basis of these gauge eigenstates, the mass
+($\B,\widetilde{W}^0,\H_d,\H_u$). In the basis of these gauge eigenstates, the mass
 matrix of the neutralinos can be written as
@@
   M_1 & 0 & -\cb\sw\mz & \sinb\sw\mz \\
-  0 & M_2 & \cb\cw\mz & \sinb\cw\mz \\
+  0 & M_2 & \cb\cw\mz & -\sinb\cw\mz \\
   -\cb\sw\mz & \cb\cw\mz & 0 & -\mu \\
@@
 \end{pmatrix},\]
-\Shufang{Check.  I think this matrix goes with ($\B,\widetilde{W}^0,\H_d,\H_u$).}
-\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$ for $\theta_W$ being the Weinberg mixing angle.
-$s_\beta, c_\beta$ are defined accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the
-vacuum expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm GeV})^2$. The parameters $M_1$, $M_2$,
-and $\mu$ are the mass parameters of Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as $\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.
+
+\Shufang{Check.  I think this matrix goes with
+($\B,\widetilde{W}^0,\H_d,\H_u$). \Adarsh{Good catch - I have fixed it.}}
+\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
+for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
+accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
+expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm
+GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
+Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as
+$\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.
 
@@
 
-The optimal search strategy for finding Electroweakinos is highly dependent on
+The optimal search strategy for finding electroweakinos is highly dependent on
 the their mass spectrums \citep{Han:2013kza}.  Phenomenological collider studies on finding
@@
 found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
-\Shufang{Say a few words about typical search strategy there.}.
+\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
+believe I've already addressed this with the paragraphs I added below in response
+to your comment ... let me know if I should add more details.}.
 Well-separated spectra have been studied in \citep{Gori:2014oua,
@@
     $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
-    TeV \emph{pp} collider. The pair-production cross sections are taken from
+    TeV \emph{pp} collider . The pair-production cross sections are taken from
     \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
@@
     and the branching ratios to the SM final states are taken from
-    \citep{Olive:2016xmw}.  \Shufang{Specify M1 as well and use the actual Br.} \Shufang{rewrite the entry.  Why chi2pm? Should not it be chi1pm?}}
+    \citep{Olive:2016xmw}. \ap{In this scenario, the LSP is assumed to be
+    massless}.
+    \Shufang{Specify M1 as well and use the actual Br.} \Adarsh{I added a line
+  specifying that the LSP is massless. As for the actual BR, I assume you mean
+  calculate it using SUSY-HIT? That'll take a bit more time, but I'll try to
+  get it.}\Shufang{rewrite the entry.  Why chi2pm? Should not it be chi1pm?}}
+  \Adarsh{$\chi_1$ is the LSP, right? In our case it's the bino, which is not
+  charged...}
   \label{tab:xsections}
@@
 
-In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section for the Higgsino-like NLSPs.
-The cross section varies between 200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV.
-The right panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of $\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as cauculated in SUSY-HIT.
-\Shufang{Add ref for SUSYHIT.}  While one of the Higgsinos mostly decays to $Z$, the other Higgsino mostly decays to $h$.
-$Zh+\met$ signal thus provide an alternative discovery channel for Higgsinos.
+In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production
+cross section for the Higgsino-like NLSPs.  The cross section varies between
+200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
+panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
+$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
+While one of the Higgsinos mostly decays to $Z$, the other
+Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative
+discovery channel for Higgsinos.
 
@@
 the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the 
-LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP and Bino LSP case.}
+LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP
+and Bino LSP case.} \Adarsh{True, but there have been no experimental searches
+for Higgsino NLSP - Bino LSP. This seemed like the most similar
+channel/topology to ours.}
 
@@
   \item \emph{Razor variables}:  Two razor variables are used in our analyses: 
-\begin{eqnarray}
-M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\ M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)^2 - \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}，
-\end{eqnarray} 
+\begin{align}
+M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
+M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)^2
+- \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
+\end{align}
  for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.

### 2019-07-14 main.tex
Addressed all comments except one

@@
 limits on electroweakinos,
-howeer, are still relatively weak: around xxx $-$ xxx GeV~\cite{}, depending on
+howeer, are still relatively weak: around 0.3 $-$ 1.1 \Adarsh{I'm rounding 1150
+GeV down to 1.1 TeV - is that ok?}
+TeV~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae} \Adarsh{0.15
+- 1.1 if we include the gravitino analysis}, depending on
 the decay modes of the parent electroweakinos.  \Shufang{add ref for 
@@
 
-Since the Bino is the only supersymmetric particle lighter than the Higgsino in the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.
-Search for Higgsinos with intermediate gauge boson and  multi-lepton final states have been studied in Ref.~\cite{Gori:2014oua}.
-\Shufang{Add more details for that study.
-Which channel, search resutls, etc.
-This would be our comparison for our analyses.}  In this paper we attempt to exploit the relatively high branching ratio of
-the SM Higgs boson to \emph{b} quarks, and study the decay mode $\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
+Since the Bino is the only supersymmetric particle lighter than the Higgsino in
+the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a
+neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.  Searches for
+Higgsinos with intermediate gauge boson and multi-lepton final states have been
+studied in Ref.~\cite{Gori:2014oua}. \Shufang{Add more details for that study.
+Which channel, search resutls, etc. This would be our comparison for our
+analyses.} \Adarsh{These details are already in section 2 (page 3) - should I
+repeat them here?}  In this paper we attempt to exploit the relatively high branching
+ratio of the SM Higgs boson to \emph{b} quarks, and study the decay mode
+$\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
 
@@
 multi-lepton channels, of the form
-\begin{equation}
+
+\begin{align}
   pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
@@
   \met,
-\end{equation}
+\end{align}
+
 \noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
@@
   cross-sections are calculated using Prospino2, with $M_1 = 25$ GeV. However, it
-  should be noted that the dependence on $M_1$ is very weak.  \Shufang{Could you make the two plot same aspect ratios?}}
+  should be noted that the dependence on $M_1$ is very weak.  
+  \Shufang{Could you make the two plot same aspect ratios?}}
+  \Adarsh{It would be pretty time consuming to do, so I would rather not if
+    it's not essential - I think it might look better to put the plots in
+  separate figures.}
   \label{fig:xsection_plot}
@@
 
-Searches for pair produced nearly mass-degenerate Higgsinos  have been performed 
-at ATLAS and CMS for various decay  topologies. While the identity of the 
-LSP in these searches is a gravitino  instead of a Bino,   the limits are still  relevant, since both  our analysis  and the experimental ones consider that  
-the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the 
+Searches for pair produced nearly mass-degenerate Higgsinos  have been
+performed at ATLAS and CMS for various decay  topologies. While the identity of
+the LSP in these searches is a gravitino  instead of a Bino,   the limits are
+still  relevant, since both  our analysis  and the experimental ones consider
+that  the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the
 LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP
-and Bino LSP case.} \Adarsh{True, but there have been no experimental searches
-for Higgsino NLSP - Bino LSP. This seemed like the most similar
+  and Bino LSP case.} \Adarsh{True, but there have been no experimental
+  searches for Higgsino NLSP - Bino LSP. This seemed like the most similar
 channel/topology to ours.}
@@
 where Higgsinos with masses between 130 and 230 GeV and between 290 and 880 
-GeV are excluded using a search channel with a final state containing 3+ 
-\emph{b}-jets. \Shufang{you mean more than 3 b jets?} The CMS analysis
+GeV are excluded using a search channel with a final state containing at least
+three \emph{b}-jets. \Shufang{you mean more than 3 b jets?} \Adarsh{At least 3 -
+I've reworded to clarify.} The CMS analysis
 in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
@@
 \Shufang{So the only available limit is with gravitino LSP?  Then it does not apply.}
-\Shufang{There is no  WZ+MET limit on Higgsinos NLSP?}
+\Shufang{There is no  WZ+MET limit on Higgsinos NLSP?} \Adarsh{Yes, that is the
+only available limit with neutral Higgsino NLSPs and bino LSP, and with
+on-shell W and Z. WZ+MET limits (with on-shell W and Z). Should I remove the
+sentences with the gravitino LSP?}.
 
@@
 calculated using \texttt{Prospino2} \citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
-Wino, we set its mass parameter $M_2$ to 3 TeV.  \Shufang{5 TeV was used for another calculation earlier.  Be consistent here.}
+Wino, we set its mass parameter $M_2$ to 5 TeV. \Shufang{5 TeV was used for
+another calculation earlier. Be consistent here.}
 
@@
   \item \emph{Trigger}: Events were selected if they had at least one lepton
-    with $p_{T}^\ell >$ 100 GeV.
-\Shufang{This is quite a high trigger level cut.
-Is the 100 TeV lepton trigger need such a high pT?
-or it is a lower pT trigger, with a 100 GeV advanced cut to suppress the bg?}
+    with $p_{T}^\ell >$ 100 GeV.  \Shufang{This is quite a high trigger level
+    cut.  Is the 100 TeV lepton trigger need such a high pT? or it is a lower
+  pT trigger, with a 100 GeV advanced cut to suppress the bg?} \Adarsh{I had it
+at 20 GeV earlier, but Ken Johns (and maybe you?) told me that that would be
+far too low for a 100 TeV collider. Also, this is consistent with the analysis
+in \cite{Gori:2014oua}.}
 
@@
 M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
-M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)^2
+M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
 - \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
@@
  for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.
-\Shufang{Check the formula.  Unit is not correct.}
+ \Shufang{Check the formula.  Unit is not correct.} \Adarsh{Fixed.}
     Representative kinematic
@@
 signal benchmark point with a $|\mu| =$ 1 TeV and $M_1$ = 25 GeV.   The
-cross-sections of the backgrounds are averages \Shufang{What do you mean by average?}  of the cross-sections output by
-MadEvent after performing the MLM matching procedure. Their small size reflects
+cross-sections of the backgrounds are \Shufang{What do you mean by average?}
+\Adarsh{I reworded it.}
+\ap{obtained from} MadEvent after performing the MLM matching procedure. Their small size reflects
 the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
-the benchmark points, we require a minimum of 5 signal events left over after
+the benchmark points, we require a minimum of 3 signal events left over after
 cuts. We can see that, after applying our cuts, $tt$ and $tbW$ remain as the
@@
 maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
-of 3000 fb$^{-1}$), shown in the last column.  \Shufang{For the reach plot, does razor variable cut value changes for each grid point?}
+of 3000 fb$^{-1}$), shown in the last column.  \Shufang{For the reach plot,
+does razor variable cut value changes for each grid point?} \Adarsh{Yes, for
+the rectangular cuts analysis.}
 
@@
 $m_{\ell\ell}$, $m_{bb}$, $M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic
-transverse energy $THT$, \Shufang{THT?} and transverse momenta of individual final state
+transverse energy $THT$, \Shufang{THT?} \Adarsh{Should I use some different
+notation? Maybe $H_T$?} and transverse momenta of individual final state
 leptons and $b$-quarks: $p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We
 then divided the events into training and test sets, with the training set
-comprising 75\% of signal events and 30\% of background events. \Shufang{You mean 70\% of all signal event generated? } We used the
+comprising 75\% of signal events and 30\% of background events. \Shufang{You
+mean 70\% of all signal event generated?} \Adarsh{Yes.} We used the
 \texttt{scikit-learn} package  \citep{Pedregosa2011} to implement our analysis.
-{\it A boosted decision tree classifier was trained with 1000 weak learners and a
-learning rate of 0.025. } \Shufang{We probably don't need this details.}  After the classifier is trained, we use it to assign
+A boosted decision tree classifier was trained with 1000 weak learners and a
+learning rate of 0.025. \Shufang{We probably don't need this details.}
+\Adarsh{I would like to keep it, for the sake of reproducibility (and for
+future researchers to compare their ML-based methods to ours).}
+After the classifier is trained, we use it to assign
 scores to individual events. A more negative score indicates a more
@@
 increase.  \Shufang{Do we still require 5 signal events minimum here?}
+\Adarsh{Actually, we do a minimum of three events - more consistent with
+Poisson statistics. I've updated the previous mention of 5 events.}
 
@@
   cut-and-count analysis (solid) and boosted decision tree analysis (dashed),
-  for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$. \Shufang{Shall we show the lepton search result in this figure for comparison?} }
+  for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
+\Shufang{Shall we show the lepton search result in this figure for comparison?}
+\Adarsh{You mean the results from \cite{Gori:2014oua}? That sounds pretty
+difficult to do...}
+}
 
@@
 
-Fig.~\ref{fig:contours} shows the expected reach in parameter space for
-95\% C.L.
-exclusion and 5$\sigma$ discovery in the parameter space of $|\mu|$ vs.
-$M_1$ for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
-The cut-and-count strategy is able to discover
-Higgsinos up to 750 GeV  and exclude them up to 1.3 TeV. \Shufang{How do you read out the numbers?}  The boosted decision
-tree analysis, improves this reach - it is able to discover Higgsinos up to 1.3
-TeV, and exclude them up to 1.8 TeV in favorable points in parameter space.
-Similarly, Binos can be discovered up to 300 GeV and excluded up to 800 GeV with
-the rectangular cut analysis, and the BDT analysis can discover them up to about
-900 GeV and exclude them up to 1.3 TeV. Table \ref{tab:summary} contains a
-summary of these results. Since the background left after cut is relatively low, We do not include systematic errors in these
-estimates.
+Fig.~\ref{fig:contours} shows the expected reach in parameter space for 95\%
+C.L. exclusion and 5$\sigma$ discovery in the parameter space of $|\mu|$ vs.
+$M_1$ for 100 TeV $pp$ collider with an integrated luminosity of 3000
+fb$^{-1}$. The cut-and-count strategy is able to discover Higgsinos up to 750
+GeV  and exclude them up to 1.3 TeV. \Shufang{How do you read out the numbers?}
+\Adarsh{I am just looking at the plot and estimating the approximate boundaries
+of the curves..}  The boosted decision tree analysis, improves this reach - it
+is able to discover Higgsinos up to 1.3 TeV, and exclude them up to 1.8 TeV in
+favorable points in parameter space.  Similarly, Binos can be discovered up to
+300 GeV and excluded up to 800 GeV with the rectangular cut analysis, and the
+BDT analysis can discover them up to about 900 GeV and exclude them up to 1.3
+TeV. Since the background left after cut is relatively low, We do not include
+systematic errors in these estimates.
 
@@
 expect as a result of applying the $b$-tagging efficiency of about 85\%
-specified in our \texttt{Delphes} card.  \Shufang{How do you get the 28\% number? }
+specified in our \texttt{Delphes} card.  \Shufang{How do you get the 28\%
+number? } \Adarsh{$(1 - 0.85^2)*100 = 27.75 \approx 28$.}
 
-\begin{table}[h]
-\centering
-\begin{tabular}{l|rr}
-\toprule
-Analysis type & 5$\sigma$ (discovery)& 1.96$\sigma$ (exclusion)\\
-\midrule
-Rectangular cuts & (0.75, 0.30) & (1.3, 0.8)\\
-BDT Analysis & (1.3, 0.90) & (1.8, 1.3)\\
-\bottomrule
-\end{tabular}
-\caption{Discovery reaches and expected exclusion limits (in TeV) for the
-parameters $(|\mu|,M_1)$ for the rectangular cuts and BDT analyses. \Shufang{Probably don't need this table.} }
-\label{tab:summary}
-\end{table}
+\Adarsh{I removed the table as you suggested.}
 
@@
 Overall, we find that the reach of our analysis strategy is a significant
-improvement over that of the LHC.  \Shufang{Did we mention the LHC reach?}  We found that the rectangular cut strategy has
+improvement over that of the LHC.  \Shufang{Did we mention the LHC reach?}
+\Adarsh{I was referring to the reach for the gravitino LSP analysis - should I
+remove that?}  We found that the rectangular cut strategy has
 the potential to discover Higgsino LSPs up to a mass of 750 GeV, and exclude

### 2019-07-19 main.tex
Updates from Overleaf

@@
   Standard Model (MSSM). In this paper, we describe a search strategy  
-  for discovering pair-produced Higgsino-like NLSPs  at a 100 TeV 
-  hadron collider that decay to Bino-like LSPs via intermediate Z and 
+  for discovering pair-produced Higgsino-like next-to-lightest supersymmetric particles  at a 100 TeV 
+  hadron collider that decay to Bino-like lightest supersymmetric particle (LSP) via intermediate $Z$ and 
   SM Higgs bosons that in turn decay to a pair of leptons and a pair of 
-  $b$-quarks respectively: $\N_{2,3}\N_{3,2}
+  $b$-quarks respectively: $\N_{2}\N_{3}
   \rightarrow (Z\N)(h\N)\rightarrow 
@@
   Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
-  to 1.3 TeV at 95\% C.L. \\
-
-  \noindent \Shufang{Abstract need to be more detailed.  Let's worry about this after we
-  get the draft done.   } \\
+  to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially at large LSP mass region. \Shufang{Update the numbers.}
 }
@@
 considerations, the lightest of the  MSSM particles known as the 
-neutralinos emerges as the most attractive candidate for the LSP \citep{Bertone:2004pz}.
+neutralinos emerges as the most attractive candidates for the LSP \citep{Bertone:2004pz}.
 
@@
 2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
-this limit is from the disappearing track search - does that apply for us?} The
+this limit is from the disappearing track search - does that apply for us?
+Update - disappearing tracks not relevant, use the regular channel} \Shufang{Actually on a second thought, in split SUSY with heavy squarks, is the gluino lifetime long enough to leave displaced vertex at detectors?
+Check pheno of split SUSY paper.
+If still decay promptly, then use searches with off-shell squark.} The
 limits on electroweakinos,
-howeer, are still relatively weak: around 0.3 $-$ 1.1 \Adarsh{I'm rounding 1150
-GeV down to 1.1 TeV - is that ok?}
-TeV~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae} \Adarsh{0.15
-- 1.1 if we include the gravitino analysis}, depending on
+howeer, are still relatively weak: around 0.3 $-$ 1.1 
+TeV~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae}, depending on
 the decay modes of the parent electroweakinos.  \Shufang{add ref for 
-electroweakino limits. Fill in the number.} In this paper, we will
+electroweakino limits.  Again, for searches with heavy squark/sleptons.} In this paper, we will
 focus on the discovery potential of the neutralinos and charginos at the 100
@@
 depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
-roughly determine the masses of the Bino, Winos, and Higgsinos, respectively.
-In this paper, we consider the Higgsino NLSP and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
+roughly determine the masses of the Bino, Winos, and Higgsinos, respectively~\citep{Han:2013kz}. 
+In this paper, we consider the Higgsino next-to-LSP (NLSP) and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
 One of the motivations for studying Higgsinos is that the parameter $\mu$ 
-that governs its mass plays an important role in electroweak symmetry breaking 
-\citep{Acharya:2014pua}. Finding Higgsinos has traditionally been more challenging 
-than finding Winos, due to their lower production rate. This, however, can 
+that governs its mass plays an important role in electroweak symmetry breaking~\citep{Acharya:2014pua}, which tends to be small by naturalness considerations.
+Finding Higgsinos has traditionally been more challenging
+than finding Winos, due to their smaller production rate. This, however, can 
 be remedied by the increased  production cross sections and luminosities 
-at a 100 TeV collider.
+at a 100 TeV $pp$ collider.
 
@@
 neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.  Searches for
-Higgsinos with intermediate gauge boson and multi-lepton final states have been
-studied in Ref.~\cite{Gori:2014oua}. \Shufang{Add more details for that study.
-Which channel, search resutls, etc. This would be our comparison for our
-analyses.} \Adarsh{These details are already in section 2 (page 3) - should I
-repeat them here?}  In this paper we attempt to exploit the relatively high branching
-ratio of the SM Higgs boson to \emph{b} quarks, and study the decay mode
+Higgsino NLPs with a Bino LSP  via  multi-lepton final states have been
+studied in Ref.~\cite{Gori:2014oua} for 100 TeV $pp$ collider, for pair production of $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm$ and  $\widetilde\chi_{1}^+\widetilde\chi_1^-$.
+In this paper, we attempt to exploit the relatively high branching
+ratio of the SM Higgs boson to \emph{b} quarks, and study the potential of the channel of
 $\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
@@
 % Why a 100 TeV collider?
-A 100 TeV collider would open up an immense number of physics
-opportunities not afforded to a 14 TeV collider, including exploring the
+A 100 TeV $pp$ collider would open up an immense number of physics
+opportunities not afforded to a 14 TeV LHC, including exploring the
 most interesting regions of the split SUSY parameter space
@@
 actively discussed in the particle physics community, with two major
-proposals being the FCC-hh by CERN \citep{FCC-hh}, and the SppC  
+proposals being the Future Circular Collider (FCC)-hh by CERN \citep{FCC-hh}, and the Super Proton Proton Collider (SppC)  
 in China \citep{CEPC}.  As the next energy frontier machine, it is of 
@@
 
-We use razor variables~\citep{Rogan:2010kb} in our study, which were originally designed
+In our study, we use razor variables~\citep{Rogan:2010kb}, which were originally designed
 for searches involving two heavy, mass-degenerate pair-produced
@@
 
-At a 100 TeV collider, the backgrounds are going to be even larger than
+At a 100 TeV collider, the  SM backgrounds are going to be even larger than
 at the LHC.  An ancillary goal of this paper is to investigate the
@@
 the field of statistical learning in recent years, the usage of ML is
-rising in experimental particle physics - in fact, the discovery of the
+rising in experimental particle physics -- in fact, the discovery of the
 SM Higgs boson in 2012 was done with the help of neural networks
@@
 The rest of the paper is structured as follows. In Sec.~\ref{sec:model}, we describe our model and search channel in more
-detail, and list the existing experimental constraints on it. In Sec.~\ref{sec:analysis}, we describe our analysis strategies 
+detail, and list the existing experimental search bounds. In Sec.~\ref{sec:analysis}, we describe our analysis strategies 
 for both traditional cut-and-count analyses and analyses
 performed using BDT. In Sec.~\ref{sec:results},
-we present the results of our analyses, i.e. the expected discovery and exclusion
+we present the results of our analyses, i.e. the expected 5 $\sigma$ discovery and 95\% C.L. exclusion
 reaches. Finally, we conclude with the implications in Sec.~\ref{sec:conclusion}.
@@
 
-\[\mathbf{M}_{\widetilde{N}}=
+\begin{equation}
+\mathbf{M}_{\widetilde{N}}=
 \begin{pmatrix}
@@
   \sinb\sw\mz & -\sinb\cw\mz & -\mu & 0
-\end{pmatrix},\]
-
-\Shufang{Check.  I think this matrix goes with
-($\B,\widetilde{W}^0,\H_d,\H_u$). \Adarsh{Good catch - I have fixed it.}}
-\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
+\end{pmatrix},
+\end{equation}
+where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
 for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
@@
 believe I've already addressed this with the paragraphs I added below in response
-to your comment ... let me know if I should add more details.}.
+to your comment ... let me know if I should add more details.}. \Shufang{What you said below is for well separated spectra, not for mass spitting of 0.1 to 50 GeV.}
 Well-separated spectra have been studied in \citep{Gori:2014oua,
@@
 multi-lepton channels, of the form 
-
 \begin{align}
   pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
-  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2l/3l +  
+  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2\ell/3\ell +  
   \met,
 \end{align}
-
-\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, and
-$\widetilde{\chi}_1^0$ is the lightest neutralino. These searches work well since
+where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino,
+$\widetilde{\chi}_1^0$ is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$ or scalar $h$.  These searches work well since
 the large mass difference between the Electroweakinos can lead to energetic
 leptons that can be easily identified. Among the multi-lepton searches for
-Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$ have the best reach, due to the relatively high production cross-section of
+Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$, with $\ell=e, \ \mu$,  have the best reach, due to the relatively high production cross-section of
 chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
-and QCD backgrounds obtained by requiring three leptons.   The cross sections for trilepton process can be find in Table~\ref{tab:xsections}. Multilepton searches
+and QCD backgrounds obtained by requiring three leptons.
+Higgsino NLSPs can be excluded at 95\% C.L.
+with mass up to 2.85 TeV or be discovered with  mass up to 1.8 TeV, for massless Bino LSP.
+The reach reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
+Multilepton searches
 with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
-due to the lower pair-production cross-section of neutral Higgsinos, combined
+due to the smaller pair-production cross-section of neutral Higgsinos, combined
 with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
@@
     \toprule
-    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{2}$ & $\N_2\N_3$\\
+    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{1}$ & $\N_2\N_3$\\
     \midrule
@@
     Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
-    Applying \emph{BR}$(W\rightarrow l\nu)$, \emph{BR}$(Z\rightarrow ll)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
+    Applying \emph{BR}$(W\rightarrow \ell\nu)$, \emph{BR}$(Z\rightarrow \ell\ell)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
     \bottomrule
   \end{tabular}
-  \caption{Comparison of cross-sections for
-    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{2})$ and
+  \caption{Comparison of Higgsino pair production cross-sections for
+    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
     $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
-    TeV \emph{pp} collider . The pair-production cross sections are taken from
+    TeV \emph{pp} collider. The pair-production cross sections are taken from
     \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
     evaluated in the limit where the Goldstone equivalence theorem applies, so
-    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_{1}^0)\approx$
-    BR$(\widetilde{\chi}_{2,3}^0\rightarrow\widetilde{\chi}_1^0)\approx 50\% $,
+    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow Z \widetilde{ \chi}_{1}^0)\approx$
+    BR$(\widetilde{\chi}_{2,3}^0\rightarrow h\widetilde{\chi}_1^0)\approx 50\% $ for massless $\widetilde{\chi}_{1}^0)$, 
     and the branching ratios to the SM final states are taken from
-    \citep{Olive:2016xmw}. \ap{In this scenario, the LSP is assumed to be
-    massless}.
-    \Shufang{Specify M1 as well and use the actual Br.} \Adarsh{I added a line
-  specifying that the LSP is massless. As for the actual BR, I assume you mean
+    \citep{Olive:2016xmw}.  
+    \Shufang{use the actual Br.} \Adarsh{As for the actual BR, I assume you mean
   calculate it using SUSY-HIT? That'll take a bit more time, but I'll try to
-  get it.}\Shufang{rewrite the entry.  Why chi2pm? Should not it be chi1pm?}}
-  \Adarsh{$\chi_1$ is the LSP, right? In our case it's the bino, which is not
-  charged...}
+  get it.} \Shufang{You can read the number out from right panel of Fig. 2.} }
   \label{tab:xsections}
@@
 
-In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production
-cross section for the Higgsino-like NLSPs.  The cross section varies between
+In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section $\widetilde\chi_2^0\widetilde\chi_3^0$ for the Higgsino-like NLSPs.  The cross section varies between
 200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
@@
   \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
-  \caption{Higgsino pair production cross section, as a function of $|\mu|$. The
-  cross-sections are calculated using Prospino2, with $M_1 = 25$ GeV. However, it
-  should be noted that the dependence on $M_1$ is very weak.  
-  \Shufang{Could you make the two plot same aspect ratios?}}
-  \Adarsh{It would be pretty time consuming to do, so I would rather not if
-    it's not essential - I think it might look better to put the plots in
-  separate figures.}
+  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$ cross section (left panel), calculated using Prospino2~\citep{Beenakker:1999xh},  and decay decay branching fractions (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function of $\mu$ for $M_1=25$ GeV.
+However, it
+  should be noted that the dependence on $M_1$ is very weak.   \Shufang{How about Br? What's the vcalue of M1 used?}\\
+  \Shufang{Could you make the two plot same aspect ratios?
+Using plot digitizer.
+Also, for ylabel in left panel, the tilde should not go above 0.
+Just above $\chi$.
+Is there way to change the xlabel of right panel to be $\mu$ instead of $|\mu|$?
+Need to be consistent with the xlabels.}}
   \label{fig:xsection_plot}
@@
 that  the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the
-LSP 100\% of the time.  \Shufang{But this is not the same as our Higgsino NLSP
-  and Bino LSP case.} \Adarsh{True, but there have been no experimental
-  searches for Higgsino NLSP - Bino LSP. This seemed like the most similar
-channel/topology to ours.}
+LSP 100\% of the time.
 
@@
 GeV are excluded using a search channel with a final state containing at least
-three \emph{b}-jets. \Shufang{you mean more than 3 b jets?} \Adarsh{At least 3 -
-I've reworded to clarify.} The CMS analysis
+three \emph{b}-jets.  \Shufang{Check the ref.  The mass windows seem a bit weird.  Is one for Higgsino and the other one for Bino?}  The CMS analysis
 in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
-$4b+\slashed{E}_T, 2l + 2j + \slashed{E}_T, 3l/4l + \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
-to exclude Higgsino-like neutralino masses up to 650-750 GeV, depending on the assumed branching 
-fraction of the neutralino decays. Finally, the $4l$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
+$4b+\slashed{E}_T, 2\ell + 2j + \slashed{E}_T, 3\ell/4\ell+ \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
+to exclude Higgsino-like neutralino masses up to 650 $-$ 750 GeV, depending on the assumed branching 
+fraction of the neutralino decays. Finally, the $4\ell$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
 to set a lower bound of 295 GeV on the Higgsino mass  \cite{Aaboud:2018zeb}.
-\Shufang{So the only available limit is with gravitino LSP?  Then it does not apply.}
-\Shufang{There is no  WZ+MET limit on Higgsinos NLSP?} \Adarsh{Yes, that is the
-only available limit with neutral Higgsino NLSPs and bino LSP, and with
-on-shell W and Z. WZ+MET limits (with on-shell W and Z). Should I remove the
-sentences with the gravitino LSP?}.
+\Shufang{Check, finalize}
 
@@
 parameter set to 40 GeV. The Higgsino pair production cross sections were
-calculated using \texttt{Prospino2} \citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
-Wino, we set its mass parameter $M_2$ to 5 TeV. \Shufang{5 TeV was used for
-another calculation earlier. Be consistent here.}
+calculated using \texttt{Prospino2}~\citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
+Wino, we set its mass parameter $M_2$ to 5 TeV.
 
@@
 a minimum $\met$ of 100 GeV at the parton level for the backgrounds as
-well.
+well.  \Shufang{This is only for BG, right?  No such cuts are imposed for signal generation?}
 
@@
 The value of 0.05 is consistent with what is suggested in previous 100 TeV
-studies (\citep{Acharya:2014pua,Gori:2014oua,Bramante:2014tba}) and will allow
+studies~\citep{Acharya:2014pua,Gori:2014oua,Bramante:2014tba} and will allow
 for easier comparison between different search strategies.
@@
   \item \emph{Trigger}: Events were selected if they had at least one lepton
-    with $p_{T}^\ell >$ 100 GeV.  \Shufang{This is quite a high trigger level
-    cut.  Is the 100 TeV lepton trigger need such a high pT? or it is a lower
-  pT trigger, with a 100 GeV advanced cut to suppress the bg?} \Adarsh{I had it
-at 20 GeV earlier, but Ken Johns (and maybe you?) told me that that would be
-far too low for a 100 TeV collider. Also, this is consistent with the analysis
-in \cite{Gori:2014oua}.}
+    with $p_{T}^\ell >$ 100 GeV.
 
@@
 
-  \item \emph{Invariant mass of h-candidate:} $75\ {\rm GeV}<m_{bb}<150\ {\rm GeV}$ for two leaving $b$-jets.
+  \item \emph{Invariant mass of h-candidate:} $75\ {\rm GeV}<m_{bb}<150\ {\rm GeV}$ for two leading $b$-jets.
 
@@
 \begin{align}
-M_R &=& \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
-M_T^R &=& \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
+M_R &= \sqrt{(E_Z+E_h)^2 - (p_Z^z + p_h^z)^2},\\
+M_T^R &= \sqrt{\frac{1}{2}\left[\slashed{E}_T(|\vec{p}_{ZT}|+|\vec{p}_{hT}|)
 - \vec{\slashed{E}}_T\cdot(\vec{p}_{ZT}+\vec{p}_{hT})\right]}
 \end{align}
- for$E_{Z,h}$ and $p_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$.
- \Shufang{Check the formula.  Unit is not correct.} \Adarsh{Fixed.}
+ for $E_{Z,h}$ and $\vec{p}_{Z,h}$ being the reconstructed energy and momentum for $Z$ and $h$, respectively.
       Representative kinematic
@@
   shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification, and
-  $\slashed{E}_{T}$ cuts. The
+  $\slashed{E}_{T}$ cuts.  \Shufang{How about mll cut? BG is generated with mll cut.}  The
   distribution for the \emph{bbWW} background is not shown, since it is negligible in
   comparison to the others.   We can see that the distribution of $M_R$ is peaked
-  around 1 TeV for the signal, which consistent with what we would expect, since
-  it corresponds to the mass difference between the NLSP and LSP.  For this mass combination, requiring $M_R >$ 800
+  around 1 TeV for the signal, which is consistent with what we would expect as   it corresponds to the mass difference between the NLSP and LSP.
+The $tt$ background peaks around 500 GeV, while the distribution of $tbW$ background almost overlaps with that of the signal process.
+Similar behaviour also appears for $M_T^R$ distributions.
+  For this mass combination, requiring $M_R >$ 800
   GeV and $M_T^R >$ 400 GeV yields the greatest significance.
@@
   \input{tables/cutflowtable.tex}
-  \caption{Representative cut flow table for the benchmark point $|\mu|=1$ TeV,
-    $M_1 = 25$ GeV, for a traditional cut-and-count analysis. All cross sections
-    are given in femtobarns, and the units for the missing energy, invariant
+  \caption{Representative cut flow table for the benchmark point $\mu=1$ TeV,
+    $M_1 = 25$ GeV at 100  TeV $pp$ collider, for a traditional cut-and-count analysis. All cross sections
+    are given in unit of fb, and the units for the missing energy, invariant
     mass, and razor variable cuts are GeV. The significance, $S/\sqrt{B}$, is
@@
 Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
-signal benchmark point with a $|\mu| =$ 1 TeV and $M_1$ = 25 GeV.   The
-cross-sections of the backgrounds are \Shufang{What do you mean by average?}
-\Adarsh{I reworded it.}
-\ap{obtained from} MadEvent after performing the MLM matching procedure. Their small size reflects
+signal benchmark point with a $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
+cross-sections of the backgrounds are obtained from MadEvent after performing the MLM matching procedure. Their small size reflects
 the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
@@
 maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
-of 3000 fb$^{-1}$), shown in the last column.  \Shufang{For the reach plot,
-does razor variable cut value changes for each grid point?} \Adarsh{Yes, for
-the rectangular cuts analysis.}
+of 3000 fb$^{-1}$), shown in the last column.
 
@@
 $m_{\ell\ell}$, $m_{bb}$, $M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic
-transverse energy $THT$, \Shufang{THT?} \Adarsh{Should I use some different
-notation? Maybe $H_T$?} and transverse momenta of individual final state
+transverse energy $H_T$,   and transverse momenta of individual final state
 leptons and $b$-quarks: $p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We
-then divided the events into training and test sets, with the training set
-comprising 75\% of signal events and 30\% of background events. \Shufang{You
-mean 70\% of all signal event generated?} \Adarsh{Yes.} We used the
+then divided the generated events into training and test sets, with the training set
+comprising 75\% of signal events and 30\% of background events.  We used the
 \texttt{scikit-learn} package  \citep{Pedregosa2011} to implement our analysis.
 A boosted decision tree classifier was trained with 1000 weak learners and a
-learning rate of 0.025. \Shufang{We probably don't need this details.}
-\Adarsh{I would like to keep it, for the sake of reproducibility (and for
-future researchers to compare their ML-based methods to ours).}
+learning rate of 0.025.  
 After the classifier is trained, we use it to assign
@@
 cut is chosen to maximize the significance for each signal benchmark point. The
-distribution of scores for the specific benchmark point ($|\mu|$ = 1 TeV, $M_1$
+distribution of scores for the specific benchmark point ($\mu$ = 1 TeV, $M_1$
 = 25 GeV) is shown in figure \ref{fig:bdt_response}. We observe that there is an
@@
 \caption{Distribution of the decision function of the gradient boosted decision
-tree classifier algorithm for signal ($|\mu| = 1$ TeV $M_1 = 25$ and
+tree classifier algorithm for signal ($\mu = 1$ TeV, $M_1 = 25$ GeV) and
 backgrounds. }
@@
     \ref{tab:cc_cutflowtable}. As before, all the cross sections are in
-  fb.  }
+  fb.  \Shufang{Fix the table.}}
 \label{tab:bdt_cutflowtable}
@@
 significance we can achieve goes up from 2.4 to 8.4, a roughly four-fold
-increase.  \Shufang{Do we still require 5 signal events minimum here?}
-\Adarsh{Actually, we do a minimum of three events - more consistent with
-Poisson statistics. I've updated the previous mention of 5 events.}
+increase.
 
@@
   for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
-\Shufang{Shall we show the lepton search result in this figure for comparison?}
-\Adarsh{You mean the results from \cite{Gori:2014oua}? That sounds pretty
-difficult to do...}
+\Shufang{Can we change the xlabel of all plots to $\mu$ instead of $|\mu|$ or it is difficult to do?}\\  \Shufang{Did you save the data for this plot?
+It is actually not difficult to overlay ref 10 results.
+They only have a few data points and can easily be read out using plot-digitizer.
+By comparison, we can see that our reach is better for large M1 region.}
 }
@@
 
-Fig.~\ref{fig:contours} shows the expected reach in parameter space for 95\%
-C.L. exclusion and 5$\sigma$ discovery in the parameter space of $|\mu|$ vs.
+Fig.~\ref{fig:contours} shows the expected reach  for 95\%
+C.L. exclusion and 5$\sigma$ discovery in the parameter space of $\mu$ vs.
 $M_1$ for 100 TeV $pp$ collider with an integrated luminosity of 3000
 fb$^{-1}$. The cut-and-count strategy is able to discover Higgsinos up to 750
-GeV  and exclude them up to 1.3 TeV. \Shufang{How do you read out the numbers?}
-\Adarsh{I am just looking at the plot and estimating the approximate boundaries
-of the curves..}  The boosted decision tree analysis, improves this reach - it
+GeV  and exclude them up to 1.3 TeV. \Shufang{Cross check the numbbers. Not entirely consistent with the plot.}    The boosted decision tree analysis, improves this reach -- it
 is able to discover Higgsinos up to 1.3 TeV, and exclude them up to 1.8 TeV in
@@
 
-This improvement is substantial, but perhaps not spectacular. However, it should
+Comparing to the reach of multi-lepton channel in Ref.~\citep{Gori:2014oua}, with an  exclusion limit of Higgsino mass up to 2.85 TeV or a discovery reach of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$ channel in our study is less.
+However, the reach for multi-lepton channel reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
+The BDT reach for $Zh+\met$ exceeds that analyses by about 300 GeV.
+
+Comparing the BDT results with that of the cut-bases anayses, the improvement is substantial, but perhaps not spectacular. However, it should
 be kept in mind that this is probably a conservative estimate. Since we reserve
-30\% of the data for training purposes, and impose the condition that the
-minimum number of MC events after cuts for the backgrounds must be 3 (see note
-at the end of subsection \ref{subsec:bdt}), the true rate of background
+30\% of the background data for training purposes, and impose the condition that the
+minimum number of MC events after cuts for the backgrounds must be 3, the true rate of background
 rejection by the classifier is likely underestimated, and the expected
@@
 expect as a result of applying the $b$-tagging efficiency of about 85\%
-specified in our \texttt{Delphes} card.  \Shufang{How do you get the 28\%
-number? } \Adarsh{$(1 - 0.85^2)*100 = 27.75 \approx 28$.}
-
-\Adarsh{I removed the table as you suggested.}
+specified in our \texttt{Delphes} card.
 
@@
 pair-produced heavy Higgsinos with Bino LSP, via 
-intermediate $Z$ and $h$ bosons that decay to a pair of leptons and $b$ quarks
-respectively.
+intermediate $Z$ and $h$ bosons that decay to a pair of leptons and $b$ quarks respectively:  $\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
 
@@
 Overall, we find that the reach of our analysis strategy is a significant
-improvement over that of the LHC.  \Shufang{Did we mention the LHC reach?}
-\Adarsh{I was referring to the reach for the gravitino LSP analysis - should I
-remove that?}  We found that the rectangular cut strategy has
+improvement over that of the LHC.    We found that the rectangular cut strategy has
 the potential to discover Higgsino LSPs up to a mass of 750 GeV, and exclude
@@
 process, we highlighted the importance of generating enough Monte Carlo events
-to estimate the huge backgrounds at a 100 TeV $pp$ collider.
+to estimate the huge backgrounds at a 100 TeV $pp$ collider.  \Shufang{Update the numbers.}
 
@@
 detector effects using Delphes, result in a lower reach in the high $|\mu|$, low
-$M_1$ region than the multilepton analysis in \citep{Gori:2014oua}, which is
-able to exclude Higgsinos up to a mass of 2.9 TeV for massless binos. The reach
-of our analysis is slightly higher in the region where the difference between
+$M_1$ region than the multilepton analysis in~\citep{Gori:2014oua}, which is
+able to exclude Higgsinos up to a mass of 2.85 TeV for massless Binos, or discover Higgsinos up to a mass of 1.8 TeV.   The reach
+of our analysis, however,  is higher in the region where the difference between
 $|\mu|$ and $M_1$ is smaller. This is consistent with our usage of the razor

### 2019-07-19 images/xsection_plot.py
Updated branching ratio plot

@@ -1,0 +1,39 @@
+from tqdm import tqdm
+from myProcesses import signals
+import matplotlib
+matplotlib.rc('font', size = 10)
+matplotlib.rc('text', usetex=True)
+import numpy as np
+import matplotlib.pyplot as plt
+# For dissertation
+# pgf_with_rc_fonts = {
+    # "font.family": "serif",
+    # # "font.serif": ,
+# }
+
+# matplotlib.rcParams.update(pgf_with_rc_fonts)
+
+def figsize(scale):
+    fig_width_pt = 281.0
+    inches_per_pt = 1.0/72.27
+    golden_mean = (np.sqrt(5.0)-1.0)/2.0
+    fig_width = fig_width_pt*inches_per_pt
+    fig_height = fig_width*golden_mean
+    fig_size = [fig_width, fig_width]
+    # fig_size = [1.9,1.9]
+    return fig_size
+
+# plt.style.use('ggplot')
+plt.figure(figsize=figsize(1.0))
+
+signals = [signal for signal in signals if signal.mB == 25.0]
+x = [signal.mH for signal in tqdm(signals)]
+y = [1000.*signal.get_pair_prod_xsection() for signal in tqdm(signals)]
+plt.ylabel(r'$\sigma(pp\rightarrow\widetilde{\chi_2^0}\widetilde{\chi_3^0})$ $\mathrm{(fb)}$',fontsize = 8)
+plt.xlabel(r'$\mu$ $\mathrm{(GeV)}$',fontsize = 8)
+plt.xlim(500,2500)
+plt.ylim(0.1,1000)
+plt.semilogy(x,y, color='maroon')
+plt.tight_layout()
+# plt.savefig('images/xsection_plot.pgf')
+plt.savefig('images/xsection_plot.pdf')

### 2019-07-19 main.tex

@@
   $b$-quarks respectively: $\N_{2}\N_{3}
-  \rightarrow (Z\N)(h\N)\rightarrow 
-  bbll+\N\N$. In addition, we examine 
+  \rightarrow (Z\N_1)(h\N_1)\rightarrow 
+  bb\ell\ell+\N_1\N_1$. In addition, we examine 
   the potential for machine learning techniques to boost the power of 
@@
   Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
-  to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially at large LSP mass region. \Shufang{Update the numbers.}
+  to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially in the region where the mass difference between
+Higgsino NLSP and LSP is smaller. \Shufang{Update the numbers.}
 }
@@
 for each SM particle\footnote{For a detailed review of the MSSM, see 
-Ref. \citep{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the 
+Ref. \cite{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the 
 lightest supersymmetric partner (LSP) is predicted to be absolutely 
@@
 considerations, the lightest of the  MSSM particles known as the 
-neutralinos emerges as the most attractive candidates for the LSP \citep{Bertone:2004pz}.
+neutralinos emerges as the most attractive candidates for the LSP \cite{Bertone:2004pz}.
 
@@
 A compelling alternative scenario comes in the form of
-split supersymmetry (split SUSY) \citep{Wells:2003tf,
+split supersymmetry (split SUSY) \cite{Wells:2003tf,
 ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
@@
 known as electroweakinos), and gluinos. The current LHC search limits on
-gluinos are already around 2.4 TeV~\cite{CMS-PAS-SUS-19-005}. \Adarsh{Should
-2460 GeV be rounded up to 2.5 TeV or down to 2.4 TeV to be conservative? Also,
-this limit is from the disappearing track search - does that apply for us?
-Update - disappearing tracks not relevant, use the regular channel} \Shufang{Actually on a second thought, in split SUSY with heavy squarks, is the gluino lifetime long enough to leave displaced vertex at detectors?
-Check pheno of split SUSY paper.
-If still decay promptly, then use searches with off-shell squark.} The
-limits on electroweakinos,
-howeer, are still relatively weak: around 0.3 $-$ 1.1 
-TeV~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae}, depending on
-the decay modes of the parent electroweakinos.  \Shufang{add ref for 
-electroweakino limits.  Again, for searches with heavy squark/sleptons.} In this paper, we will
+gluinos are already around 2 TeV for prompt decay and 2.46 TeV for disappearing track searches~\cite{CMS-PAS-SUS-19-005}.   The
+limits on electroweakinos with heavy scalar superparticles,
+however, are still relatively weak: around 650 $-$ 750 GeV or  less~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}, depending on
+the decay modes of the parent electroweakinos and their species.  In this paper, we will
 focus on the discovery potential of the neutralinos and charginos at the 100
@@
 The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos)
-depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $|\mu|$, which 
-roughly determine the masses of the Bino, Winos, and Higgsinos, respectively~\citep{Han:2013kz}. 
-In this paper, we consider the Higgsino next-to-LSP (NLSP) and Bino LSP scenario with $M_1 < |\mu| \ll M_2$.
+depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $\mu$~\footnote{For our study, we assume all the mass parameters are positive.
+For the current analyses, the results do not depend much on the sign of those parameters.}, which
+roughly determine the masses of the Bino, Winos, and Higgsinos, respectively~\cite{Han:2013kza}. 
+In this paper, we consider the Higgsino NLSP and Bino LSP scenario with $M_1 < \mu \ll M_2$.
 One of the motivations for studying Higgsinos is that the parameter $\mu$ 
-that governs its mass plays an important role in electroweak symmetry breaking~\citep{Acharya:2014pua}, which tends to be small by naturalness considerations.
+that governs its mass plays an important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, which tends to be small by naturalness considerations.
 Finding Higgsinos has traditionally been more challenging
@@
 Higgsino NLPs with a Bino LSP  via  multi-lepton final states have been
-studied in Ref.~\cite{Gori:2014oua} for 100 TeV $pp$ collider, for pair production of $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm$ and  $\widetilde\chi_{1}^+\widetilde\chi_1^-$.
+studied in Ref.~\cite{Gori:2014oua} at a 100 TeV $pp$ collider, for pair production of $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm$ and  $\widetilde\chi_{1}^+\widetilde\chi_1^-$.
 In this paper, we attempt to exploit the relatively high branching
@@
 most interesting regions of the split SUSY parameter space
-\citep{Arkani-Hamed:2015vfh}.
+\cite{Arkani-Hamed:2015vfh}.
 % Status of 100 TeV planning
@@
 actively discussed in the particle physics community, with two major
-proposals being the Future Circular Collider (FCC)-hh by CERN \citep{FCC-hh}, and the Super Proton Proton Collider (SppC)  
-in China \citep{CEPC}.  As the next energy frontier machine, it is of 
+proposals being the Future Circular Collider (FCC)-hh by CERN \cite{FCC-hh}, and the Super Proton Proton Collider (SppC)  
+in China \cite{CEPC}.  As the next energy frontier machine, it is of 
 crucial importance to fully explore the physics potential of a 100 TeV $pp$
 collider, especially for new particles that are either too heavy or too rare 
-to be produced at the LHC~\citep{Arkani-Hamed:2015vfh,Contino:2016spe,Golling:2016gvc,Mangano:2016jyj}.
+to be produced at the LHC~\cite{Arkani-Hamed:2015vfh,Contino:2016spe,Golling:2016gvc,Mangano:2016jyj}.
 In particular, studies have already been performed on the prospects of
@@
 
-In our study, we use razor variables~\citep{Rogan:2010kb}, which were originally designed
+In our study, we use razor variables~\cite{Rogan:2010kb}, which were originally designed
 for searches involving two heavy, mass-degenerate pair-produced
@@
 SM Higgs boson in 2012 was done with the help of neural networks
-\citep{Aad:2012tfa} and boosted decision trees (BDT)
-\citep{Chatrchyan:2012xdj}.
+\cite{Aad:2012tfa} and boosted decision trees (BDT)
+\cite{Chatrchyan:2012xdj}.
 
@@
 
-The optimal search strategy for finding electroweakinos is highly dependent on
-the their mass spectrums \citep{Han:2013kza}.  Phenomenological collider studies on finding
-Electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
-found in \citep{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
+The optimal search strategy for finding electroweakinos   highly depends on
+  their mass spectrums \cite{Han:2013kza}.  Phenomenological collider studies on finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
+found in \cite{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
 \Shufang{Say a few words about typical search strategy there.} \Adarsh{I
@@
 to your comment ... let me know if I should add more details.}. \Shufang{What you said below is for well separated spectra, not for mass spitting of 0.1 to 50 GeV.}
-Well-separated spectra have been studied in \citep{Gori:2014oua,
+Well-separated spectra have been studied in \cite{Gori:2014oua,
 Acharya:2014pua} using
@@
 $\widetilde{\chi}_1^0$ is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$ or scalar $h$.  These searches work well since
-the large mass difference between the Electroweakinos can lead to energetic
+the large mass difference between the electroweakinos can lead to energetic
 leptons that can be easily identified. Among the multi-lepton searches for
@@
 multilepton searches, the channel with \emph{Zh} (originally suggested in
-\citep{Han:2013kza}) as the intermediate dibosons emerges as a possible
+\cite{Han:2013kza}) as the intermediate dibosons emerges as a possible
 competitor to the \emph{WZ} channel.
@@
     $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
-    $(\N_{2}\N_{3})$, for $|\mu|\approx 1$ TeV, at a 100
+    $(\N_{2}\N_{3})$, for $\mu\approx 1$ TeV, at a 100
     TeV \emph{pp} collider. The pair-production cross sections are taken from
-    \citep{Gori:2014oua}. The branching ratio to intermediate dibosons is
+    \cite{Gori:2014oua}. The branching ratio to intermediate dibosons is
     evaluated in the limit where the Goldstone equivalence theorem applies, so
@@
     and the branching ratios to the SM final states are taken from
-    \citep{Olive:2016xmw}.  
+    \cite{Olive:2016xmw}.  
     \Shufang{use the actual Br.} \Adarsh{As for the actual BR, I assume you mean
@@
 
-For pair produced Higgsinos $\tilde\chi_2^0\tilde\chi_3^0$ in a scenario with
+For pair produced Higgsinos $\widetilde\chi_2^0\widetilde\chi_3^0$ in a scenario with
 decoupled Winos and  sfermions, the \emph{Zh} mode has the greatest
@@
   \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
-  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$ cross section (left panel), calculated using Prospino2~\citep{Beenakker:1999xh},  and decay decay branching fractions (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function of $\mu$ for $M_1=25$ GeV.
+  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$ cross section (left panel), calculated using Prospino2~\cite{Beenakker:1999xh},  and decay decay branching fractions (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function of $\mu$ for $M_1=25$ GeV.
 However, it
@@
 Searches for pair produced nearly mass-degenerate Higgsinos  have been
-performed at ATLAS and CMS for various decay  topologies. While the identity of
-the LSP in these searches is a gravitino  instead of a Bino,   the limits are
-still  relevant, since both  our analysis  and the experimental ones consider
-that  the neutral Higgsinos decay to a  neutral SM boson (\emph{h/Z})  and the
-LSP 100\% of the time.
-
-The most stringent limits are obtained by ATLAS in \cite{Aaboud:2018htj},
-where Higgsinos with masses between 130 and 230 GeV and between 290 and 880 
-GeV are excluded using a search channel with a final state containing at least
-three \emph{b}-jets.  \Shufang{Check the ref.  The mass windows seem a bit weird.  Is one for Higgsino and the other one for Bino?}  The CMS analysis
-in \cite{Sirunyan:2017ubx} which uses a combination of channels and final states 
-$4b+\slashed{E}_T, 2\ell + 2j + \slashed{E}_T, 3\ell/4\ell+ \slashed{E}_T$ and $2\gamma+\slashed{E}_T$ 
-to exclude Higgsino-like neutralino masses up to 650 $-$ 750 GeV, depending on the assumed branching 
-fraction of the neutralino decays. Finally, the $4\ell$ final state has been studied by ATLAS in \cite{Aaboud:2018zeb}
-to set a lower bound of 295 GeV on the Higgsino mass  \cite{Aaboud:2018zeb}.
-\Shufang{Check, finalize}
+performed at ATLAS and CMS for various decay  topologies\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.
+For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\% C.L.
+exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$ and an equal mixture of $WZ+WH$ topology, with the most stringest limits from the multi-lepton searches.
+For neutralino pair production with $ZZ$, $ZH$ and $HH$ topologies~\footnote{While such searches assume gravitino LSP with Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or multi-$b$ jets searches, depending on the decay branching fractions of Higgsino NLSP.
 
@@
 final state are described in
-\citep{Aaboud:2018sua,Aaboud:2018jiw, ATLAS:2016uwq,Khachatryan:2014qwa,Chatrchyan:2012pka}, assuming a
+\cite{Aaboud:2018sua,Aaboud:2018jiw, ATLAS:2016uwq,Khachatryan:2014qwa,Chatrchyan:2012pka}, assuming a
 wino-like NLSP and a bino-like LSP. The best reach is obtained in the $2/3l$
 channel by ATLAS with 36.1 fb$^{-1}$ of data, with NLSP masses up to 600 GeV
-excluded for massless LSPs \citep{Aaboud:2018sua}.
+excluded for massless LSPs \cite{Aaboud:2018sua}.
 
@@
 %Topologies with one or two hadronically-decaying tau leptons and missing energy
-%in the final state have been studied in \citep{ATLAS:2016ety,
+%in the final state have been studied in \cite{ATLAS:2016ety,
 %Khachatryan:2016trj}, with the greatest reach obtained by ATLAS in
-%\citep{ATLAS:2016ety}, using 13 TeV data - they are able to exclude wino-like
+%\cite{ATLAS:2016ety}, using 13 TeV data - they are able to exclude wino-like
 %NLSPs up to a mass of 700 GeV for a massless bino-like LSP.
@@
 Searches with a combination of leptons and jets in the final states can be found
-in \citep{Aad:2014vma,Khachatryan:2015kxa,Khachatryan:2014mma}. Winos up to 465
-GeV are excluded in the $2l + 0/2j$ final states in \citep{Aad:2014vma}. A
-compressed mass spectrum is studied in \citep{Khachatryan:2015kxa}, with a mass
+in \cite{Aad:2014vma,Khachatryan:2015kxa,Khachatryan:2014mma}. Winos up to 465
+GeV are excluded in the $2l + 0/2j$ final states in \cite{Aad:2014vma}. A
+compressed mass spectrum is studied in \cite{Khachatryan:2015kxa}, with a mass
 difference of about 50 GeV between winos and binos. This study uses the vector
@@
 excludes winos up to a mass of 170 GeV. Of particular interest to us is the
-analysis in \citep{Khachatryan:2014mma}, where higgsinos can be excluded up to a
+analysis in \cite{Khachatryan:2014mma}, where higgsinos can be excluded up to a
 mass of 380 GeV using the $bbll + \slashed{E}_T$ final state, but cannot be
@@
 We simulated parton-level events using \texttt{MadGraph5 v2.3.2.2} and
-\texttt{MadEvent} \citep{Alwall:2014hca}, then passed those events to Pythia 6
-\citep{Sjostrand:2006za} for showering and hadronization. Finally, we used
-\texttt{Delphes 3} \citep{deFavereau:2013fsa} to perform a fast, parametrized
+\texttt{MadEvent} \cite{Alwall:2014hca}, then passed those events to Pythia 6
+\cite{Sjostrand:2006za} for showering and hadronization. Finally, we used
+\texttt{Delphes 3} \cite{deFavereau:2013fsa} to perform a fast, parametrized
 detector simulation, with the detector card devised by the FCC-hh working
@@
 parameter set to 40 GeV. The Higgsino pair production cross sections were
-calculated using \texttt{Prospino2}~\citep{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
+calculated using \texttt{Prospino2}~\cite{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
 Wino, we set its mass parameter $M_2$ to 5 TeV.
@@
 The value of 0.05 is consistent with what is suggested in previous 100 TeV
-studies~\citep{Acharya:2014pua,Gori:2014oua,Bramante:2014tba} and will allow
+studies~\cite{Acharya:2014pua,Gori:2014oua,Bramante:2014tba} and will allow
 for easier comparison between different search strategies.
@@
 on the variables listed below, using the MadAnalysis 5 package
-\citep{Conte:2012fm}.
+\cite{Conte:2012fm}.
 
@@
     mass, and razor variable cuts are GeV. The significance, $S/\sqrt{B}$, is
-    calculated for an integrated luminosity of 3 ab$^{-1}$.    }
+    calculated for an integrated luminosity of 3 ab$^{-1}$.   \Shufang{MET $>$ 400 or $<$ 400? }}
 \label{tab:cc_cutflowtable}
@@
 events that passed the lepton trigger, contained two SFOS leptons and two
-$b$-tagged jets, and calculated a number of kinematic variables for each event. We then
+$b$-tagged jets, and calculated a number of kinematic variables for each event. \Shufang{Again, generator level MET, mll cut for the BG?} We then
 placed these kinematic variables in an array, with each row corresponding to an event, and
@@
 comprising 75\% of signal events and 30\% of background events.  We used the
-\texttt{scikit-learn} package  \citep{Pedregosa2011} to implement our analysis.
+\texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
 A boosted decision tree classifier was trained with 1000 weak learners and a
@@
     \ref{tab:cc_cutflowtable}. As before, all the cross sections are in
-  fb.  \Shufang{Fix the table.}}
+  fb.  }
 \label{tab:bdt_cutflowtable}
@@
 They only have a few data points and can easily be read out using plot-digitizer.
-By comparison, we can see that our reach is better for large M1 region.}
+By comparison, we can clearly see that our reach is better for large M1 region.}
 }
@@
 
-Comparing to the reach of multi-lepton channel in Ref.~\citep{Gori:2014oua}, with an  exclusion limit of Higgsino mass up to 2.85 TeV or a discovery reach of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$ channel in our study is less.
-However, the reach for multi-lepton channel reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
-The BDT reach for $Zh+\met$ exceeds that analyses by about 300 GeV.
-
 Comparing the BDT results with that of the cut-bases anayses, the improvement is substantial, but perhaps not spectacular. However, it should
@@
 In regions with large mass differences between the LSP and NLSP, the reach is
-not as good, since the intermediate SM Higgs boson will be highly boosted, and
+reduced.  This is because the intermediate SM Higgs boson will be highly boosted, and
 thus decay into a highly collimated pair of $b$-jets. The extent to which this
@@
 specified in our \texttt{Delphes} card.
+
+ Comparing to the reach of multi-lepton channel in Ref.~\cite{Gori:2014oua}, with an  exclusion limit of Higgsino mass up to 2.85 TeV or a discovery reach of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$ channel in our study is less.
+However, the reach for multi-lepton channel reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
+The reach for $Zh+\met$ search in our study exceed that of the multi-lepton search for larger LSP masses.
+In particular,
+ the BDT reach for LSP mass with $Zh+\met$ search exceeds the reach for multi-lepton analyses by about 300 GeV.
 
@@
 Additionally, we found that the reach for both strategies is considerably
-reduced when the difference $ |\mu|-M_1$ is high, since it results in a highly
-boosted $h$ that decays to a collimated pair of $b$'s that will most likely be
+reduced when the difference $ \mu-M_1$ is high, since it results in a highly
+boosted $h$ that decays to a collimated pair of $b$ jets that will most likely be
 identified as a single jet. This is not an insurmountable difficulty - there are
@@
 highly boosted/collimated decay products. For a review of currently used methods
-to determine jet substructure, see \citep{Shelton:2013an}. In the future,
+to determine jet substructure, see \cite{Shelton:2013an}. In the future,
 machine learning techniques might be profitably applied to this area as well -
-for a review of developments along this line, see \citep{Schwartzman:2016jqu}.
+for a review of developments along this line, see \cite{Schwartzman:2016jqu}.
 
-The collimation of the $b$-jets, along with the fact that we take into account
-detector effects using Delphes, result in a lower reach in the high $|\mu|$, low
-$M_1$ region than the multilepton analysis in~\citep{Gori:2014oua}, which is
+The collimation of the $b$ jets, along with the fact that we take into account
+detector effects using Delphes, result in a relatively lower reach in the high $\mu$, low
+$M_1$ region than the multilepton analysis in~\cite{Gori:2014oua}, which is
 able to exclude Higgsinos up to a mass of 2.85 TeV for massless Binos, or discover Higgsinos up to a mass of 1.8 TeV.   The reach
 of our analysis, however,  is higher in the region where the difference between
-$|\mu|$ and $M_1$ is smaller. This is consistent with our usage of the razor
+$\mu$ and $M_1$ is smaller. This is consistent with our usage of the razor
 variable $M_R$, which is sensitive to the mass difference between the parent

### 2019-07-19 images/xsection_plot.py
removing accidentally added python script

@@ -1,39 +1,0 @@
-from tqdm import tqdm
-from myProcesses import signals
-import matplotlib
-matplotlib.rc('font', size = 10)
-matplotlib.rc('text', usetex=True)
-import numpy as np
-import matplotlib.pyplot as plt
-# For dissertation
-# pgf_with_rc_fonts = {
-    # "font.family": "serif",
-    # # "font.serif": ,
-# }
-
-# matplotlib.rcParams.update(pgf_with_rc_fonts)
-
-def figsize(scale):
-    fig_width_pt = 281.0
-    inches_per_pt = 1.0/72.27
-    golden_mean = (np.sqrt(5.0)-1.0)/2.0
-    fig_width = fig_width_pt*inches_per_pt
-    fig_height = fig_width*golden_mean
-    fig_size = [fig_width, fig_width]
-    # fig_size = [1.9,1.9]
-    return fig_size
-
-# plt.style.use('ggplot')
-plt.figure(figsize=figsize(1.0))
-
-signals = [signal for signal in signals if signal.mB == 25.0]
-x = [signal.mH for signal in tqdm(signals)]
-y = [1000.*signal.get_pair_prod_xsection() for signal in tqdm(signals)]
-plt.ylabel(r'$\sigma(pp\rightarrow\widetilde{\chi_2^0}\widetilde{\chi_3^0})$ $\mathrm{(fb)}$',fontsize = 8)
-plt.xlabel(r'$\mu$ $\mathrm{(GeV)}$',fontsize = 8)
-plt.xlim(500,2500)
-plt.ylim(0.1,1000)
-plt.semilogy(x,y, color='maroon')
-plt.tight_layout()
-# plt.savefig('images/xsection_plot.pgf')
-plt.savefig('images/xsection_plot.pdf')

### 2019-07-19 main.tex

@@
   Standard Model (MSSM). In this paper, we describe a search strategy  
-  for discovering pair-produced Higgsino-like next-to-lightest supersymmetric particles  at a 100 TeV 
+  for discovering pair-produced Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV 
   hadron collider that decay to Bino-like lightest supersymmetric particle (LSP) via intermediate $Z$ and 
@@
   to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially in the region where the mass difference between
-Higgsino NLSP and LSP is smaller. \Shufang{Update the numbers.}
+Higgsino NLSP and Bino LSP is smaller. \Shufang{Update the numbers.}
 }
@@
   \centering
-  \includegraphics[width=0.49\textwidth]{images/higgsino_production_xsection.png}
+  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
   \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}

### 2019-07-20 main.tex

@@
 Searches for pair produced nearly mass-degenerate Higgsinos  have been
-performed at ATLAS and CMS for various decay  topologies\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.
+performed at ATLAS and CMS for various decay  topologies
+\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
 For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\% C.L.

### 2019-07-20 main.tex
Addressing more comments

@@
 \abstract{%
-  A 100 TeV proton-proton collider will be an extremely effective 
-  way to probe the electroweak sector of the Minimal Supersymmetric 
-  Standard Model (MSSM). In this paper, we describe a search strategy  
-  for discovering pair-produced Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV 
-  hadron collider that decay to Bino-like lightest supersymmetric particle (LSP) via intermediate $Z$ and 
-  SM Higgs bosons that in turn decay to a pair of leptons and a pair of 
-  $b$-quarks respectively: $\N_{2}\N_{3}
-  \rightarrow (Z\N_1)(h\N_1)\rightarrow 
-  bb\ell\ell+\N_1\N_1$. In addition, we examine 
-  the potential for machine learning techniques to boost the power of 
-  our searches. Using this analysis, Higgsinos up to 1.3 TeV can be 
-  discovered for Binos  up to 0.9 TeV using 3000 fb$^{-1}$ of data,  
-  Additionally, Higgsinos up  to 1.8 TeV can be excluded for Binos up 
-  to 1.3 TeV at 95\% C.L.   This search channel extends the multi-lepton search limits, especially in the region where the mass difference between
-Higgsino NLSP and Bino LSP is smaller. \Shufang{Update the numbers.}
-}
+
+  A 100 TeV proton-proton collider will be an extremely effective way to probe
+  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).
+  In this paper, we describe a search strategy  for discovering pair-produced
+  Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV
+  hadron collider that decay to Bino-like lightest supersymmetric particle
+  (LSP) via intermediate $Z$ and SM Higgs bosons that in turn decay to a pair
+  of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
+  (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
+  potential for machine learning techniques to boost the power of our searches.
+  Using this analysis, Higgsinos up to 1.4 TeV can be discovered for Binos with
+  masses of about
+  0.9 TeV using 3000 fb$^{-1}$ of data. Additionally, Higgsinos up to 1.8
+  TeV can be excluded for Binos with masses of about 1.3 TeV at 95\% C.L.   This search
+  channel extends the multi-lepton search limits, especially in the region
+  where the mass difference between Higgsino NLSP and Bino LSP is smaller.
+\Shufang{Update the numbers.} \Adarsh{They are consistent with the text now.}}
 
@@
 believe I've already addressed this with the paragraphs I added below in response
-to your comment ... let me know if I should add more details.}. \Shufang{What you said below is for well separated spectra, not for mass spitting of 0.1 to 50 GeV.}
+to your comment ... let me know if I should add more details.}. \Shufang{What
+you said below is for well separated spectra, not for mass spitting of 0.1 to
+50 GeV.}
 Well-separated spectra have been studied in \cite{Gori:2014oua,
@@
   \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
-  \includegraphics[width=0.49\textwidth]{images/higgsino_br_plot.png}
-  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$ cross section (left panel), calculated using Prospino2~\cite{Beenakker:1999xh},  and decay decay branching fractions (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function of $\mu$ for $M_1=25$ GeV.
-However, it
-  should be noted that the dependence on $M_1$ is very weak.   \Shufang{How about Br? What's the vcalue of M1 used?}\\
-  \Shufang{Could you make the two plot same aspect ratios?
-Using plot digitizer.
-Also, for ylabel in left panel, the tilde should not go above 0.
-Just above $\chi$.
-Is there way to change the xlabel of right panel to be $\mu$ instead of $|\mu|$?
-Need to be consistent with the xlabels.}}
+  \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
+  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$
+    cross section (left panel), calculated using
+    Prospino2~\cite{Beenakker:1999xh},  and decay decay branching fractions
+    (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
+    of $|\mu|$ for $M_1=25$ GeV. However, it should be noted that the dependence
+    on $M_1$ is very weak. \Shufang{How about Br? What's the vcalue of M1
+    used? Could you make the two plot same aspect ratios? Using plot
+digitizer. Also, for ylabel in left panel, the tilde should not go above 0.
+Just above $\chi$.  Is there way to change the xlabel of right panel to be
+$\mu$ instead of $|\mu|$?  Need to be consistent with the xlabels.
+}\Adarsh{The value of $M_1$ used is 25 GeV for the branching ratio plot as
+well. I was able to rerun prospino and susyhit, so I didn't need to run the
+plotdigitizer for these plots. I also changed the tildes as you suggested.
+I changed the x-axis of both plots to $|\mu|$ for consistency - is that ok?}
+}
   \label{fig:xsection_plot}
@@
 \cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
-For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\% C.L.
-exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$ and an equal mixture of $WZ+WH$ topology, with the most stringest limits from the multi-lepton searches.
-For neutralino pair production with $ZZ$, $ZH$ and $HH$ topologies~\footnote{While such searches assume gravitino LSP with Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or multi-$b$ jets searches, depending on the decay branching fractions of Higgsino NLSP.
+For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\%
+C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$
+and an equal mixture of $WZ+WH$ topology, with the most stringest limits from
+the multi-lepton searches.  For neutralino pair production with $ZZ$, $ZH$ and
+$HH$ topologies~\footnote{While such searches assume gravitino LSP with
+Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino
+LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
+multi-$b$ jets searches, depending on the decay branching fractions of Higgsino
+NLSP.
 
@@
 a minimum $\met$ of 100 GeV at the parton level for the backgrounds as
-well.  \Shufang{This is only for BG, right?  No such cuts are imposed for signal generation?}
+well. \Shufang{This is only for BG, right?  No such cuts are imposed for
+signal generation?} \Adarsh{Yes, the MET cut was only for background.}
 
@@
   distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
-  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification, and
-  $\slashed{E}_{T}$ cuts.  \Shufang{How about mll cut? BG is generated with mll cut.}  The
+  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
+  $m_{\ell^+\ell^-}$, and
+  $\slashed{E}_{T}$ cuts.  \Shufang{How about mll cut? BG is generated with mll
+  cut.}  \Adarsh{I have added the $m_{ll}$ cut to the sentence.} The
   distribution for the \emph{bbWW} background is not shown, since it is negligible in
@@
     mass, and razor variable cuts are GeV. The significance, $S/\sqrt{B}$, is
-    calculated for an integrated luminosity of 3 ab$^{-1}$.   \Shufang{MET $>$ 400 or $<$ 400? }}
+    calculated for an integrated luminosity of 3 ab$^{-1}$. \Shufang{MET $>$
+  400 or $<$ 400? } \Adarsh{$> 400$ - I've fixed it now.}}
 \label{tab:cc_cutflowtable}
@@
 events that passed the lepton trigger, contained two SFOS leptons and two
-$b$-tagged jets, and calculated a number of kinematic variables for each event. \Shufang{Again, generator level MET, mll cut for the BG?} We then
-placed these kinematic variables in an array, with each row corresponding to an event, and
-the columns corresponding to the kinematic variables. A mixture of low-level and high level
-kinematic variables was shown to have the greatest effectiveness. The kinematic variables chosen were
-$m_{\ell\ell}$, $m_{bb}$, $M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic
-transverse energy $H_T$,   and transverse momenta of individual final state
-leptons and $b$-quarks: $p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We
-then divided the generated events into training and test sets, with the training set
+$b$-tagged jets, and calculated a number of kinematic variables for each event.
+\Shufang{Again, generator level MET, mll cut for the BG?} \Adarsh{Yes.} We then
+placed these kinematic variables in an array, with each row corresponding to an
+event, and the columns corresponding to the kinematic variables. A mixture of
+low-level and high level kinematic variables was shown to have the greatest
+effectiveness. The kinematic variables chosen were $m_{\ell\ell}$, $m_{bb}$,
+$M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic transverse energy $H_T$,
+and transverse momenta of individual final state leptons and $b$-quarks:
+$p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We then divided
+the generated events into training and test sets, with the training set
 comprising 75\% of signal events and 30\% of background events.  We used the
@@
 learning rate of 0.025.
-After the classifier is trained, we use it to assign
-scores to individual events. A more negative score indicates a more
-background-like event, and a more positive score denotes a more signal-like
-event. After the scores have been assigned to the events in the test sets, we
-can use this score just as we would a regular kinematical variable, that is, we
-apply a cut that selects events with a minimum of this score. The value of the
-cut is chosen to maximize the significance for each signal benchmark point. The
-distribution of scores for the specific benchmark point ($\mu$ = 1 TeV, $M_1$
-= 25 GeV) is shown in figure \ref{fig:bdt_response}. We observe that there is an
-appreciable separation between the signal and background distributions.
+
+After the classifier is trained, we use it to assign scores to individual
+events. A more negative score indicates a more background-like event, and a
+more positive score denotes a more signal-like event. After the scores have
+been assigned to the events in the test sets, we can use this score just as we
+would a regular kinematical variable, that is, we apply a cut that selects
+events with a minimum of this score. The value of the cut is chosen to maximize
+the significance for each signal benchmark point. The distribution of scores
+for the specific benchmark point ($\mu$ = 1 TeV, $M_1$ = 25 GeV) is shown in
+figure \ref{fig:bdt_response}. We observe that there is an appreciable
+separation between the signal and background distributions.
 
@@
   for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
-\Shufang{Can we change the xlabel of all plots to $\mu$ instead of $|\mu|$ or it is difficult to do?}\\  \Shufang{Did you save the data for this plot?
-It is actually not difficult to overlay ref 10 results.
-They only have a few data points and can easily be read out using plot-digitizer.
-By comparison, we can clearly see that our reach is better for large M1 region.}
+\Shufang{Can we change the xlabel of all plots to $\mu$ instead of $|\mu|$ or
+it is difficult to do? Did you save the data for this plot?  It is
+actually not difficult to overlay ref 10 results.  They only have a few data
+points and can easily be read out using plot-digitizer.  By comparison, we can
+clearly see that our reach is better for large M1 region.} \Adarsh{I did not
+save the data for this plot - I thought I could always regenerate it - however,
+the HPC folks changed their policy on the number of files per GB that they
+would allow - MadGraph and MadEvent produce a lot of files - for the Exotic
+Higgs project, I came up with ways to deal with this, but to do the same for
+this project would take a very large amount of time. I could change the xlabel
+to $\mu$ instead of $|\mu|$, but isn't $|\mu|$ more accurate, since $\mu$ can
+be positive or negative?}
 }
@@
 
-Fig.~\ref{fig:contours} shows the expected reach  for 95\%
-C.L. exclusion and 5$\sigma$ discovery in the parameter space of $\mu$ vs.
-$M_1$ for 100 TeV $pp$ collider with an integrated luminosity of 3000
-fb$^{-1}$. The cut-and-count strategy is able to discover Higgsinos up to 750
-GeV  and exclude them up to 1.3 TeV. \Shufang{Cross check the numbbers. Not entirely consistent with the plot.}    The boosted decision tree analysis, improves this reach -- it
-is able to discover Higgsinos up to 1.3 TeV, and exclude them up to 1.8 TeV in
-favorable points in parameter space.  Similarly, Binos can be discovered up to
-300 GeV and excluded up to 800 GeV with the rectangular cut analysis, and the
-BDT analysis can discover them up to about 900 GeV and exclude them up to 1.3
-TeV. Since the background left after cut is relatively low, We do not include
-systematic errors in these estimates.
+Fig.~\ref{fig:contours} shows the expected reach  for 95\% C.L. exclusion and
+5$\sigma$ discovery in the parameter space of $\mu$ vs.  $M_1$ for 100 TeV $pp$
+collider with an integrated luminosity of 3000 fb$^{-1}$. The cut-and-count
+strategy is able to discover Higgsinos up to 850 GeV  and exclude them up to
+1.3 TeV. \Shufang{Cross check the numbers. Not entirely consistent with the
+plot.} \Adarsh{I updated the numbers - how do they look?} The boosted decision
+tree analysis, improves this reach -- it is able to discover Higgsinos up to
+1.4 TeV, and exclude them up to 1.8 TeV in favorable points in parameter space.
+Similarly, Binos can be discovered up to 300 GeV and excluded up to 700 GeV
+with the rectangular cut analysis, and the BDT analysis can discover them up to
+about 900 GeV and exclude them up to 1.3 TeV. Since the background left after
+cut is relatively low, we do not include systematic errors in these estimates.
 
@@
 improvement over that of the LHC. We found that the rectangular cut strategy has
-the potential to discover Higgsino LSPs up to a mass of 750 GeV, and exclude
-them up to a mass of 1.3 TeV. As expected, the boosted decision tree classifier
-performs better, with the ability to discover Higgsino NLSPs up to 1.3 TeV and
-exclude them up to a mass of 1.8 TeV. With the BDT analysis, Bino dark matter
-candidates can be discovered up to 900 GeV, and excluded up to 1.3 TeV. In the
+the potential to discover Higgsino LSPs up to a mass of 850 GeV, and exclude
+them up to a mass of 1.3 TeV, for bino masses around 350 GeV and 700 GeV
+respectively. 
+As expected, the boosted decision tree classifier
+performs better, with the ability to discover Higgsino NLSPs up to 1.4 TeV and
+exclude them up to a mass of 1.8 TeV, for bino masses of about 900 GeV and 1.3
+TeV respectively. With the BDT analysis, Bino dark matter
+candidates can be discovered up to 0.9 TeV, and excluded up to 1.3 TeV. In the
 process, we highlighted the importance of generating enough Monte Carlo events
-to estimate the huge backgrounds at a 100 TeV $pp$ collider.  \Shufang{Update the numbers.}
+to estimate the huge backgrounds at a 100 TeV $pp$ collider.  \Shufang{Update
+the numbers.} \Adarsh{They are updated now.}
 

### 2019-07-23 main.tex
Pushing latest overleaf version

@@
   0.9 TeV using 3000 fb$^{-1}$ of data. Additionally, Higgsinos up to 1.8
-  TeV can be excluded for Binos with masses of about 1.3 TeV at 95\% C.L.   This search
+  TeV can be excluded for Binos with masses of about 1.4 TeV at 95\% C.L.   This search
   channel extends the multi-lepton search limits, especially in the region
   where the mass difference between Higgsino NLSP and Bino LSP is smaller.
-\Shufang{Update the numbers.} \Adarsh{They are consistent with the text now.}}
+ }
 
@@
 \maketitle
-\flushbottom
+%\flushbottom
 
@@
 known as electroweakinos), and gluinos. The current LHC search limits on
-gluinos are already around 2 TeV for prompt decay and 2.46 TeV for disappearing track searches~\cite{CMS-PAS-SUS-19-005}.   The
+gluinos are already around 2 TeV for prompt decay and 2.5 TeV for disappearing track searches~\cite{CMS-PAS-SUS-19-005}.   The
 limits on electroweakinos with heavy scalar superparticles,
@@
 GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
-Bino, Wino, and Higgsinos.  The mass eigenstates are usually labels as
+Bino, Wino, and Higgsinos.  The mass eigenstates are usually labeled as
 $\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.
@@
 The optimal search strategy for finding electroweakinos   highly depends on
-  their mass spectrums \cite{Han:2013kza}.  Phenomenological collider studies on finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
+  their mass spectra \cite{Han:2013kza}.  Phenomenological collider studies on finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
 found in \cite{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
-\Shufang{Say a few words about typical search strategy there.} \Adarsh{I
-believe I've already addressed this with the paragraphs I added below in response
-to your comment ... let me know if I should add more details.}. \Shufang{What
-you said below is for well separated spectra, not for mass spitting of 0.1 to
-50 GeV.}
+\Shufang{Say a few words about typical search strategy there.}
+\Adarsh{Yes, I focused more on well separated spectra since that is more similar to our case - should I add more details for the 0.1 - 50 GeV compressed spectra studies?} \Shufang{Add a couple sentences here of the search strategy for the small mass splitting case.}
 Well-separated spectra have been studied in \cite{Gori:2014oua,
@@
 Higgsino NLSPs can be excluded at 95\% C.L.
-with mass up to 2.85 TeV or be discovered with  mass up to 1.8 TeV, for massless Bino LSP.
+with mass up to 2.8 TeV or be discovered with  mass up to 1.8 TeV, for a massless Bino LSP.
 The reach reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
@@
 
-\begin{table}
-  \centering
-  \begin{tabular}{l|rr}
-    \toprule
-    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{1}$ & $\N_2\N_3$\\
-    \midrule
-    Pair production cross section & 60 fb & 16 fb\\
-    Intermediate diboson contribution & ($WZ$) 30 fb  & ($Zh$) 8 fb \\
-    Applying \emph{BR}$(W\rightarrow \ell\nu)$, \emph{BR}$(Z\rightarrow \ell\ell)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.32 fb\\
-    \bottomrule
-  \end{tabular}
-  \caption{Comparison of Higgsino pair production cross-sections for
-    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
-    $(\N_{2}\N_{3})$, for $\mu\approx 1$ TeV, at a 100
-    TeV \emph{pp} collider. The pair-production cross sections are taken from
-    \cite{Gori:2014oua}. The branching ratio to intermediate dibosons is
-    evaluated in the limit where the Goldstone equivalence theorem applies, so
-    that BR$(\widetilde{\chi}_{2,3}^0\rightarrow Z \widetilde{ \chi}_{1}^0)\approx$
-    BR$(\widetilde{\chi}_{2,3}^0\rightarrow h\widetilde{\chi}_1^0)\approx 50\% $ for massless $\widetilde{\chi}_{1}^0)$, 
-    and the branching ratios to the SM final states are taken from
-    \cite{Olive:2016xmw}.  
-    \Shufang{use the actual Br.} \Adarsh{As for the actual BR, I assume you mean
-  calculate it using SUSY-HIT? That'll take a bit more time, but I'll try to
-  get it.} \Shufang{You can read the number out from right panel of Fig. 2.} }
-  \label{tab:xsections}
-\end{table}
-
-For pair produced Higgsinos $\widetilde\chi_2^0\widetilde\chi_3^0$ in a scenario with
-decoupled Winos and  sfermions, the \emph{Zh} mode has the greatest
-branching ratio.  After multiplying all the branching fractions, the signal cross
-sections of
-
+In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section $\widetilde\chi_2^0\widetilde\chi_3^0$ for the Higgsino-like NLSPs.  The cross section varies between
+200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
+panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
+$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
+While one of the Higgsinos mostly decays to $Z$, the other
+Higgsino mostly decays to $h$.    Therefore,  for pair produced Higgsinos $\widetilde\chi_2^0\widetilde\chi_3^0$, the \emph{Zh} mode has the greatest
+branching fraction.  After multiplying all the branching fractions, the signal cross sections of 
 \begin{align}
@@
 \end{align}
-become comparable  to trilepton processes, as shown in    table \ref{tab:xsections}.    The signal contains two
+become comparable  to trilepton processes, as shown in    table \ref{tab:xsections}.   $Zh+\met$ signal thus provide an alternative
+discovery channel for Higgsinos.   The signal contains two
 \emph{b}-jets, two same flavor, opposite sign leptons, and missing transverse
@@
 $s$-channel top quarks.
-
-\begin{comment}
-\begin{figure}%
-  \centering
-  \image{0.21}{signal}
-  \image{0.21}{tt}
-  \image{0.27}{tbW}
-  \image{0.27}{bbWW}
-  \caption{From left to right, the representative Feynman diagrams of the signal
-    process, the dominant \emph{tt} background, \emph{tbW} without a top quark in the
-    \emph{s}-channel, and \emph{bbWW} without a top quark in the \emph{s}-channel. (Generated
-    using \cite{Ellis:2016jkw}.) \Shufang{Use $\chi_i^0$ etc.}}%
-  \label{fig:feynman_diagrams}
-\end{figure}
-\end{comment}
-
-In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section $\widetilde\chi_2^0\widetilde\chi_3^0$ for the Higgsino-like NLSPs.  The cross section varies between
-200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
-panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
-$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
-While one of the Higgsinos mostly decays to $Z$, the other
-Higgsino mostly decays to $h$.  $Zh+\met$ signal thus provide an alternative
-discovery channel for Higgsinos.
 
@@
     cross section (left panel), calculated using
-    Prospino2~\cite{Beenakker:1999xh},  and decay decay branching fractions
+    Prospino2~\cite{Beenakker:1999xh},  and decay branching fractions
     (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
-    of $|\mu|$ for $M_1=25$ GeV. However, it should be noted that the dependence
-    on $M_1$ is very weak. \Shufang{How about Br? What's the vcalue of M1
-    used? Could you make the two plot same aspect ratios? Using plot
-digitizer. Also, for ylabel in left panel, the tilde should not go above 0.
-Just above $\chi$.  Is there way to change the xlabel of right panel to be
-$\mu$ instead of $|\mu|$?  Need to be consistent with the xlabels.
-}\Adarsh{The value of $M_1$ used is 25 GeV for the branching ratio plot as
-well. I was able to rerun prospino and susyhit, so I didn't need to run the
-plotdigitizer for these plots. I also changed the tildes as you suggested.
-I changed the x-axis of both plots to $|\mu|$ for consistency - is that ok?}
+    of $\mu$ for $M_1=25$ GeV. However, it should be noted that the dependence
+    on $M_1$ is very weak.
+\Shufang{Could you use $\mu$ for both xlabels?
+The CS and Br will depend slightly on the sign of mu.
+Since we do use positive mu in our analyses, let's label it this way.
+I have a footnote in intro to explain the sign effect of mu.
+Also, change right panel, ylabel to be either Br or Branching Fraction.}
 }
@@
 \end{figure}
+
+\begin{table}
+  \centering
+  \begin{tabular}{l|rr}
+    \toprule
+    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{1}$ & $\N_2\N_3$\\
+    \midrule
+    Pair production cross section & 60 fb & 17.2 fb\\
+    Intermediate diboson contribution & ($WZ$) 29.7 fb  & ($Zh$) 9.15 fb \\
+    Applying \emph{BR}$(W\rightarrow \ell\nu)$, \emph{BR}$(Z\rightarrow \ell\ell)$ \& \emph{BR}$(h\rightarrow bb)$ & 0.42 fb & 0.37 fb\\
+    \bottomrule
+  \end{tabular}
+  \caption{Comparison of Higgsino pair production cross-sections for
+    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
+    $(\N_{2}\N_{3})$, for $\mu\approx 1$ TeV, at a 100
+    TeV \emph{pp} collider. 
+    The pair-production cross section for $\N_{2,3}\widetilde{\chi}^\pm_1$ is taken from
+    \cite{Gori:2014oua}, while the pair-production cross-section for $\N_2\N_3$ is calculated at Next-to-Leading Order (NLO) using Prospino2.
+The branching ratios to the diboson intermediate states are calculated using SUSY-HIT, and the branching ratios to the SM final states are taken from
+    \cite{Olive:2016xmw}.    }
+  \label{tab:xsections}
+\end{table}
 
@@
 C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$
-and an equal mixture of $WZ+WH$ topology, with the most stringest limits from
+and an equal mixture of $WZ+WH$ topology, with the most strongest limits from
 the multi-lepton searches.  For neutralino pair production with $ZZ$, $ZH$ and
@@
 % ATLAS, 4 leptons (hh/ZZ/hZ --> 4l)
-
-\begin{comment}
-While the majority of the existing searches for supersymmetry focus on gluino
-pair production, there are a number of analyses involving electroweak pair
-production of charginos and neutralinos as well, which we will attempt to briefly review here.  Searches
-involving multiple leptons and missing energy $(2l/3l +\slashed{E}_T)$ in the
-final state are described in
-\cite{Aaboud:2018sua,Aaboud:2018jiw, ATLAS:2016uwq,Khachatryan:2014qwa,Chatrchyan:2012pka}, assuming a
-wino-like NLSP and a bino-like LSP. The best reach is obtained in the $2/3l$
-channel by ATLAS with 36.1 fb$^{-1}$ of data, with NLSP masses up to 600 GeV
-excluded for massless LSPs \cite{Aaboud:2018sua}.
-
-% AP: These have intermediate sleptons, so I am omitting them.
-%Topologies with one or two hadronically-decaying tau leptons and missing energy
-%in the final state have been studied in \cite{ATLAS:2016ety,
-%Khachatryan:2016trj}, with the greatest reach obtained by ATLAS in
-%\cite{ATLAS:2016ety}, using 13 TeV data - they are able to exclude wino-like
-%NLSPs up to a mass of 700 GeV for a massless bino-like LSP.
-
-Searches with a combination of leptons and jets in the final states can be found
-in \cite{Aad:2014vma,Khachatryan:2015kxa,Khachatryan:2014mma}. Winos up to 465
-GeV are excluded in the $2l + 0/2j$ final states in \cite{Aad:2014vma}. A
-compressed mass spectrum is studied in \cite{Khachatryan:2015kxa}, with a mass
-difference of about 50 GeV between winos and binos. This study uses the vector
-boson fusion channel, with a final state of $2l + 2j + \slashed{E}_T$, and
-excludes winos up to a mass of 170 GeV. Of particular interest to us is the
-analysis in \cite{Khachatryan:2014mma}, where higgsinos can be excluded up to a
-mass of 380 GeV using the $bbll + \slashed{E}_T$ final state, but cannot be
-discovered in any region of the relevant parameter space. As we shall see, a 100
-TeV collider will enable us to greatly improve upon these limits.
-\end{comment}
 
@@
 parameter set to 40 GeV. The Higgsino pair production cross sections were
-calculated using \texttt{Prospino2}~\cite{Beenakker:1999xh}. \Shufang{tree level or NLO or what?}  To decouple the
-Wino, we set its mass parameter $M_2$ to 5 TeV.
+calculated using \texttt{Prospino2}~\cite{Beenakker:1999xh} at NLO.  
+To decouple the Wino, we set its mass parameter $M_2$ to 3 TeV.
 
@@
 a minimum $\met$ of 100 GeV at the parton level for the backgrounds as
-well. \Shufang{This is only for BG, right?  No such cuts are imposed for
-signal generation?} \Adarsh{Yes, the MET cut was only for background.}
+well.
 
@@
 
+   \item \emph{Missing Tranverse Energy:}  $\met> 400$ GeV.
+
  \item \emph{Invariant mass of Z-candidate:}  $85\ {\rm GeV}<m_{\ell^{+}\ell^{-}}<95\ {\rm GeV}$.
@@
   \item \emph{Invariant mass of h-candidate:} $75\ {\rm GeV}<m_{bb}<150\ {\rm GeV}$ for two leading $b$-jets.
-
-  \item \emph{Missing Tranverse Energy:}  $\met> 400$ GeV.
 
@@
       Representative kinematic
-  distributions of these variables for signal events of a 1 TeV Higgsino and a 25 GeV Bino, as well as $tt$ and $tbW$ backgrounds are
+  distributions of these variables for signal events of $\mu=1$ TeV Higgsinos NLSP and a $M_1=25$ GeV Bino LSP, as well as $tt$ and $tbW$ backgrounds are
   shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
-  $m_{\ell^+\ell^-}$, and
-  $\slashed{E}_{T}$ cuts.  \Shufang{How about mll cut? BG is generated with mll
-  cut.}  \Adarsh{I have added the $m_{ll}$ cut to the sentence.} The
+  $\slashed{E}_{T}$,  and  $m_{\ell^+\ell^-}$cuts.
+\Shufang{BG generator level mll and MET cut (MET bigger tan 100 GeV), or cut level mll and MET cut (MET bigger than 400 GEV)?
+Both signal and backgrounds?} The
   distribution for the \emph{bbWW} background is not shown, since it is negligible in
@@
 \includegraphics[trim = {0.3cm 0.6cm 0.1cm 0}, clip, width=0.496\textwidth]{images/mTR_copy.png}
-\caption{Normalized distributions of the razor kinematical variables $M_R$
-  (left) and $M_T^R$ (right) for signal process with a 1 TeV Higgsino NLSP and 25 GeV Bino LSP,  as well as the dominant $tt$ and $tbW$ backgrounds,
-  after the trigger, identification, and $\slashed{E}_{T}$ cuts.}
+\caption{Normalized distributions of the razor kinematic variables $M_R$
+  (left) and $M_T^R$ (right) for signal process with $\mu=1$ TeV Higgsinos NLSP and a $M_1=25$ GeV Bino LSP,  as well as the dominant $tt$ and $tbW$ backgrounds,
+  after the trigger, identification,  $\slashed{E}_{T}$ and $m_{\ell^+\ell^-}$ cuts.}
 \label{fig:razor_histos}
@@
     mass, and razor variable cuts are GeV. The significance, $S/\sqrt{B}$, is
-    calculated for an integrated luminosity of 3 ab$^{-1}$. \Shufang{MET $>$
-  400 or $<$ 400? } \Adarsh{$> 400$ - I've fixed it now.}}
+    calculated for an integrated luminosity of 3 ab$^{-1}$.  }
 \label{tab:cc_cutflowtable}
@@
 the benchmark points, we require a minimum of 3 signal events left over after
-cuts. We can see that, after applying our cuts, $tt$ and $tbW$ remain as the
-dominant backgrounds. The values of the razor variable cuts were chosen to
+cuts. We can see that, after applying our cuts, $tbW$ remains as the
+dominant backgrounds, followed by $tt$.   The values of the razor variable cuts were chosen to
 maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
@@
 $b$-tagged jets, and calculated a number of kinematic variables for each event.
-\Shufang{Again, generator level MET, mll cut for the BG?} \Adarsh{Yes.} We then
+  \Shufang{So singal event does not have mll and MET parton level cuts while BG events have those two cuts. right?}   We then
 placed these kinematic variables in an array, with each row corresponding to an
@@
 been assigned to the events in the test sets, we can use this score just as we
-would a regular kinematical variable, that is, we apply a cut that selects
+would a regular kinematic variable, that is, we apply a cut that selects
 events with a minimum of this score. The value of the cut is chosen to maximize
@@
 
-Table \ref{tab:bdt_cutflowtable} shows the cut efficiences for the same
+Table \ref{tab:bdt_cutflowtable} shows the cut efficiencies for the same
 representative benchmark point as in table \ref{tab:cc_cutflowtable}, but this
@@
 For certain values of the
-cuts on kinematical variables or the score of the classifier, no events survived
+cuts on kinematic variables or the score of the classifier, no events survived
 for one or more of the background components. To guard against overly optimistic
@@
   for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
-\Shufang{Can we change the xlabel of all plots to $\mu$ instead of $|\mu|$ or
-it is difficult to do? Did you save the data for this plot?  It is
-actually not difficult to overlay ref 10 results.  They only have a few data
-points and can easily be read out using plot-digitizer.  By comparison, we can
-clearly see that our reach is better for large M1 region.} \Adarsh{I did not
-save the data for this plot - I thought I could always regenerate it - however,
-the HPC folks changed their policy on the number of files per GB that they
-would allow - MadGraph and MadEvent produce a lot of files - for the Exotic
-Higgs project, I came up with ways to deal with this, but to do the same for
-this project would take a very large amount of time. I could change the xlabel
+\Adarsh{  I could change the xlabel
 to $\mu$ instead of $|\mu|$, but isn't $|\mu|$ more accurate, since $\mu$ can
-be positive or negative?}
+be positive or negative?} \Shufang{Yes, change to $\mu$.  Sign of mu has a small effect.  Since we use positive mu, let's label it this way.}
 }
@@
 strategy is able to discover Higgsinos up to 850 GeV  and exclude them up to
-1.3 TeV. \Shufang{Cross check the numbers. Not entirely consistent with the
-plot.} \Adarsh{I updated the numbers - how do they look?} The boosted decision
+1.35 TeV.  The boosted decision
 tree analysis, improves this reach -- it is able to discover Higgsinos up to
 1.4 TeV, and exclude them up to 1.8 TeV in favorable points in parameter space.
-Similarly, Binos can be discovered up to 300 GeV and excluded up to 700 GeV
+Similarly, Binos can be discovered up to 350 GeV and excluded up to 700 GeV
 with the rectangular cut analysis, and the BDT analysis can discover them up to
-about 900 GeV and exclude them up to 1.3 TeV. Since the background left after
+about 900 GeV and exclude them up to 1.4 TeV. Since the background left after
 cut is relatively low, we do not include systematic errors in these estimates.
 
-Comparing the BDT results with that of the cut-bases anayses, the improvement is substantial, but perhaps not spectacular. However, it should
+Comparing the BDT results with that of the cut-and-count bases analyses, the improvement is substantial, but perhaps not spectacular. However, it should
 be kept in mind that this is probably a conservative estimate. Since we reserve
@@
 
- Comparing to the reach of multi-lepton channel in Ref.~\cite{Gori:2014oua}, with an  exclusion limit of Higgsino mass up to 2.85 TeV or a discovery reach of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$ channel in our study is less.
+ Comparing to the reach of multi-lepton channel in Ref.~\cite{Gori:2014oua}, with an  exclusion limit of Higgsino mass up to 2.8 TeV or a discovery reach of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$ channel in our study is less.
 However, the reach for multi-lepton channel reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
@@
 In this paper, we examined the discovery potential for a 100 TeV $pp$ collider For 
-pair-produced heavy Higgsinos with Bino LSP, via 
+pair-produced heavy Higgsino NLSPs with Bino LSP, via 
 intermediate $Z$ and $h$ bosons that decay to a pair of leptons and $b$ quarks respectively:  $\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
 
-We pursued two analysis strategies. One was the traditional cut-and-count methos , including razor variables
+We pursued two analysis strategies. One was the traditional cut-and-count methods , including razor variables
 that are sensitive to the mass difference between the LSP and the NLSP. The
@@
 the potential to discover Higgsino LSPs up to a mass of 850 GeV, and exclude
-them up to a mass of 1.3 TeV, for bino masses around 350 GeV and 700 GeV
+them up to a mass of 1.35 TeV, for Bino masses around 350 GeV and 700 GeV
 respectively. 
@@
 performs better, with the ability to discover Higgsino NLSPs up to 1.4 TeV and
-exclude them up to a mass of 1.8 TeV, for bino masses of about 900 GeV and 1.3
-TeV respectively. With the BDT analysis, Bino dark matter
-candidates can be discovered up to 0.9 TeV, and excluded up to 1.3 TeV. In the
+exclude them up to a mass of 1.8 TeV, for Bino masses of about 900 GeV and 1.4
+TeV respectively.   In the
 process, we highlighted the importance of generating enough Monte Carlo events
-to estimate the huge backgrounds at a 100 TeV $pp$ collider.  \Shufang{Update
-the numbers.} \Adarsh{They are updated now.}
+to estimate the huge backgrounds at a 100 TeV $pp$ collider.
 
@@
 research activities of AP and SS were supported in part by the Department of
-Energy under Grant DE-FG02-13ER41976 / de-sc0009913;. An allocation of computer
+Energy under Grant DE-FG02-13ER41976/de-sc0009913. An allocation of computer
 time from the UA Research Computing High Performance Computing (HPC) and High
 Throughput Computing (HTC) at the University of Arizona is gratefully
-acknowledged.
+acknowledged.  We also thank KITP for its hospitality when this draft is completed.  This research was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.
 

### 2019-07-23 main.tex
Added a couple of sentences about compressed spectra

@@
 \newcommand{\N}{\widetilde{\chi}^0}
+\newcommand{\C}{\widetilde{\chi}^\pm}
 \newcommand{\image}[2]{\parbox{#1\textwidth}{\includegraphics[width=#1\textwidth]{images/#2.pdf}}}
@@
 
-The existence of dark matter provides unambiguous evidence of new 
-physics beyond the Standard Model (SM) of particle physics. Indeed, 
-given that there is far more dark matter in the Universe than there 
-is baryonic matter, determining its precise nature is one of the most 
-exciting challenges in particle physics today.  One promising group 
-of candidate for dark matter is the class of stable particles known as 
-weakly interacting massive particles (WIMPs). These particles arise 
-naturally in many extensions of the SM that are motivated by the need to
-stabilize the electroweak scale. One of the most studied extensions
-to the SM is the Minimal Supersymmetric Standard Model
-(MSSM), which predicts a `supersymmetric partner', or \emph{superpartner}, 
-for each SM particle\footnote{For a detailed review of the MSSM, see 
-Ref. \cite{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the 
-lightest supersymmetric partner (LSP) is predicted to be absolutely 
-stable, making it a good candidate for dark matter. The identity of 
-the LSP is determined by the mass hierarchy of the superpartners, 
-which in turn depends on how supersymmetry is broken.
-However, taking into account experimental constraints and phenomenological 
-considerations, the lightest of the  MSSM particles known as the 
-neutralinos emerges as the most attractive candidates for the LSP \cite{Bertone:2004pz}.
+The existence of dark matter provides unambiguous evidence of new physics
+beyond the Standard Model (SM) of particle physics. Indeed, given that there is
+far more dark matter in the Universe than there is baryonic matter, determining
+its precise nature is one of the most exciting challenges in particle physics
+today.  One promising group of candidate for dark matter is the class of stable
+particles known as weakly interacting massive particles (WIMPs). These
+particles arise naturally in many extensions of the SM that are motivated by
+the need to stabilize the electroweak scale. One of the most studied extensions
+to the SM is the Minimal Supersymmetric Standard Model (MSSM), which predicts a
+`supersymmetric partner', or \emph{superpartner}, for each SM
+particle\footnote{For a detailed review of the MSSM, see Ref.
+\cite{Martin:1997ns}.}. In the MSSM with \emph{R}-parity conservation, the
+lightest supersymmetric partner (LSP) is predicted to be absolutely stable,
+making it a good candidate for dark matter. The identity of the LSP is
+determined by the mass hierarchy of the superpartners, which in turn depends on
+how supersymmetry is broken.  However, taking into account experimental
+constraints and phenomenological considerations, the lightest of the  MSSM
+particles known as the neutralinos emerges as the most attractive candidates
+for the LSP \cite{Bertone:2004pz}.
 
  % Why go beyond the MSSM?
-Though a natural MSSM spectrum has the potential to tame the hierarchy
-problem, it is under siege from recent data from the Large Hadron
-Collider (LHC) \cite{Aaboud:2018ujj, Sirunyan:2018vjp}. 
-A compelling alternative scenario comes in the form of
-split supersymmetry (split SUSY) \cite{Wells:2003tf,
+Though a natural MSSM spectrum has the potential to tame the hierarchy problem,
+it is under siege from recent data from the Large Hadron Collider (LHC)
+\cite{Aaboud:2018ujj, Sirunyan:2018vjp}.  A compelling alternative scenario
+comes in the form of split supersymmetry (split SUSY) \cite{Wells:2003tf,
 ArkaniHamed:2004yi, Giudice:2004tc}. In this scenario, the lightest
-superpartners are the fermionic ones, on the
-scale of 1-10 TeV, while the scalar superpartners can be much heavier,
-on the scale of 100 - 1000 TeV. In exchange for accepting some level of
-fine-tuning, we obtain numerous benefits, including the suppression of
-flavor-changing neutral currents and greater compatibility with data
-from CP-violation experiments.  The low lying 
-fermionic superpartners consist of neutralinos and charginos (collectively
-known as electroweakinos), and gluinos. The current LHC search limits on
-gluinos are already around 2 TeV for prompt decay and 2.5 TeV for disappearing track searches~\cite{CMS-PAS-SUS-19-005}.   The
-limits on electroweakinos with heavy scalar superparticles,
-however, are still relatively weak: around 650 $-$ 750 GeV or  less~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}, depending on
-the decay modes of the parent electroweakinos and their species.  In this paper, we will
-focus on the discovery potential of the neutralinos and charginos at the 100
-TeV $pp$ collider.
+superpartners are the fermionic ones, on the scale of 1-10 TeV, while the
+scalar superpartners can be much heavier, on the scale of 100 - 1000 TeV. In
+exchange for accepting some level of fine-tuning, we obtain numerous benefits,
+including the suppression of flavor-changing neutral currents and greater
+compatibility with data from CP-violation experiments.  The low lying fermionic
+superpartners consist of neutralinos and charginos (collectively known as
+electroweakinos), and gluinos. The current LHC search limits on gluinos are
+already around 2 TeV for prompt decay and 2.5 TeV for disappearing track
+searches~\cite{CMS-PAS-SUS-19-005}.   The limits on electroweakinos with heavy
+scalar superparticles, however, are still relatively weak: around 650 $-$ 750
+GeV or less~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae, Aaboud:2018htj,
+Sirunyan:2018ubx, Aaboud:2018zeb}, depending on the decay modes of the parent
+electroweakinos and their species.  In this paper, we will focus on the
+discovery potential of the neutralinos and charginos at the 100 TeV $pp$
+collider.
 
 % Point to review papers for enumeration of studies
-The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos)
-depend on the hierarchy of the MSSM parameters $M_1, M_2$, and $\mu$~\footnote{For our study, we assume all the mass parameters are positive.
-For the current analyses, the results do not depend much on the sign of those parameters.}, which
-roughly determine the masses of the Bino, Winos, and Higgsinos, respectively~\cite{Han:2013kza}. 
-In this paper, we consider the Higgsino NLSP and Bino LSP scenario with $M_1 < \mu \ll M_2$.
-One of the motivations for studying Higgsinos is that the parameter $\mu$ 
-that governs its mass plays an important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, which tends to be small by naturalness considerations.
-Finding Higgsinos has traditionally been more challenging
-than finding Winos, due to their smaller production rate. This, however, can 
-be remedied by the increased  production cross sections and luminosities 
-at a 100 TeV $pp$ collider.
+The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos) depend
+on the hierarchy of the MSSM parameters $M_1, M_2$, and $\mu$~\footnote{For our
+study, we assume all the mass parameters are positive.  For the current
+analyses, the results do not depend much on the sign of those parameters.},
+which roughly determine the masses of the Bino, Winos, and Higgsinos,
+respectively~\cite{Han:2013kza}.  In this paper, we consider the Higgsino NLSP
+and Bino LSP scenario with $M_1 < \mu \ll M_2$.  One of the motivations for
+studying Higgsinos is that the parameter $\mu$ that governs its mass plays an
+important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, which
+tends to be small by naturalness considerations.   Finding Higgsinos has
+traditionally been more challenging than finding Winos, due to their smaller
+production rate. This, however, can be remedied by the increased  production
+cross sections and luminosities at a 100 TeV $pp$ collider.
 
@@
 neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.  Searches for
-Higgsino NLPs with a Bino LSP  via  multi-lepton final states have been
-studied in Ref.~\cite{Gori:2014oua} at a 100 TeV $pp$ collider, for pair production of $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm$ and  $\widetilde\chi_{1}^+\widetilde\chi_1^-$.
-In this paper, we attempt to exploit the relatively high branching
-ratio of the SM Higgs boson to \emph{b} quarks, and study the potential of the channel of
-$\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
+Higgsino NLPs with a Bino LSP  via  multi-lepton final states have been studied
+in Ref.~\cite{Gori:2014oua} at a 100 TeV $pp$ collider, for pair production of
+$\N_{2,3}\C_1$ and
+$\widetilde\chi_{1}^+\widetilde\chi_1^-$. In this paper, we attempt to exploit
+the relatively high branching ratio of the SM Higgs boson to \emph{b} quarks,
+and study the potential of the channel of $\N_2\N_3\rightarrow Zh
+\N_1\N_1\rightarrow bb\ell\ell \met$.
 
@@
 A 100 TeV $pp$ collider would open up an immense number of physics
-opportunities not afforded to a 14 TeV LHC, including exploring the
-most interesting regions of the split SUSY parameter space
+opportunities not afforded to a 14 TeV LHC, including exploring the most
+interesting regions of the split SUSY parameter space
 \cite{Arkani-Hamed:2015vfh}.
@@
 Such a collider would be a natural next step after the LHC, and is being
-actively discussed in the particle physics community, with two major
-proposals being the Future Circular Collider (FCC)-hh by CERN \cite{FCC-hh}, and the Super Proton Proton Collider (SppC)  
-in China \cite{CEPC}.  As the next energy frontier machine, it is of 
-crucial importance to fully explore the physics potential of a 100 TeV $pp$
-collider, especially for new particles that are either too heavy or too rare 
-to be produced at the LHC~\cite{Arkani-Hamed:2015vfh,Contino:2016spe,Golling:2016gvc,Mangano:2016jyj}.
+actively discussed in the particle physics community, with two major proposals
+being the Future Circular Collider (FCC)-hh by CERN \cite{FCC-hh}, and the
+Super Proton Proton Collider (SppC)  in China \cite{CEPC}.  As the next energy
+frontier machine, it is of crucial importance to fully explore the physics
+potential of a 100 TeV $pp$ collider, especially for new particles that are
+either too heavy or too rare to be produced at the
+LHC~\cite{Arkani-Hamed:2015vfh,Contino:2016spe,Golling:2016gvc,Mangano:2016jyj}.
 In particular, studies have already been performed on the prospects of
-discovering neutralino dark matter for compressed \cite{Low:2014cba, diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus}
-and well-separated \cite{Gori:2014oua,Acharya:2014pua}
-neutralino spectra.
+discovering neutralino dark matter for compressed \cite{Low:2014cba,
+diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus} and
+well-separated \cite{Gori:2014oua,Acharya:2014pua} neutralino spectra.
 
@@
 
-The rest of the paper is structured as follows. In Sec.~\ref{sec:model}, we describe our model and search channel in more
-detail, and list the existing experimental search bounds. In Sec.~\ref{sec:analysis}, we describe our analysis strategies 
-for both traditional cut-and-count analyses and analyses
-performed using BDT. In Sec.~\ref{sec:results},
-we present the results of our analyses, i.e. the expected 5 $\sigma$ discovery and 95\% C.L. exclusion
-reaches. Finally, we conclude with the implications in Sec.~\ref{sec:conclusion}.
+The rest of the paper is structured as follows. In Sec.~\ref{sec:model}, we
+describe our model and search channel in more detail, and list the existing
+experimental search bounds. In Sec.~\ref{sec:analysis}, we describe our
+analysis strategies for both traditional cut-and-count analyses and analyses
+performed using BDT. In Sec.~\ref{sec:results}, we present the results of our
+analyses, i.e. the expected 5 $\sigma$ discovery and 95\% C.L. exclusion
+reaches. Finally, we conclude with the implications in
+Sec.~\ref{sec:conclusion}.
 
@@
 The neutralino sector of MSSM consists of four mass eigenstates
-($\N_1,\N_2,\N_3,\N_4$), which
-are mixtures of the Bino, Wino, and two neutral Higgsinos: 
-($\B,\widetilde{W}^0,\H_d,\H_u$). In the basis of these gauge eigenstates, the mass
-matrix of the neutralinos can be written as
+($\N_1,\N_2,\N_3,\N_4$), which are mixtures of the Bino, Wino, and two neutral
+Higgsinos: ($\B,\widetilde{W}^0,\H_d,\H_u$). In the basis of these gauge
+eigenstates, the mass matrix of the neutralinos can be written as
 
@@
 
-\begin{equation}
+\begin{align}
   \mathbf{M}_{\widetilde{N}}=
@@
   \end{pmatrix},
-\end{equation}
-where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
+\end{align}
+
+\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
 for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
@@
 The optimal search strategy for finding electroweakinos   highly depends on
-  their mass spectra \cite{Han:2013kza}.  Phenomenological collider studies on finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a 100 TeV collider can be
-found in \cite{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa},
-\Shufang{Say a few words about typical search strategy there.}
-\Adarsh{Yes, I focused more on well separated spectra since that is more similar to our case - should I add more details for the 0.1 - 50 GeV compressed spectra studies?} \Shufang{Add a couple sentences here of the search strategy for the small mass splitting case.}
+their mass spectra \cite{Han:2013kza}.  Phenomenological collider studies on
+finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a
+100 TeV collider can be found in \cite{Low:2014cba, Bramante:2014tba,
+Berlin:2015aba, Cirelli:2014dsa}. The projected exclusion reaches for pure Wino
+LSPs (with a mass splitting of 164.6 MeV \cite{Ibe:2012sx}) at a 100 TeV
+collider using the monojet channel is $\sim1.4$~TeV.  The reach
+can be increased to $\sim3$ TeV using a disappearing tracks search.
+Neutralinos up to 1 TeV can be excluded for mass splittings of about 20-30 GeV,
+using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
+with masses up to 1.5 TeV and $\sim 1$~GeV inter-state mass splitting can be
+discovered at a 100 TeV collider with $\sim7 \text{ab}^{-1}$ of data.
+
+  \Shufang{Say a few words about typical
+  search strategy there.} \Adarsh{Yes, I focused more on well separated spectra
+  since that is more similar to our case - should I add more details for the
+  0.1 - 50 GeV compressed spectra studies?} \Shufang{Add a couple sentences
+  here of the search strategy for the small mass splitting case.}
+  \Adarsh{I added a couple of sentences.}
+
   Well-separated spectra have been studied in \cite{Gori:2014oua,
-Acharya:2014pua} using
-multi-lepton channels, of the form 
+  Acharya:2014pua} using multi-lepton channels, of the form
+
 \begin{align}
   pp\rightarrow \widetilde{\chi}_i\widetilde{\chi}_j\rightarrow VV +
-  \widetilde{\chi}_1^0\widetilde{\chi}_1^0\rightarrow 2\ell/3\ell +  
-  \met,
+  \N_1\N_1\rightarrow 2\ell/3\ell + \met,
 \end{align}
-where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino,
-$\widetilde{\chi}_1^0$ is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$ or scalar $h$.  These searches work well since
-the large mass difference between the electroweakinos can lead to energetic
-leptons that can be easily identified. Among the multi-lepton searches for
-Higgsinos, the trilepton searches: $\widetilde\chi_{2,3}^0\widetilde\chi_1^\pm\rightarrow WZ\widetilde\chi_1^0\widetilde\chi_1^0\rightarrow \ell\ell\ell + \met$, with $\ell=e, \ \mu$,  have the best reach, due to the relatively high production cross-section of
-chargino-neutralino pairs combined with the large reduction in $t\overline{t}$
-and QCD backgrounds obtained by requiring three leptons.
-Higgsino NLSPs can be excluded at 95\% C.L.
-with mass up to 2.8 TeV or be discovered with  mass up to 1.8 TeV, for a massless Bino LSP.
-The reach reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
-Multilepton searches
-with \emph{Zh} and \emph{ZZ} as the intermediate dibosons are unlikely to be as powerful,
-due to the smaller pair-production cross-section of neutral Higgsinos, combined
-with the low branching ratio of \emph{Z/h} to leptons. However, if we move beyond
+
+\noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, $\N_1$
+is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$
+or scalar $h$.  These searches work well since the large mass difference
+between the electroweakinos can lead to energetic leptons that can be easily
+identified. Among the multi-lepton searches for Higgsinos, the trilepton
+searches: $\N_{2,3}\C_1\pm\rightarrow WZ\N_1\N_1\rightarrow \ell\ell\ell +
+\met$, with $\ell=e, \ \mu$,  have the best reach, due to the relatively high
+production cross-section of chargino-neutralino pairs combined with the large
+reduction in $t\overline{t}$ and QCD backgrounds obtained by requiring three
+leptons.  Higgsino NLSPs can be excluded at 95\% C.L. with mass up to 2.8 TeV
+or be discovered with  mass up to 1.8 TeV, for a massless Bino LSP.   The reach
+reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV)
+for discovery (exclusion).    Multilepton searches with \emph{Zh} and \emph{ZZ}
+as the intermediate dibosons are unlikely to be as powerful, due to the smaller
+pair-production cross-section of neutral Higgsinos, combined with the low
+branching ratio of \emph{Z/h} to leptons. However, if we move beyond
 multilepton searches, the channel with \emph{Zh} (originally suggested in
@@
 
-In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production cross section $\widetilde\chi_2^0\widetilde\chi_3^0$ for the Higgsino-like NLSPs.  The cross section varies between
-200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The right
-panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions of
-$\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT \cite{Djouadi:2006bz}.
-While one of the Higgsinos mostly decays to $Z$, the other
-Higgsino mostly decays to $h$.    Therefore,  for pair produced Higgsinos $\widetilde\chi_2^0\widetilde\chi_3^0$, the \emph{Zh} mode has the greatest
-branching fraction.  After multiplying all the branching fractions, the signal cross sections of 
+In the left panel of Fig.~\ref{fig:xsection_plot}, we show the pair-production
+cross section $\N_2\N_3$ for the Higgsino-like NLSPs.  The cross section varies
+between 200 fb to 0.5 fb for Higgsino masses between 500 GeV and 2500 GeV. The
+right panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions
+of $\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT
+\cite{Djouadi:2006bz}.  While one of the Higgsinos mostly decays to $Z$, the
+other Higgsino mostly decays to $h$.    Therefore,  for pair produced Higgsinos
+$\N_2\N_3$, the \emph{Zh} mode has the greatest branching fraction.  After
+multiplying all the branching fractions, the signal cross sections of
+
 \begin{align}
-pp\rightarrow \widetilde{\chi}_{2}^{0}\widetilde{\chi}_{3}^{0}\rightarrow
-(Z\widetilde{\chi}_1^{0})(h\widetilde{\chi}_1^{0})\rightarrow
-bb\ell\ell \chi_1^0\chi_1^0.
+  pp\rightarrow \N_2\N_3\rightarrow (Z\N_1)(h\N_1)\rightarrow bb\ell\ell \N_1\N_1.
 \end{align}
-become comparable  to trilepton processes, as shown in    table \ref{tab:xsections}.   $Zh+\met$ signal thus provide an alternative
-discovery channel for Higgsinos.   The signal contains two
-\emph{b}-jets, two same flavor, opposite sign leptons, and missing transverse
-energy. The main backgrounds for this process are: $t\overline{t}$, \emph{tbW} with
-the $b$ and $W$ not coming from a \emph{t}, and \emph{bbWW} with no intermediate
-$s$-channel top quarks.
+
+\noindent become comparable  to trilepton processes, as shown in table
+\ref{tab:xsections}. $Zh+\met$ signal thus provide an alternative discovery
+channel for Higgsinos. The signal contains two \emph{b}-jets, two same flavor,
+opposite sign leptons, and missing transverse energy. The main backgrounds for
+this process are: $t\overline{t}$, \emph{tbW} with the $b$ and $W$ not coming
+from a \emph{t}, and \emph{bbWW} with no intermediate $s$-channel top quarks.
 
@@
   \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
-  \caption{Higgsino pair production $\widetilde\chi_2^0\widetilde\chi_3^0$
+  \caption{Higgsino pair production $\N_2\N_3$
     cross section (left panel), calculated using
@@
     of $\mu$ for $M_1=25$ GeV. However, it should be noted that the dependence
-    on $M_1$ is very weak.
-\Shufang{Could you use $\mu$ for both xlabels?
-The CS and Br will depend slightly on the sign of mu.
-Since we do use positive mu in our analyses, let's label it this way.
-I have a footnote in intro to explain the sign effect of mu.
-Also, change right panel, ylabel to be either Br or Branching Fraction.}
+    on $M_1$ is very weak.  \Shufang{Could you use $\mu$ for both xlabels?  The
+    CS and Br will depend slightly on the sign of mu.  Since we do use positive
+  mu in our analyses, let's label it this way.  I have a footnote in intro to
+explain the sign effect of mu.  Also, change right panel, ylabel to be either
+Br or Branching Fraction.}
 }
@@
     \toprule
-    Stage & $\N_{2,3}\widetilde{\chi}^\pm_{1}$ & $\N_2\N_3$\\
+    Stage & $\N_{2,3}\C_1$ & $\N_2\N_3$\\
     \midrule
@@
   \caption{Comparison of Higgsino pair production cross-sections for
-    $(\widetilde{\chi}_{2,3}^0\widetilde{\chi}^\pm_{1})$ and
+    $(\N_{2,3}\C_1)$ and
     $(\N_{2}\N_{3})$, for $\mu\approx 1$ TeV, at a 100
     TeV \emph{pp} collider. 
-    The pair-production cross section for $\N_{2,3}\widetilde{\chi}^\pm_1$ is taken from
-    \cite{Gori:2014oua}, while the pair-production cross-section for $\N_2\N_3$ is calculated at Next-to-Leading Order (NLO) using Prospino2.
-The branching ratios to the diboson intermediate states are calculated using SUSY-HIT, and the branching ratios to the SM final states are taken from
-    \cite{Olive:2016xmw}.    }
+    The pair-production cross section for $\N_{2,3}\C_1$ is taken from
+    \cite{Gori:2014oua}, while the pair-production cross-section for $\N_2\N_3$
+    is calculated at Next-to-Leading Order (NLO) using Prospino2. The branching
+    ratios to the diboson intermediate states are calculated using SUSY-HIT,
+    and the branching ratios to the SM final states are taken from
+    \cite{Olive:2016xmw}.}
   \label{tab:xsections}
@@
       Representative kinematic
-  distributions of these variables for signal events of $\mu=1$ TeV Higgsinos NLSP and a $M_1=25$ GeV Bino LSP, as well as $tt$ and $tbW$ backgrounds are
+  distributions of these variables for signal events of $\mu=1$ TeV Higgsinos
+  NLSP and a $M_1=25$ GeV Bino LSP, as well as $tt$ and $tbW$ backgrounds are
   shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
   $\slashed{E}_{T}$,  and  $m_{\ell^+\ell^-}$cuts.   
-\Shufang{BG generator level mll and MET cut (MET bigger tan 100 GeV), or cut level mll and MET cut (MET bigger than 400 GEV)?
-Both signal and backgrounds?} The
+  \Shufang{BG generator level mll and MET cut (MET bigger tan 100 GeV), or cut
+    level mll and MET cut (MET bigger than 400 GEV)? Both signal and
+  backgrounds?} The
   distribution for the \emph{bbWW} background is not shown, since it is negligible in
   comparison to the others.   We can see that the distribution of $M_R$ is peaked
-  around 1 TeV for the signal, which is consistent with what we would expect as   it corresponds to the mass difference between the NLSP and LSP.
-The $tt$ background peaks around 500 GeV, while the distribution of $tbW$ background almost overlaps with that of the signal process.
-Similar behaviour also appears for $M_T^R$ distributions.
+  around 1 TeV for the signal, which is consistent with what we would expect as
+  it corresponds to the mass difference between the NLSP and LSP.  The $tt$
+  background peaks around 500 GeV, while the distribution of $tbW$ background
+  almost overlaps with that of the signal process.  Similar behaviour also
+  appears for $M_T^R$ distributions.  
   For this mass combination, requiring $M_R >$ 800
@@
 
- Comparing to the reach of multi-lepton channel in Ref.~\cite{Gori:2014oua}, with an  exclusion limit of Higgsino mass up to 2.8 TeV or a discovery reach of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$ channel in our study is less.
-However, the reach for multi-lepton channel reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV) for discovery (exclusion).
-The reach for $Zh+\met$ search in our study exceed that of the multi-lepton search for larger LSP masses.
-In particular,
- the BDT reach for LSP mass with $Zh+\met$ search exceeds the reach for multi-lepton analyses by about 300 GeV.
+Comparing to the reach of multi-lepton channel in Ref.~\cite{Gori:2014oua},
+with an  exclusion limit of Higgsino mass up to 2.8 TeV or a discovery reach
+of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$
+channel in our study is less.  However, the reach for multi-lepton channel
+reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV)
+for discovery (exclusion).   The reach for $Zh+\met$ search in our study
+exceed that of the multi-lepton search for larger LSP masses.  In particular,
+the BDT reach for LSP mass with $Zh+\met$ search exceeds the reach for
+multi-lepton analyses by about 300 GeV.
 
@@
 
-In this paper, we examined the discovery potential for a 100 TeV $pp$ collider For 
-pair-produced heavy Higgsino NLSPs with Bino LSP, via 
-intermediate $Z$ and $h$ bosons that decay to a pair of leptons and $b$ quarks respectively:  $\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
+In this paper, we examined the discovery potential for a 100 TeV $pp$ collider
+For pair-produced heavy Higgsino NLSPs with Bino LSP, via intermediate $Z$ and
+$h$ bosons that decay to a pair of leptons and $b$ quarks respectively:
+$\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
 
@@
 The collimation of the $b$ jets, along with the fact that we take into account
-detector effects using Delphes, result in a relatively lower reach in the high $\mu$, low
-$M_1$ region than the multilepton analysis in~\cite{Gori:2014oua}, which is
-able to exclude Higgsinos up to a mass of 2.85 TeV for massless Binos, or discover Higgsinos up to a mass of 1.8 TeV.   The reach
-of our analysis, however,  is higher in the region where the difference between
-$\mu$ and $M_1$ is smaller. This is consistent with our usage of the razor
-variable $M_R$, which is sensitive to the mass difference between the parent
-Higgsino and daughter Bino.
+detector effects using Delphes, result in a relatively lower reach in the high
+$\mu$, low $M_1$ region than the multilepton analysis in~\cite{Gori:2014oua},
+which is able to exclude Higgsinos up to a mass of 2.85 TeV for massless Binos,
+or discover Higgsinos up to a mass of 1.8 TeV.   The reach of our analysis,
+however,  is higher in the region where the difference between $\mu$ and $M_1$
+is smaller. This is consistent with our usage of the razor variable $M_R$,
+which is sensitive to the mass difference between the parent Higgsino and
+daughter Bino.
 

### 2019-07-23 main.tex
removing abs value bars around mu in dm contour plot
Updates from Overleaf

@@
     of $\mu$ for $M_1=25$ GeV. However, it should be noted that the dependence
-    on $M_1$ is very weak.  \Shufang{Could you use $\mu$ for both xlabels?  The
-    CS and Br will depend slightly on the sign of mu.  Since we do use positive
-  mu in our analyses, let's label it this way.  I have a footnote in intro to
-explain the sign effect of mu.  Also, change right panel, ylabel to be either
-Br or Branching Fraction.}
+    on $M_1$ is very weak.
 }

### 2019-07-23 main.tex
Addressing comments about generator level cuts for signal and bg

@@
     level mll and MET cut (MET bigger than 400 GEV)? Both signal and
-  backgrounds?} The
-  distribution for the \emph{bbWW} background is not shown, since it is negligible in
+  backgrounds?} \Adarsh{The plots in figure 2 show distributions at the reconstructed level,
+  so they have the generator level cuts and the reconstructed level cuts. 
+  For the signal, no generator-level cuts are applied.
+  For the background, the $80 < m_{ll} < 100 $ GeV and  $\met > 100$ GeV
+  generator level cuts are applied.}
+  The distribution for the \emph{bbWW} background is not shown, since it is negligible in
   comparison to the others.   We can see that the distribution of $M_R$ is peaked
@@
 $b$-tagged jets, and calculated a number of kinematic variables for each event.
-  \Shufang{So singal event does not have mll and MET parton level cuts while BG events have those two cuts. right?}   We then
+  \Shufang{So singal event does not have mll and MET parton level cuts 
+  while BG events have those two cuts. right?} \Adarsh{Right.}   We then
 placed these kinematic variables in an array, with each row corresponding to an
@@
 \centering
-%\includegraphics[width=0.6\textwidth]{images/combined.pdf}
-\includegraphics[width=0.6\textwidth]{images/dm_100_TeV_contours.png}
+%\includegraphics[width=0.6\textwidth]{images/dm_100_TeV_contours.png}
+\input{images/dm_100_TeV_contours.pgf}
 
@@
   for 100 TeV $pp$ collider with an integrated luminosity of 3000 fb$^{-1}$.
-\Adarsh{  I could change the xlabel
-to $\mu$ instead of $|\mu|$, but isn't $|\mu|$ more accurate, since $\mu$ can
-be positive or negative?} \Shufang{Yes, change to $\mu$.  Sign of mu has a small effect.  Since we use positive mu, let's label it this way.}
 }

### 2019-07-23 main.tex
Pushing overleaf changes

@@
 \author[b]{and Shufang Su}
-\affiliation[a]{School of Information, University of Arizona, Tucson, AZ 85718 , USA}
+\affiliation[a]{School of Information, University of Arizona, Tucson, AZ 85721 , USA}
 \affiliation[b]{Department of Physics, University of Arizona, Tucson, AZ 85718, USA}
@@
 \abstract{% 
-
   A 100 TeV proton-proton collider will be an extremely effective way to probe
@@
   channel extends the multi-lepton search limits, especially in the region
-  where the mass difference between Higgsino NLSP and Bino LSP is smaller.
+  where the mass difference between Higgsino NLSP and Bino LSP is small.
 }
@@
 beyond the Standard Model (SM) of particle physics. Indeed, given that there is
-far more dark matter in the Universe than there is baryonic matter, determining
+far more dark matter in the universe than there is baryonic matter, determining
 its precise nature is one of the most exciting challenges in particle physics
@@
 constraints and phenomenological considerations, the lightest of the MSSM
-particles known as the neutralinos emerges as the most attractive candidates
+particles known as the neutralinos emerges as the most attractive candidate
 for the LSP \cite{Bertone:2004pz}.
@@
 studying Higgsinos is that the parameter $\mu$ that governs its mass plays an
-important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, which
-tends to be small by naturalness considerations.   Finding Higgsinos has
-traditionally been more challenging than finding Winos, due to their smaller
-production rate. This, however, can be remedied by the increased  production
-cross sections and luminosities at a 100 TeV $pp$ collider.
+important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, and
+is driven to be relatively small by naturalness considerations. 
+Finding Higgsinos has traditionally been more challenging than finding Winos,
+due to their smaller production rate.
+This, however, can be remedied by the increased production cross sections and 
+luminosities at a 100 TeV $pp$ collider.
 

### 2019-07-23 main.tex
Updates from Overleaf

@@
 \usepackage{booktabs, longtable}
+\usepackage{microtype}
 \bibliographystyle{JHEP.bst}
@@
 \renewcommand{\H}{\widetilde{H}^0}
+\newcommand{\W}{\widetilde{W}^0}
 \newcommand{\B}{\widetilde{B}^0}
@@
 \newcommand{\C}{\widetilde{\chi}^\pm}
-\newcommand{\image}[2]{\parbox{#1\textwidth}{\includegraphics[width=#1\textwidth]{images/#2.pdf}}}
+\newcommand{\image}[2]{\parbox{#1\textwidth}{%
+\includegraphics[width=#1\textwidth]{images/#2.pdf}}
+}
 \newcommand{\met}{{\slashed{E}_T}}
@@
 the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a
-neutral SM boson (\emph{Z/h}) with a branching ratio of 100\%.  Searches for
+neutral SM boson (\emph{Z/h}) with a branching fraction of 100\%.  Searches for
 Higgsino NLPs with a Bino LSP  via  multi-lepton final states have been studied
@@
 $\widetilde\chi_{1}^+\widetilde\chi_1^-$. In this paper, we attempt to exploit
-the relatively high branching ratio of the SM Higgs boson to \emph{b} quarks,
-and study the potential of the channel of $\N_2\N_3\rightarrow Zh
-\N_1\N_1\rightarrow bb\ell\ell \met$.
+the relatively high branching fraction of the SM Higgs boson to \emph{b} quarks,
+and study the potential of the $\N_2\N_3\rightarrow Zh
+\N_1\N_1\rightarrow bb\ell\ell \met$ channel.
 
@@
 A 100 TeV $pp$ collider would open up an immense number of physics
-opportunities not afforded to a 14 TeV LHC, including exploring the most
+opportunities not afforded to the 14 TeV LHC, including exploring the most
 interesting regions of the split SUSY parameter space
@@
 Super Proton Proton Collider (SppC)  in China \cite{CEPC}.  As the next energy
-frontier machine, it is of crucial importance to fully explore the physics
+frontier machine, it is crucial to fully explore the physics
 potential of a 100 TeV $pp$ collider, especially for new particles that are
@@
 SM Higgs boson in 2012 was done with the help of neural networks
-\cite{Aad:2012tfa} and boosted decision trees (BDT)
+\cite{Aad:2012tfa} and boosted decision trees (BDTs)
 \cite{Chatrchyan:2012xdj}.
@@
 analysis strategies for both traditional cut-and-count analyses and analyses
-performed using BDT. In Sec.~\ref{sec:results}, we present the results of our
+performed using BDTs. In Sec.~\ref{sec:results}, we present the results of our
 analyses, i.e. the expected 5 $\sigma$ discovery and 95\% C.L. exclusion
@@
 ($\N_1,\N_2,\N_3,\N_4$), which are mixtures of the Bino, Wino, and two neutral
-Higgsinos: ($\B,\widetilde{W}^0,\H_d,\H_u$). In the basis of these gauge
+Higgsinos: ($\B,\W,\H_d,\H_u$). In the basis of these gauge
 eigenstates, the mass matrix of the neutralinos can be written as
@@
 \newcommand{\cb}{ c_\beta}
-\newcommand{\cw}{ c_W}
+\newcommand{\cw}{ c_{\theta_W}}
 \newcommand{\sinb}{ s_\beta}
@@
 
-\noindent where we employ the notation $s_W, c_W = \sin\theta_W, \cos\theta_W$
-for $\theta_W$ being the Weinberg mixing angle. $s_\beta, c_\beta$ are defined
-accordingly with $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
+\noindent where we employ the notation $s_\theta, c_\theta = \sin\theta, \cos\theta$. Here,  $\theta_W$ is the Weinberg mixing angle, 
+and $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
 expectation values of $H_u^0$ and $H_d^0$, with $v_u^2+v_d^2=v^2=(246\ {\rm
 GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
-Bino, Wino, and Higgsinos.  The mass eigenstates are usually labeled as
-$\chi_i^0$ for $i=1 \ldots 4$ with increasing mass eigenvalues.
-
-In the limit of $\mz \ll |\mu\pm M_1|, |\mu\pm M_2|,$ the mass eigenstates
+the Bino, Wino, and the Higgsino, respectively.
+The mass eigenstates are labeled as $\N_i$ for $i=1 \ldots 4$ with increasing mass eigenvalues.
+In the limit where $\mz \ll |\mu\pm M_1|, |\mu\pm M_2|,$ the mass eigenstates
 are, to good approximation, a nearly pure Bino, $\B$, with mass $M_1$,
-a nearly pure Wino, $\widetilde{W}^0$, with mass $M_2$, and nearly pure Higgsinos
+a nearly pure Wino, $\W$, with mass $M_2$, and nearly pure Higgsinos
 $\H_{1,2} = (\H_u \pm \H_d)/\sqrt{2}$, with mass
@@
 identified. Among the multi-lepton searches for Higgsinos, the trilepton
-searches: $\N_{2,3}\C_1\pm\rightarrow WZ\N_1\N_1\rightarrow \ell\ell\ell +
+searches: $\N_{2,3}\C_1\rightarrow WZ\N_1\N_1\rightarrow \ell\ell\ell +
 \met$, with $\ell=e, \ \mu$,  have the best reach, due to the relatively high
 production cross-section of chargino-neutralino pairs combined with the large
-reduction in $t\overline{t}$ and QCD backgrounds obtained by requiring three
+reduction in $t\overline{t}$ and QCD backgrounds from requiring three
 leptons.  Higgsino NLSPs can be excluded at 95\% C.L. with mass up to 2.8 TeV
-or be discovered with  mass up to 1.8 TeV, for a massless Bino LSP.   The reach
-reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV)
+or be discovered with  mass up to 1.8 TeV, for a massless Wino LSP.   The reach
+reduces for larger $M_1$, and vanishes for $M_1\gtrsim 600$ GeV (1000 GeV)
 for discovery (exclusion).  Multilepton searches with \emph{Zh} and \emph{ZZ}
@@
 pair-production cross-section of neutral Higgsinos, combined with the low
-branching ratio of \emph{Z/h} to leptons. However, if we move beyond
+branching fraction of \emph{Z/h} to leptons. However, if we move beyond
 multilepton searches, the channel with \emph{Zh} (originally suggested in
-\cite{Han:2013kza}) as the intermediate dibosons emerges as a possible
+Ref.~\cite{Han:2013kza}) as the intermediate dibosons emerges as a possible
 competitor to the \emph{WZ} channel.
@@
 right panel of Fig.~\ref{fig:xsection_plot} shows the decay branching fractions
-of $\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated in SUSY-HIT
+of $\chi_{2,3}^0\rightarrow Z/h \chi_1^0$, as calculated by SUSY-HIT
 \cite{Djouadi:2006bz}.  While one of the Higgsinos mostly decays to $Z$, the
@@
 
-\noindent become comparable  to trilepton processes, as shown in table
-\ref{tab:xsections}. $Zh+\met$ signal thus provide an alternative discovery
+\noindent become comparable  to trilepton processes, as shown in Table
+\ref{tab:xsections}. Thus, the $Zh+\met$ signal provides an alternative discovery
 channel for Higgsinos. The signal contains two \emph{b}-jets, two same flavor,
@@
     ratios to the diboson intermediate states are calculated using SUSY-HIT,
-    and the branching ratios to the SM final states are taken from
+    and the branching fractions to the SM final states are taken from
     \cite{Olive:2016xmw}.}
@@
 \cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
-For neutralino-chargino pair production with $WZ$ and $WH$ topologies, the 95\%
-C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for $WZ$, $WH$
-and an equal mixture of $WZ+WH$ topology, with the most strongest limits from
-the multi-lepton searches.  For neutralino pair production with $ZZ$, $ZH$ and
-$HH$ topologies~\footnote{While such searches assume gravitino LSP with
+For neutralino-chargino pair production with \emph{WZ} and \emph{WH} topologies, the 95\%
+C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for \emph{WZ}, \emph{WH}
+and an equal mixture of \emph{WZ}+\emph{WH} topology, with the strongest limits coming from
+the multi-lepton searches.  For neutralino pair production with \emph{ZZ, ZH}, and \emph{HH} topologies~\footnote{While such searches assume gravitino LSP with
 Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino

### 2019-07-25 main.tex
Preparing for arXiv submission

@@
 \usepackage{microtype}
+\usepackage{soul}
 \bibliographystyle{JHEP.bst}
@@
 \newcommand{\met}{{\slashed{E}_T}}
+\newcommand{\cb}{ c_\beta}
+\newcommand{\cw}{ c_{\theta_W}}
+\newcommand{\sinb}{ s_\beta}
+\newcommand{\sw}{ s_W}
+\newcommand{\mz}{ m_Z}
 
-\title{Higgs Assisted Razor Search for Higgsinos at 100 TeV}
+\title{Higgs Assisted Razor Search for Higgsinos at a 100 TeV $pp$ Collider}
 \author[a]{Adarsh Pyarelal}
@@
   In this paper, we describe a search strategy  for discovering pair-produced
-  Higgsino-like next-to-lightest supersymmetric particles (NLSP)  at a 100 TeV
+  Higgsino-like next-to-lightest supersymmetric particles (NLSPs)  at a 100 TeV
   hadron collider that decay to Bino-like lightest supersymmetric particle
-  (LSP) via intermediate $Z$ and SM Higgs bosons that in turn decay to a pair
+  (LSP) via intermediate $Z$ and SM Higgs boson that in turn decay to a pair
   of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
@@
   potential for machine learning techniques to boost the power of our searches.
-  Using this analysis, Higgsinos up to 1.4 TeV can be discovered for Binos with
-  masses of about
+  Using this analysis, Higgsinos up to 1.4 TeV can be discovered  at 5 $\sigma$ level for a Bino with
+  mass of about
   0.9 TeV using 3000 fb$^{-1}$ of data.  Additionally, Higgsinos up to 1.8
-  TeV can be excluded for Binos with masses of about 1.4 TeV at 95\% C.L.   This search
+  TeV can be excluded  at 95\% C.L. for a Bino with mass of about 1.4 TeV。   This search
   channel extends the multi-lepton search limits, especially in the region
-  where the mass difference between Higgsino NLSP and Bino LSP is small.
+  where the mass difference between the Higgsino NLSPs and the Bino LSP is small.
 }
@@
 beyond the Standard Model (SM) of particle physics. Indeed, given that there is
-far more dark matter in the universe than there is baryonic matter, determining
+far more dark matter in the Universe than there is baryonic matter, determining
 its precise nature is one of the most exciting challenges in particle physics
-today.  One promising group of candidate for dark matter is the class of stable
+today.  One promising group of candidates for dark matter is the class of stable
 particles known as weakly interacting massive particles (WIMPs). These
 particles arise naturally in many extensions of the SM that are motivated by
-the need to stabilize the electroweak scale. One of the most studied extensions
-to the SM is the Minimal Supersymmetric Standard Model (MSSM), which predicts a
+the need to stabilize the electroweak scale. One of the most heavily studied extensions
+is the Minimal Supersymmetric Standard Model (MSSM), which predicts a
 `supersymmetric partner', or \emph{superpartner}, for each SM
@@
 determined by the mass hierarchy of the superpartners, which in turn depends on
-how supersymmetry is broken.  However, taking into account experimental
+the mechanism of supersymmetry breaking.  However, taking into account experimental
 constraints and phenomenological considerations, the lightest of the MSSM
@@
 electroweakinos and their species.  In this paper, we will focus on the
-discovery potential of the neutralinos and charginos at the 100 TeV $pp$
+discovery potential of the neutralinos and charginos at a 100 TeV $pp$
 collider.
@@
 % Point to review papers for enumeration of studies
-The decay patterns of the electroweakinos (Winos, Binos, and Higgsinos) depend
+The decay patterns of the electroweakinos (Winos, Bino, and Higgsinos) depend
 on the hierarchy of the MSSM parameters $M_1, M_2$, and $\mu$~\footnote{For our
@@
 which roughly determine the masses of the Bino, Winos, and Higgsinos,
-respectively~\cite{Han:2013kza}.  In this paper, we consider the Higgsino NLSP
+respectively~\cite{Han:2013kza}.  In this paper, we consider the Higgsino NLSPs
 and Bino LSP scenario with $M_1 < \mu \ll M_2$.  One of the motivations for
-studying Higgsinos is that the parameter $\mu$ that governs its mass plays an
+studying Higgsinos is that the parameter $\mu$ that governs their masses plays an
 important role in electroweak symmetry breaking~\cite{Acharya:2014pua}, and
@@
 Finding Higgsinos has traditionally been more challenging than finding Winos,
-due to their smaller production rate.
+due to their smaller production rates.
 This, however, can be remedied by the increased production cross sections and 
@@
 
-Since the Bino is the only supersymmetric particle lighter than the Higgsino in
-the mass hierarchy we consider, the neutral Higgsino will decay to a Bino and a
+Since the Bino is the only supersymmetric particle lighter than the Higgsinos in
+the mass hierarchy we consider, the neutral Higgsinos will decay to a Bino and a
 neutral SM boson (\emph{Z/h}) with a branching fraction of 100\%.  Searches for
-Higgsino NLPs with a Bino LSP  via  multi-lepton final states have been studied
-in Ref.~\cite{Gori:2014oua} at a 100 TeV $pp$ collider, for pair production of
+Higgsino NLSPs with Bino LSPs via  multi-lepton final states have been studied
+in Ref.~\cite{Gori:2014oua} for a 100 TeV $pp$ collider, for pair production of
 $\N_{2,3}\C_1$ and
 $\widetilde\chi_{1}^+\widetilde\chi_1^-$. In this paper, we attempt to exploit
-the relatively high branching fraction of the SM Higgs boson to \emph{b} quarks,
+the relatively large branching fraction of the SM Higgs boson to \emph{b} quarks,
 and study the potential of the $\N_2\N_3\rightarrow Zh
@@
 The rest of the paper is structured as follows. In Sec.~\ref{sec:model}, we
-describe our model and search channel in more detail, and list the existing
+describe our model and search channel in more detail, and review the existing
 experimental search bounds. In Sec.~\ref{sec:analysis}, we describe our
-analysis strategies for both traditional cut-and-count analyses and analyses
+analysis strategies for both traditional cut-and-count analysis and analysis
 performed using BDTs. In Sec.~\ref{sec:results}, we present the results of our
-analyses, i.e. the expected 5 $\sigma$ discovery and 95\% C.L. exclusion
+analyses, i.e. the expected 5$\sigma$ discovery and 95\% C.L. exclusion
 reaches. Finally, we conclude with the implications in
@@
 eigenstates, the mass matrix of the neutralinos can be written as
-
-\newcommand{\cb}{ c_\beta}
-\newcommand{\cw}{ c_{\theta_W}}
-\newcommand{\sinb}{ s_\beta}
-\newcommand{\sw}{ s_W}
-\newcommand{\mz}{ m_Z}
-
 \begin{align}
@@
 \end{align} 
-
-\noindent where we employ the notation $s_\theta, c_\theta = \sin\theta, \cos\theta$. Here,  $\theta_W$ is the Weinberg mixing angle, 
+where we employ the notation $s_\theta, c_\theta = \sin\theta, \cos\theta$. Here,  $\theta_W$ is the Weinberg mixing angle, 
 and $\tan\beta= v_u/v_d$, where $v_u$ and $v_d$ are the vacuum
@@
 GeV})^2$. The parameters $M_1$, $M_2$, and $\mu$ are the mass parameters of
-the Bino, Wino, and the Higgsino, respectively.
+the Bino, Wino, and the Higgsinos, respectively.
 The mass eigenstates are labeled as $\N_i$ for $i=1 \ldots 4$ with increasing mass eigenvalues.
@@
 their mass spectra \cite{Han:2013kza}.  Phenomenological collider studies on
-finding electroweakinos with a small mass splitting of about 0.1 - 50 GeV at a
-100 TeV collider can be found in \cite{Low:2014cba, Bramante:2014tba,
-Berlin:2015aba, Cirelli:2014dsa}. The projected exclusion reaches for pure Wino
-LSPs (with a mass splitting of 164.6 MeV \cite{Ibe:2012sx}) at a 100 TeV
-collider using the monojet channel is $\sim1.4$~TeV.  The reach
-can be increased to $\sim3$ TeV using a disappearing tracks search.
+finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at a
+100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
+Berlin:2015aba, Cirelli:2014dsa}.
+For $3\ \text{ab}^{-1}$ of data, the projected exclusion reaches for pure Wino
+LSPs using the monojet channel is about $1.4$~TeV.  The reach
+can be increased to $\sim3$ TeV with a disappearing tracks search.
 Neutralinos up to 1 TeV can be excluded for mass splittings of about 20-30 GeV,
 using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
-with masses up to 1.5 TeV and $\sim 1$~GeV inter-state mass splitting can be
-discovered at a 100 TeV collider with $\sim7 \text{ab}^{-1}$ of data.
-
-  \Shufang{Say a few words about typical
-  search strategy there.} \Adarsh{Yes, I focused more on well separated spectra
-  since that is more similar to our case - should I add more details for the
-  0.1 - 50 GeV compressed spectra studies?} \Shufang{Add a couple sentences
-  here of the search strategy for the small mass splitting case.}
-  \Adarsh{I added a couple of sentences.}
+with masses up to 1.5 TeV for an inter-state mass splitting of around 1 GeV  can be
+discovered at a 100 TeV $pp$ collider with $\sim7\ \text{ab}^{-1}$
+of data \cite{Bramante:2014tba}.
 
@@
 \noindent where $\widetilde{\chi}_{i,j}$ can be a neutralino or chargino, $\N_1$
-is the lightest neutralino, and $V$ being any of the SM gauge bosons $W$, $Z$
+is the lightest neutralino, and $V$ is any of the SM gauge bosons $W$, $Z$
 or scalar $h$.  These searches work well since the large mass difference
@@
 leptons.  Higgsino NLSPs can be excluded at 95\% C.L. with mass up to 2.8 TeV
-or be discovered with  mass up to 1.8 TeV, for a massless Wino LSP.   The reach
+or be discovered with  mass up to 1.8 TeV, for a massless Bino LSP.   The reach
 reduces for larger $M_1$, and vanishes for $M_1\gtrsim 600$ GeV (1000 GeV)
@@
 competitor to the \emph{WZ} channel.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
+  \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
+  \caption{Higgsino pair production $\N_2\N_3$
+    cross section (left panel), calculated using
+    Prospino2~\cite{Beenakker:1999xh},  and decay branching fractions
+    (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
+    of $\mu$ for $M_1=25$ GeV.
+}
+  \label{fig:xsection_plot}
+\end{figure}
 
@@
 
-\noindent become comparable  to trilepton processes, as shown in Table
+\noindent become comparable to the trilepton processes, as shown in Table
 \ref{tab:xsections}. Thus, the $Zh+\met$ signal provides an alternative discovery
@@
 from a \emph{t}, and \emph{bbWW} with no intermediate $s$-channel top quarks.
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=0.49\textwidth]{images/xsection_plot.pdf}
-  \includegraphics[width=0.49\textwidth]{images/br_plot.pdf}
-  \caption{Higgsino pair production $\N_2\N_3$
-    cross section (left panel), calculated using
-    Prospino2~\cite{Beenakker:1999xh},  and decay branching fractions
-    (right panel), calculated in SUSY-HIT~\cite{Djouadi:2006bz},  as a function
-    of $\mu$ for $M_1=25$ GeV. However, it should be noted that the dependence
-    on $M_1$ is very weak.
-}
-  \label{fig:xsection_plot}
-\end{figure}
 
@@
 \cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
-For neutralino-chargino pair production with \emph{WZ} and \emph{WH} topologies, the 95\%
-C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for \emph{WZ}, \emph{WH}
-and an equal mixture of \emph{WZ}+\emph{WH} topology, with the strongest limits coming from
-the multi-lepton searches.  For neutralino pair production with \emph{ZZ, ZH}, and \emph{HH} topologies~\footnote{While such searches assume gravitino LSP with
-Higgsino NLSP, the limits are still relevant for our Higgsino NLSP with Bino
+For neutralino-chargino pair production with \emph{WZ} and \emph{Wh} topologies, the 95\%
+C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for \emph{WZ}, \emph{Wh} and an equal mixture of \emph{WZ}+\emph{Wh} topology, with the strongest limits coming from
+the multi-lepton searches.
+For neutralino pair production with \emph{ZZ, Zh}, and \emph{hh} topologies\footnote{While such searches assume a gravitino LSP with Higgsino NLSPs, the limits are still relevant for our Higgsino NLSPs - Bino
 LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
-multi-$b$ jets searches, depending on the decay branching fractions of Higgsino
-NLSP.
+multi-$b$ jets searches, depending on the decay branching fractions of the Higgsino NLSPs.
 
@@
 motivated by the fact that due to the large mass difference between the Higgsino
-NLSP and the Bino LSP in our search channel, the intermediate $Z$ bosons will be
+NLSPs and the Bino LSP in our search channel, the intermediate $Z$ bosons will be
 highly boosted, and the leptons to which they decay will be highly collimated.
@@
       Representative kinematic
-  distributions of these variables for signal events of $\mu=1$ TeV Higgsinos
-  NLSP and a $M_1=25$ GeV Bino LSP, as well as $tt$ and $tbW$ backgrounds are
-  shown in Fig.~\ref{fig:razor_histos}, after the trigger, identification,
-  $\slashed{E}_{T}$,  and  $m_{\ell^+\ell^-}$cuts.   
-  \Shufang{BG generator level mll and MET cut (MET bigger tan 100 GeV), or cut
-    level mll and MET cut (MET bigger than 400 GEV)? Both signal and
-  backgrounds?} \Adarsh{The plots in figure 2 show distributions at the reconstructed level,
-  so they have the generator level cuts and the reconstructed level cuts. 
-  For the signal, no generator-level cuts are applied.
-  For the background, the $80 < m_{ll} < 100 $ GeV and  $\met > 100$ GeV
-  generator level cuts are applied.}
+  distributions of these variables for a signal benchmark point with $\mu=1$ TeV and $M_1=25$ GeV, as well as $tt$ and $tbW$ backgrounds are
+  shown in Fig.~\ref{fig:razor_histos}, after the trigger and identification cuts.
   The distribution for the \emph{bbWW} background is not shown, since it is negligible in
@@
   around 1 TeV for the signal, which is consistent with what we would expect as
-  it corresponds to the mass difference between the NLSP and LSP.  The $tt$
+  it corresponds to the mass difference between the NLSPs and the LSP.  The $tt$
   background peaks around 500 GeV, while the distribution of $tbW$ background
-  almost overlaps with that of the signal process.  Similar behaviour also
-  appears for $M_T^R$ distributions.  
+  almost overlaps with that of the signal process.
+  Similar behaviour is also seen in the $M_T^R$ distributions.  
   For this mass combination, requiring $M_R >$ 800
@@
 \caption{Normalized distributions of the razor kinematic variables $M_R$
-  (left) and $M_T^R$ (right) for signal process with $\mu=1$ TeV Higgsinos NLSP and a $M_1=25$ GeV Bino LSP,  as well as the dominant $tt$ and $tbW$ backgrounds,
-  after the trigger, identification,  $\slashed{E}_{T}$ and $m_{\ell^+\ell^-}$ cuts.}
+  (left) and $M_T^R$ (right) for  a signal benchmark point with $\mu=1$ TeV and $M_1=25$ GeV,
+  as well as the dominant $tt$ and $tbW$ backgrounds
+  after the trigger and identification cuts.}
 \label{fig:razor_histos}
@@
   \input{tables/cutflowtable.tex}
-  \caption{Representative cut flow table for the benchmark point $\mu=1$ TeV,
+  \caption{Representative cut flow table for a signal benchmark point with $\mu=1$ TeV,
     $M_1 = 25$ GeV at 100  TeV $pp$ collider, for a traditional cut-and-count analysis. All cross sections
@@
 Table \ref{tab:cc_cutflowtable} shows the cut efficiencies for a representative
-signal benchmark point with a $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
+signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
 cross-sections of the backgrounds are obtained from MadEvent after performing the MLM matching procedure. Their small size reflects
@@
 events that passed the lepton trigger, contained two SFOS leptons and two
-$b$-tagged jets, and calculated a number of kinematic variables for each event.
-  \Shufang{So singal event does not have mll and MET parton level cuts 
-  while BG events have those two cuts. right?} \Adarsh{Right.}   We then
+$b$-tagged jets, and calculated a number of kinematic variables for each event.   We then
 placed these kinematic variables in an array, with each row corresponding to an
 event, and the columns corresponding to the kinematic variables. A mixture of
-low-level and high level kinematic variables was shown to have the greatest
+low-level and high-level kinematic variables was shown to have the greatest
 effectiveness. The kinematic variables chosen were $m_{\ell\ell}$, $m_{bb}$,
 $M_R$, $M_T^R$, $\slashed{E}_T,$ the total hadronic transverse energy $H_T$,
-and transverse momenta of individual final state leptons and $b$-quarks:
+and the transverse momenta of individual final state leptons and $b$-quarks:
 $p_T^{\ell_1}$, $p_T^{\ell_2}$, $p_T^{b_1}$, and $p_T^{b_2}$. We then divided
@@
 the significance for each signal benchmark point. The distribution of scores
-for the specific benchmark point ($\mu$ = 1 TeV, $M_1$ = 25 GeV) is shown in
-figure \ref{fig:bdt_response}. We observe that there is an appreciable
+for the representative benchmark point ($\mu$ = 1 TeV, $M_1$ = 25 GeV) is shown in Fig.~\ref{fig:bdt_response}. We observe that there is an appreciable
 separation between the signal and background distributions.
@@
 \caption{Distribution of the decision function of the gradient boosted decision
-tree classifier algorithm for signal ($\mu = 1$ TeV, $M_1 = 25$ GeV) and
-backgrounds. }
+tree classifier for   the representative signal benchmark point ($\mu = 1$ TeV, $M_1 = 25$ GeV) and backgrounds.}
 \label{fig:bdt_response}
@@
   \caption{Representative cut flow table for the same benchmark point and
-    integrated luminosity as in table \ref{tab:cc_cutflowtable}, but using a
-    boosted decision tree (BDT) analysis instead. The preselection is equivalent
-    to the trigger and identification cuts listed in table
+    integrated luminosity as in Table \ref{tab:cc_cutflowtable}, but using a BDT  analysis instead. The preselection is equivalent
+    to the trigger and identification cuts listed in Table
     \ref{tab:cc_cutflowtable}. As before, all the cross sections are in
@@
 Table \ref{tab:bdt_cutflowtable} shows the cut efficiencies for the same
-representative benchmark point as in table \ref{tab:cc_cutflowtable}, but this
+representative benchmark point as in Table \ref{tab:cc_cutflowtable}, but this
 time for a boosted decision tree analysis. We observe that the statistical
@@
 estimates of the significance $S/\sqrt{B}$, we set a lower bound of 3 for the
-number of MC events after cuts for each background component, corresponding to
+number of Monte Carlo (MC) events after cuts for each background component, corresponding to
 the 95\% confidence interval for a Poisson distribution.
@@
 1.35 TeV.  The boosted decision
-tree analysis, improves this reach -- it is able to discover Higgsinos up to
+tree analysis improves this reach -- it is able to discover Higgsinos up to
 1.4 TeV, and exclude them up to 1.8 TeV in favorable points in parameter space.
@@
 about 900 GeV and exclude them up to 1.4 TeV. Since the background left after
-cut is relatively low, we do not include systematic errors in these estimates.
+cuts is relatively low, we do not include systematic errors in these estimates.
 
-Comparing the BDT results with that of the cut-and-count bases analyses, the improvement is substantial, but perhaps not spectacular. However, it should
+Comparing the BDT results with that of the cut-and-count bases analysis, the improvement is substantial, but perhaps not spectacular. However, it should
 be kept in mind that this is probably a conservative estimate. Since we reserve
@@
 
-In regions with large mass differences between the LSP and NLSP, the reach is
+In regions with large mass differences between the LSP and NLSP, the reach in $\mu$ is
 reduced.  This is because the intermediate SM Higgs boson will be highly boosted, and
 thus decay into a highly collimated pair of $b$-jets. The extent to which this
-affects our results can be estimated from table \ref{tab:cc_cutflowtable}. We
+affects our results can be estimated from Table \ref{tab:cc_cutflowtable}. We
 see that requiring two $b$-tagged jets reduces our signal cross-section by
@@
 
-Comparing to the reach of multi-lepton channel in Ref.~\cite{Gori:2014oua},
-with an  exclusion limit of Higgsino mass up to 2.8 TeV or a discovery reach
-of Higgsino mass up to 1.8 TeV for massless Bino, the reach of $Zh+\met$
-channel in our study is less.  However, the reach for multi-lepton channel
-reduces for larger $M_1$, which vanishes for $M_1\gtrsim 600$ GeV (1000 GeV)
-for discovery (exclusion).   The reach for $Zh+\met$ search in our study
-exceed that of the multi-lepton search for larger LSP masses.  In particular,
-the BDT reach for LSP mass with $Zh+\met$ search exceeds the reach for
-multi-lepton analyses by about 300 GeV.
+For massless Binos, the reach of the $Zh+\met$ channel in our study is less than the reach of the multi-lepton channel studied in Ref.~\cite{Gori:2014oua},
+which can exclude Higgsinos with masses up to 2.8 TeV and discover them for masses 
+up to 1.8 TeV.
+However, for heavier Binos (larger $M_1$), the reach of the multi-lepton channel
+is reduced, and vanishes completely for $M_1\gtrsim 600$ GeV (1000 GeV)
+for discovery (exclusion).
+In this region, the reach of the $Zh+\met$ channel in our study exceeds that of the multi-lepton search for larger LSP masses: an increasement of about 300 GeV with BDT analysis.
 
@@
 
-In this paper, we examined the discovery potential for a 100 TeV $pp$ collider
-For pair-produced heavy Higgsino NLSPs with Bino LSP, via intermediate $Z$ and
-$h$ bosons that decay to a pair of leptons and $b$ quarks respectively:
-$\chi_2^0\chi_3^0\rightarrow Zh \chi_1^0\chi_1^0\rightarrow bb\ell\ell \met$.
+In this paper, we examined the discovery/exclusion potential of a 100 TeV \emph{pp} collider
+for pair-produced heavy Higgsino NLSPs with a Bino LSP, via intermediate \emph{Z} and
+\emph{h} bosons that decay to a pair of leptons and \emph{b} quarks respectively:
+$\N_2\N_3\rightarrow Zh \N_1\N_1\rightarrow bb\ell\ell \met$.
 
-We pursued two analysis strategies. One was the traditional cut-and-count methods , including razor variables
-that are sensitive to the mass difference between the LSP and the NLSP. The
+We pursued two analysis strategies. One was the traditional cut-and-count methods, including razor variables
+that are sensitive to the mass difference between the LSP and the NLSPs. The
 other strategy was to use a boosted decision tree classifier trained with a
@@
 improvement over that of the LHC. We found that the rectangular cut strategy has
-the potential to discover Higgsino LSPs up to a mass of 850 GeV, and exclude
-them up to a mass of 1.35 TeV, for Bino masses around 350 GeV and 700 GeV
+the potential to discover Higgsino NLSPs up to a mass of 850 GeV, and exclude
+them up to a mass of 1.35 TeV, for a Bino LSP mass around 350 GeV and 700 GeV
 respectively. 
@@
 performs better, with the ability to discover Higgsino NLSPs up to 1.4 TeV and
-exclude them up to a mass of 1.8 TeV, for Bino masses of about 900 GeV and 1.4
+exclude them up to a mass of 1.8 TeV, for a Bino mass of about 900 GeV and 1.4
 TeV respectively.   In the
-process, we highlighted the importance of generating enough Monte Carlo events
+process, we highlighted the importance of generating enough MC  events
 to estimate the huge backgrounds at a 100 TeV $pp$ collider.
@@
 reduced when the difference $ \mu-M_1$ is high, since it results in a highly
-boosted $h$ that decays to a collimated pair of $b$ jets that will most likely be
+boosted $h$ that decays to a collimated pair of $b$-jets that will most likely be
 identified as a single jet. This is not an insurmountable difficulty - there are
@@
 
-The collimation of the $b$ jets, along with the fact that we take into account
+The collimation of the $b$ jets, along with the fact that we simulate
 detector effects using Delphes, result in a relatively lower reach in the high
 $\mu$, low $M_1$ region than the multilepton analysis in~\cite{Gori:2014oua},
-which is able to exclude Higgsinos up to a mass of 2.85 TeV for massless Binos,
-or discover Higgsinos up to a mass of 1.8 TeV.   The reach of our analysis,
-however,  is higher in the region where the difference between $\mu$ and $M_1$
+which is able to exclude Higgsinos up to a mass of 2.8 TeV for massless Binos,
+or discover them up to a mass of 1.8 TeV. However, the reach of our analysis
+is higher in the region where the difference between $\mu$ and $M_1$
 is smaller. This is consistent with our usage of the razor variable $M_R$,
-which is sensitive to the mass difference between the parent Higgsino and
+which is sensitive to the mass difference between the parent Higgsinos and the
 daughter Bino.
 
-A 100 TeV $pp$ collider represents an excellent opportunity to discover
+A 100 TeV \emph{pp} collider represents an excellent opportunity to discover
 physics beyond the Standard Model. The extremely high energies and luminosities
@@
 Throughput Computing (HTC) at the University of Arizona is gratefully
-acknowledged.  We also thank KITP for its hospitality when this draft is completed.  This research was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.
+acknowledged. We also thank KITP for its hospitality when this draft is completed.
+This research was supported in part by the National Science Foundation under Grant No. NSF PHY-1748958.
 

### 2019-08-09 main.tex

@@
 \usepackage{pgfplots}
+\pgfplotsset{compat=1.14}
 \usepackage{booktabs, longtable}
@@
   A 100 TeV proton-proton collider will be an extremely effective way to probe
-  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).
-  In this paper, we describe a search strategy  for discovering pair-produced
+  the electroweak sector of the Minimal Supersymmetric Standard Model (MSSM).  In
+  this paper, we describe a search strategy for discovering pair-produced
   Higgsino-like next-to-lightest supersymmetric particles (NLSPs) at a 100 TeV
-  hadron collider that decay to Bino-like lightest supersymmetric particle
-  (LSP) via intermediate $Z$ and SM Higgs boson that in turn decay to a pair
-  of leptons and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
+  hadron collider that decay to Bino-like lightest supersymmetric particle (LSP)
+  via intermediate $Z$ and SM Higgs boson that in turn decay to a pair of leptons
+  and a pair of $b$-quarks respectively: $\N_{2}\N_{3} \rightarrow
   (Z\N_1)(h\N_1)\rightarrow bb\ell\ell+\N_1\N_1$. In addition, we examine the
   potential for machine learning techniques to boost the power of our searches.
-  Using this analysis, Higgsinos up to 1.4 TeV can be discovered  at 5 $\sigma$ level for a Bino with
-  mass of about
-  0.9 TeV using 3000 fb$^{-1}$ of data.  Additionally, Higgsinos up to 1.8
-  TeV can be excluded  at 95\% C.L. for a Bino with mass of about 1.4 TeV。   This search
-  channel extends the multi-lepton search limits, especially in the region
-  where the mass difference between the Higgsino NLSPs and the Bino LSP is small.
+  Using this analysis, Higgsinos up to 1.4 TeV can be discovered  at 5 $\sigma$
+  level for a Bino with mass of about 0.9 TeV using 3000 fb$^{-1}$ of data.
+  Additionally, Higgsinos up to 1.8 TeV can be excluded  at 95\% C.L. for Binos
+  with mass of about 1.4 TeV. This search channel extends the multi-lepton search
+  limits, especially in the region where the mass difference between the Higgsino
+  NLSPs and the Bino LSP is small.
 }
@@
 \begin{document}
+
 \maketitle
-%\flushbottom
 

### 2019-09-25 main.tex
Added \pdfoutput=1 to document in order to submit to JHEP
Create referee reply document

@@
 \documentclass[a4paper,11pt]{article}
+\pdfoutput=1
  \providecommand{\tightlist}{%
@@
 discovering neutralino dark matter for compressed \cite{Low:2014cba,
-diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus} and
+diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2017gjh,Mahbubani:2018tin,Han:2018wus} and
 well-separated \cite{Gori:2014oua,Acharya:2014pua} neutralino spectra.

### 2019-10-20 referee_reply/referee_reply.tex
Adding *.swp to .gitignore, renaming Referee reply to referee_reply

\documentclass{article}
\title{Reply to referee report on \verbatim{JHEP_111P_0819}}
\author{Adarsh Pyarelal and Shufang Su}

\begin{document}
\maketitle

We would like to thank the referee for their careful reading of the paper and their 
suggestions. The issues and our replies are below.

Issue 1: • On page 1 the authors state ”the lightest of the MSSM particles known as the neutralinos emerges as the most attractive candidate for the LSP.”. It is not true that the lightest MSSM particles ought to be neutralinos (there is nothing wrong with sneutrinos being the LSP), and also I guess that one is not hunting for an attractive candidate for LSP, but rather trying to probe the particle nature of dark matter. I would suggest to correct this sentence accordingly.

\end{document}

### 2019-10-20 referee_reply/referee_reply.tex
Adding Makefile for referee reply, also adding rest of issues

@@
 
-Issue 1: • On page 1 the authors state ”the lightest of the MSSM particles known as the neutralinos emerges as the most attractive candidate for the LSP.”.
-It is not true that the lightest MSSM particles ought to be neutralinos (there is nothing wrong with sneutrinos being the LSP), and also I guess that one is not hunting for an attractive candidate for LSP, but rather trying to probe the particle nature of dark matter.
-I would suggest to correct this sentence accordingly.
+\noindent \textbf{Issue 1}: On page 1 the authors state ``the lightest of the
+MSSM particles known as the neutralinos emerges as the most attractive
+candidate for the LSP.". It is not true that the lightest MSSM particles ought
+to be neutralinos (there is nothing wrong with sneutrinos being the LSP), and
+also I guess that one is not hunting for an attractive candidate for LSP, but
+rather trying to probe the particle nature of dark matter. I would suggest to
+correct this sentence accordingly.
+
+\noindent\textbf{Reply:} What we meant was that the lightest neutralino
+emerges as the most attractive candidate for the LSP. We realize that the
+wording might be confusing, so we have changed it to...
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 2:} The authors state on page 2 that limits on
+electroweakinos are around 650-750 GeV, but this is only true for a certain
+mass gap among the neutralinos (e.g: 10-20 GeV such that the multi-lepton
+searches are effective). From instance, the latest limits from ATLAS for pure
+Higgsinos are around 150 GeV. Please correct the sentence.
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 3:} On page 2 the authors write The most interesting
+regions of split SUSY....  This is a biased statement. Interesting because of
+exactly what reason? The most interesting for who, and why? Please explain
+and/or clarify.
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 4:} On page 3 the authors make a brief overview of
+existing bounds on electroweakinos at 100 TeV colliders, and a few important
+references are missing. On one hand, the studies going for ”small mass split-
+tings” [23,25,31,32] strongly drew inspiration from the mono-jet + soft- lepton
+strategies (dubbed ”soft-lepton search” by the authors) that were proposed and
+studied for the LHC in e.g: 1004.4902, 1307.5952, 1310.4274, 1312.7350,
+1401.1162, 1401.1235, etc. Furthermore, bounds are quoted on Winos including
+disappearing track searches but not on Higgsinos (1703.05327, 1703.09675,
+1901.02987 should be added), nei- ther acknowledging the chance that Higgsinos
+below 100 GeV can still occur (1801.05432). This is a strange choice given that
+the authors work in a Bino-Higgsino system.
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 5:} On page 5 the authors use LO kinematics normalized
+to NLO via PROSPINO, but the background is only done at LO + matching. Some
+processes can have large K-factors, e.g: ttbar is about 2 in the BDT, in- deed,
+ttbar and tbW appear, so the significance can be overestimated. It would be
+necessary to run a small sample of NLO events (which can now be done with
+several MC generators in a very simple way) to check the difference in the
+kinematic distributions and assess how the cut-and-count and BDT analysis are
+affected. For the latter it would be enough to use the NLO events as a test
+sample using the current LO training.
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 6:} On page 7 the authors discuss the background
+processes. While it is clear that they have considered the relevant
+”irreducible” backgrounds, they do not include any process of V+jets, with V
+being a vector boson. In particular, a leptonically decaying Z plus a few jets
+can mimic the final state due to missing energy generated from miss-measured
+jet momenta. While the efficiency is low, the cross sections of V+jets are
+fairly large, so this needs to be properly estimated.
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 7:} On page 8 the authors start a multi-variate analysis
+based on boosted- decision trees (BDTs). It is not clear that the BDT would be
+able to ”discover” the razor variables, e.g: Ez and Eh from Eq. 3.1 are not
+explicitly included: with pT of both b’s and mbb one would still have a
+degeneracy between the energy and z-momenta of the Higgs boson. So please
+explain if in addition there is more information used (e.g: eta of the
+b-quarks) or what motivated the choices of input variables. If the BDT includes
+the razor variables, then it naively should outperform it (or have a similar
+performance, in the best case).
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 9:} In the same page I find that there are very few details about the BDT
+implementation. The maximal depth and minimum node size are not written. There
+is no evidence of the reliability of the study, e.g: no ROC curve is shown
+neither the AUC is reported. It would be desriable to present the ROC curve,
+the AUC for some benchmark points, as well as illustrate the robustness of the
+study by presenting e.g: the precision vs recall (or PPR vs TPR, depending on
+the ML jargon used).
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 10:} The sentence about the training set is confusing, so
+please clearly state if a) 75 % of the signal events and 30% of the background
+events go into training (so test is 25 % of signal and 70 % of background). If
+this is what was done, what is the reason to save background events for test
+purposes? Just limited MC statistics?  b) 75% of the training events are signal
+and 30% are background (since this does not add up to 100%, maybe a typo?) c)
+please also specify the size /weights of signal and background events.
+According to Table 5 in the preselection the bgd XS is about 9000 times larger
+than the signal so if events are weighted according to XS then the BDT will
+learn to recognize background more than focusing on signal features. One option
+would be to re-train assigning the signal and background samples the same
+weight.
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 11:} In page 9 the authors claim their sensitivity stems
+from S/Sqrt[B], but they request 3 Monte Carlo (MC) events. This sentence is
+confusing, because the number of MC events in itself is meaningless. Is it the
+weight of the corresponding events what the authors mean? Please clarify it.
+Moreover, to claim that 3 events is enough, this requires to have a good
+control over the statistics... can the authors comment on the sample size of
+both signal and background? What is the ratio of the cross section of generated
+events over the one expected at FCC-hh with 3ab-1?
+
+\noindent\textbf{Reply:}
+
+\noindent\textbf{Issue 12:} In page 9 the authors display their results. If, as
+stated in the introduc- tion, dark matter is a motivation, then it iso-relic
+contour lines on Fig.4 could be shown (of course, there could be a mild
+dependence on other parameters like tan beta, in that case one can fix some
+values). By the same token, is the model affected by current and/or future
+direct and indirect detection constraints? This information is also available
+in the literature, but the relevant results need to be explicitly pointed out.
+
+\noindent\textbf{Reply:}
 

### 2019-10-20 main.tex
Updating statement about electroweakino limits in response to refree report

@@
 searches~\cite{CMS-PAS-SUS-19-005}. The limits on electroweakinos with heavy
-scalar superparticles, however, are still relatively weak: around 650 $-$ 750
-GeV or less~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae, Aaboud:2018htj,
-Sirunyan:2018ubx, Aaboud:2018zeb}, depending on the decay modes of the parent
-electroweakinos and their species.  In this paper, we will focus on the
-discovery potential of the neutralinos and charginos at a 100 TeV $pp$
-collider.
+scalar superparticles, however, are still relatively weak: between 0.15 $-$ 1.0
+TeV, depending on the mixing among the gauge
+eigenstates~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae, Aaboud:2018htj,
+Sirunyan:2018ubx, Aaboud:2018zeb} \Adarsh{TODO: Confirm that these are the
+latest limits.}, depending on the decay modes of the parent electroweakinos and
+their species.  In this paper, we will focus on the discovery potential of the
+neutralinos and charginos at a 100 TeV $pp$ collider.
 

### 2019-10-20 referee_reply/referee_reply.tex
Updating formatting, etc
Addressing a couple of issues

@@
-\documentclass{article}
-\title{Reply to referee report on \verbatim{JHEP_111P_0819}}
+\documentclass[12pt]{article}
+\usepackage{fullpage}
+\title{Reply to referee report on \texttt{JHEP\_111P\_0819}}
+\usepackage[dvipsnames]{xcolor}
+\newcommand{\Shufang}[1]{{\bf\color{Maroon}  #1}}
+\newcommand{\Adarsh}[1]{{\bf\color{RoyalBlue} AP: #1}}
+\newcommand{\ap}[1]{\textcolor{RoyalBlue}{#1}}
+\newcommand{\issue}[1]{\bigskip\noindent\textbf{\color{Maroon}Issue #1: }}
+\newcommand{\reply}{\medskip\noindent\textbf{\color{RoyalBlue}Reply:}}
+
 \author{Adarsh Pyarelal and Shufang Su}
@@
 \begin{document}
+
 \maketitle
@@
 
-\noindent \textbf{Issue 1}: On page 1 the authors state ``the lightest of the
+ \issue{1}: On page 1 the authors state ``the lightest of the
 MSSM particles known as the neutralinos emerges as the most attractive
@@
 
-\noindent\textbf{Reply:} What we meant was that the lightest neutralino
+\reply{} What we meant was that the lightest neutralino
 emerges as the most attractive candidate for the LSP. We realize that the
-wording might be confusing, so we have changed it to...
+wording might be confusing, so we have changed it to...\Adarsh{TODO}.
 
-\noindent\textbf{Reply:}
-
-\noindent\textbf{Issue 2:} The authors state on page 2 that limits on
+ \issue{2} The authors state on page 2 that limits on
 electroweakinos are around 650-750 GeV, but this is only true for a certain
@@
 
-\noindent\textbf{Reply:}
+\reply{} We have corrected the sentence to state that the
+limits on electroweakinos are between 0.15 and 1.0 TeV, depending on the mixing
+of the gauge eigenstates.
 
-\noindent\textbf{Issue 3:} On page 2 the authors write The most interesting
+\issue{3} On page 2 the authors write The most interesting
 regions of split SUSY....  This is a biased statement. Interesting because of
@@
 
-\noindent\textbf{Reply:}
+\reply{} We acknowledge that this statement is too
+strong, and have accordingly softened it, clarifying that our main interest is
+in discovering thermal electroweakino dark matter.
 
-\noindent\textbf{Issue 4:} On page 3 the authors make a brief overview of
-existing bounds on electroweakinos at 100 TeV colliders, and a few important
-references are missing. On one hand, the studies going for ”small mass split-
-tings” [23,25,31,32] strongly drew inspiration from the mono-jet + soft- lepton
+\issue{4} On page 3 the authors make a brief overview of existing bounds on
+electroweakinos at 100 TeV colliders, and a few important references are
+missing. On one hand, the studies going for ”small mass splittings”
+[23,25,31,32] strongly drew inspiration from the mono-jet + soft- lepton
 strategies (dubbed ”soft-lepton search” by the authors) that were proposed and
@@
 
-\noindent\textbf{Reply:}
+\reply{}
 
-\noindent\textbf{Issue 5:} On page 5 the authors use LO kinematics normalized
+\issue{5} On page 5 the authors use LO kinematics normalized
 to NLO via PROSPINO, but the background is only done at LO + matching. Some
@@
 
-\noindent\textbf{Reply:}
+\reply{}
 
-\noindent\textbf{Issue 6:} On page 7 the authors discuss the background
+\issue{6} On page 7 the authors discuss the background
 processes. While it is clear that they have considered the relevant
@@
 
-\noindent\textbf{Reply:}
+\reply{}
 
-\noindent\textbf{Issue 7:} On page 8 the authors start a multi-variate analysis
+\issue{7} On page 8 the authors start a multi-variate analysis
 based on boosted- decision trees (BDTs). It is not clear that the BDT would be
@@
 
-\noindent\textbf{Reply:}
+\reply{}
 
-\noindent\textbf{Issue 9:} In the same page I find that there are very few details about the BDT
-implementation. The maximal depth and minimum node size are not written. There
-is no evidence of the reliability of the study, e.g: no ROC curve is shown
-neither the AUC is reported. It would be desriable to present the ROC curve,
-the AUC for some benchmark points, as well as illustrate the robustness of the
-study by presenting e.g: the precision vs recall (or PPR vs TPR, depending on
-the ML jargon used).
+\issue{8} In the same page I find that there are very few details
+about the BDT implementation. The maximal depth and minimum node size are not
+written. There is no evidence of the reliability of the study, e.g: no ROC
+curve is shown neither the AUC is reported. It would be desriable to present
+the ROC curve, the AUC for some benchmark points, as well as illustrate the
+robustness of the study by presenting e.g: the precision vs recall (or PPR vs
+TPR, depending on the ML jargon used).
 
-\noindent\textbf{Reply:}
+\reply{}
 
-\noindent\textbf{Issue 10:} The sentence about the training set is confusing, so
-please clearly state if a) 75 % of the signal events and 30% of the background
-events go into training (so test is 25 % of signal and 70 % of background). If
+\issue{9} The sentence about the training set is confusing, so
+please clearly state if a) 75\% of the signal events and 30\% of the background
+events go into training (so test is 25\% of signal and 70\% of background). If
 this is what was done, what is the reason to save background events for test
-purposes? Just limited MC statistics?  b) 75% of the training events are signal
-and 30% are background (since this does not add up to 100%, maybe a typo?) c)
+purposes? Just limited MC statistics?  b) 75\% of the training events are signal
+and 30\% are background (since this does not add up to 100\%, maybe a typo?) c)
 please also specify the size /weights of signal and background events.
@@
 
-\noindent\textbf{Reply:}
+\reply{}
 
-\noindent\textbf{Issue 11:} In page 9 the authors claim their sensitivity stems
+\issue{10} In page 9 the authors claim their sensitivity stems
 from S/Sqrt[B], but they request 3 Monte Carlo (MC) events. This sentence is
@@
 
-\noindent\textbf{Reply:}
+\reply{}
 
-\noindent\textbf{Issue 12:} In page 9 the authors display their results. If, as
-stated in the introduc- tion, dark matter is a motivation, then it iso-relic
+\issue{11} In page 9 the authors display their results. If, as
+stated in the introduction, dark matter is a motivation, then it iso-relic
 contour lines on Fig.4 could be shown (of course, there could be a mild
@@
 
-\noindent\textbf{Reply:}
+\reply{}
 

### 2019-10-20 main.tex
Addressing a couple of issues

--- 2019-09-25 main.tex
@@
 searches~\cite{CMS-PAS-SUS-19-005}. The limits on electroweakinos with heavy
-scalar superparticles, however, are still relatively weak: around 650 $-$ 750
-GeV or less~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae, Aaboud:2018htj,
-Sirunyan:2018ubx, Aaboud:2018zeb}, depending on the decay modes of the parent
-electroweakinos and their species.  In this paper, we will focus on the
-discovery potential of the neutralinos and charginos at a 100 TeV $pp$
-collider.
+scalar superparticles, however, are still relatively weak: between \ap{0.15 $-$ 1.0
+TeV, depending on the mixing among the gauge
+eigenstates~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae, Aaboud:2018htj,
+Sirunyan:2018ubx, Aaboud:2018zeb}} \Adarsh{TODO: Confirm that these are the
+latest limits.}, depending on the decay modes of the parent electroweakinos and
+their species.  In this paper, we will focus on the discovery potential of the
+neutralinos and charginos at a 100 TeV $pp$ collider.
 
@@
 A 100 TeV $pp$ collider would open up an immense number of physics
-opportunities not afforded to the 14 TeV LHC, including exploring the most
-interesting regions of the split SUSY parameter space
+opportunities not afforded to the 14 TeV LHC, including \st{exploring the most
+interesting regions of the split SUSY parameter space} \ap{discovering thermal
+electroweakino dark matter candidates.}
 \cite{Arkani-Hamed:2015vfh}.

### 2019-10-21 referee_reply/referee_reply.tex
Adding references to earlier studies of mono-jet and soft-lepton channels for the LHC

@@
 electroweakinos at 100 TeV colliders, and a few important references are
-missing. On one hand, the studies going for ”small mass splittings”
-[23,25,31,32] strongly drew inspiration from the mono-jet + soft- lepton
-strategies (dubbed ”soft-lepton search” by the authors) that were proposed and
+missing. On one hand, the studies going for ``small mass splittings"
+[23,25,31,32] strongly drew inspiration from the mono-jet + soft-lepton
+strategies (dubbed ``soft-lepton search" by the authors) that were proposed and
 studied for the LHC in e.g: 1004.4902, 1307.5952, 1310.4274, 1312.7350,
@@
 
-\reply{}
+\reply{} We have added the references to the earlier studies proposed for the
+LHC.
 

### 2019-10-21 main.tex
Adding references to earlier studies of mono-jet and soft-lepton channels for the LHC

@@
 
-The optimal search strategy for finding electroweakinos   highly depends on
+The optimal search strategy for finding electroweakinos is highly dependent on
 their mass spectra \cite{Han:2013kza}. Phenomenological collider studies on
@@
 100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
-Berlin:2015aba, Cirelli:2014dsa}.
+Berlin:2015aba, Cirelli:2014dsa}, which in turn draw inspiration from earlier
+studies done for the LHC \cite{Giudice:2010wb, Gori:2013ala, Han:2013usa,
+Schwaller:2013baa, Baer:2014cua, Han:2014kaa}.
 For $3\ \text{ab}^{-1}$ of data, the projected exclusion reaches for pure Wino

### 2019-10-21 main.tex
Updating higgsino limits and references

@@
 100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
-Berlin:2015aba, Cirelli:2014dsa}, which in turn draw inspiration from earlier
+  Berlin:2015aba, Cirelli:2014dsa, Mahbubani:2017gjh, Mahbubani:2018tin,
+Fukuda:2017jmk, Saito:2019rtg},
+  \ap{which in turn draw inspiration from earlier
 studies done for the LHC \cite{Giudice:2010wb, Gori:2013ala, Han:2013usa,
-Schwaller:2013baa, Baer:2014cua, Han:2014kaa}.
-For $3\ \text{ab}^{-1}$ of data, the projected exclusion reaches for pure Wino
-LSPs using the monojet channel is about $1.4$~TeV.  The reach
-can be increased to $\sim3$ TeV with a disappearing tracks search.
-Neutralinos up to 1 TeV can be excluded for mass splittings of about 20-30 GeV,
+Schwaller:2013baa, Baer:2014cua, Han:2014kaa}}.
+For $3\ \text{ab}^{-1}$ of data, the \ap{strongest projected discovery reaches for pure Wino
+(Higgsino) LSPs using the monojet channel with disappearing tracks at a 100 TeV
+collider is about $4.8$~TeV (1.1~TeV) \cite{Saito:2019rtg}}\st{. The reach
+can be increased to $\sim3$ TeV (870 GeV) with disappearing tracks
+searches.}\Adarsh{Shufang, does this look ok to you? Why are the results in
+\cite{Saito:2019rtg} so much better than those in \cite{Low:2014cba}?} 
+For mass splittings of about 20-30 GeV, neutralinos up to 1 TeV can be excluded 
 using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
@@
 
-Well-separated spectra have been studied in \cite{Gori:2014oua,
-Acharya:2014pua} using multi-lepton channels, of the form
+Well-separated spectra have been studied using multi-lepton channels
+\cite{Gori:2014oua, Acharya:2014pua}, of the form
 

### 2019-12-17 main.tex
Addressed issue 4
Shufang's edits

--- 2019-10-20 main.tex
@@
 the mechanism of supersymmetry breaking.  However, taking into account experimental
-constraints and phenomenological considerations, the lightest of the MSSM
+constraints and phenomenological considerations, \st{the lightest of the MSSM
 particles known as the neutralinos emerges as the most attractive candidate
-for the LSP \cite{Bertone:2004pz}.
+for the LSP}
+\Shufang{neutralino LSP emerges as the most attractive candidate for WIMP dark matter.}~\cite{Bertone:2004pz}.
 
@@
 already around 2 TeV for prompt decay and 2.5 TeV for disappearing track
-searches~\cite{CMS-PAS-SUS-19-005}. The limits on electroweakinos with heavy
-scalar superparticles, however, are still relatively weak: between \ap{0.15 $-$ 1.0
-TeV, depending on the mixing among the gauge
-eigenstates~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae, Aaboud:2018htj,
-Sirunyan:2018ubx, Aaboud:2018zeb}} \Adarsh{TODO: Confirm that these are the
-latest limits.}, depending on the decay modes of the parent electroweakinos and
-their species.  In this paper, we will focus on the discovery potential of the
-neutralinos and charginos at a 100 TeV $pp$ collider.
+searches~\cite{CMS-PAS-SUS-19-005}.
+\Shufang{The limits on electroweakinos with heavy scalar superparticles, however, are still relatively weak: between 150 GeV $-$ 1.0 TeV, depending on the neutralino/chargino species, decay modes, and their mass splittings~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,Sirunyan:2018ubx,  Aaboud:2018htj,Aaboud:2018zeb,
+Aad:2019qnd,Aad:2019vvf,Aad:2019vnb,Aaboud:2018ngk,Aaboud:2018sua,Aaboud:2018jiw,Aaboud:2017leg,Aaboud:2017mpt,Aaboud:2017nhr}.  In this paper, we will focus on the discovery potential of the
+neutralinos and charginos at a 100 TeV $pp$ collider. }
+{\bf Can not find Ref. 9}
 
@@
 A 100 TeV $pp$ collider would open up an immense number of physics
-opportunities not afforded to the 14 TeV LHC, including \st{exploring the most
-interesting regions of the split SUSY parameter space} \ap{discovering thermal
-electroweakino dark matter candidates.}
-\cite{Arkani-Hamed:2015vfh}.
+opportunities not afforded to the 14 TeV LHC. \st{including exploring the most
+interesting regions of the split SUSY parameter space}~\cite{Arkani-Hamed:2015vfh}.
 % Status of 100 TeV planning
@@
 In particular, studies have already been performed on the prospects of
-discovering neutralino dark matter for compressed \cite{Low:2014cba,
-diCortona:2014yua,Cirelli:2014dsa,Mahbubani:2017gjh,Mahbubani:2018tin,Han:2018wus} and
-well-separated \cite{Gori:2014oua,Acharya:2014pua} neutralino spectra.
+discovering neutralino dark matter for compressed \cite{Low:2014cba,Cirelli:2014dsa,Mahbubani:2017gjh,Mahbubani:2018tin,Han:2018wus,Bramante:2014tba, Berlin:2015aba, 
+Fukuda:2017jmk, Saito:2019rtg} and
+well-separated \cite{Gori:2014oua,Acharya:2014pua,diCortona:2014yua} neutralino spectra.
 
@@
 
-The optimal search strategy for finding electroweakinos   highly depends on
-their mass spectra \cite{Han:2013kza}.  Phenomenological collider studies on
-finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at a
-100 TeV $pp$  collider can be found in \cite{Low:2014cba, Bramante:2014tba,
-Berlin:2015aba, Cirelli:2014dsa}.
-For $3\ \text{ab}^{-1}$ of data, the projected exclusion reaches for pure Wino
-LSPs using the monojet channel is about $1.4$~TeV.  The reach
-can be increased to $\sim3$ TeV with a disappearing tracks search.
-Neutralinos up to 1 TeV can be excluded for mass splittings of about 20-30 GeV,
-using a soft lepton search \cite{Low:2014cba}. Additionally, Bino-Wino LSPs
-with masses up to 1.5 TeV for an inter-state mass splitting of around 1 GeV  can be
-discovered at a 100 TeV $pp$ collider with $\sim7\ \text{ab}^{-1}$
-of data \cite{Bramante:2014tba}.
+\Shufang{
+The optimal search strategy for finding electroweakinos is highly dependent on
+their mass spectra \cite{Han:2013kza}. There are phenomenological collider studies on
+finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at the LHC~\cite{Giudice:2010wb, Gori:2013ala, Han:2013usa, Schwaller:2013baa, Baer:2014cua, Han:2014kaa} and 
+at a 100 TeV $pp$  collider~\cite{Low:2014cba, Bramante:2014tba,
+  Berlin:2015aba, Cirelli:2014dsa, Mahbubani:2017gjh, Mahbubani:2018tin,
+Fukuda:2017jmk, Saito:2019rtg,Han:2018wus}.
+For 100 TeV $pp$ collider with $30\ \text{ab}^{-1}$ of data, disappearing track search can discover Wino (Higgsino) LSP with mass up to about 4.7 TeV (1 TeV)~\cite{Low:2014cba,Cirelli:2014dsa,Mahbubani:2017gjh,Saito:2019rtg,Han:2018wus}.
+The discovery reach from Monojet, mono-$Z$, mono-photon search is weaker: about 1 TeV (600 GeV) for Wino (Higgsino)~\cite{Low:2014cba,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus}.
+For mass splittings of about 20-30 GeV between low-lying neutralinos and charginos, soft lepton plus missing $E_T$ signal can be used~\cite{Low:2014cba,Bramante:2014tba}.
+In addition, Weak boson fusion process can discover a Wino (Higgsino) up to about 1 TeV (530 GeV)~\cite{Cirelli:2014dsa, Berlin:2015aba}.
+Note, however,  that in certain
+scenarios, light Higgsinos between 75 $-$ 100 GeV are still viable, evading LEP and LHC
+constraints \cite{Egana-Ugrinovic:2018roi}.}
 
-Well-separated spectra have been studied in \cite{Gori:2014oua,
-Acharya:2014pua} using multi-lepton channels, of the form
+Well-separated spectra have been studied using multi-lepton channels
+\cite{Gori:2014oua, Acharya:2014pua}, of the form
 
@@
 the generated events into training and test sets, with the training set
-comprising 75\% of signal events and 30\% of background events.  We used the
+comprising 75\% of signal events and 30\% of background events.  \Shufang{More details here -- Referee comment 9.} We used the
 \texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
@@
 number of Monte Carlo (MC) events after cuts for each background component, corresponding to
-the 95\% confidence interval for a Poisson distribution.
+the 95\% confidence interval for a Poisson distribution.  \Shufang{SS: Is it 3 MC events, or 3 weighted events after CS values used? Referee comment 10.}
 

### 2019-12-17 main.tex
Removed duplicate references, added note about minimum of 3 events

@@
 its precise nature is one of the most exciting challenges in particle physics
-today.  One promising group of candidates for dark matter is the class of stable
-particles known as weakly interacting massive particles (WIMPs). These
+today.  One promising group of candidates for dark matter is the class of
+stable particles known as weakly interacting massive particles (WIMPs). These
 particles arise naturally in many extensions of the SM that are motivated by
-the need to stabilize the electroweak scale. One of the most heavily studied extensions
-is the Minimal Supersymmetric Standard Model (MSSM), which predicts a
-`supersymmetric partner', or \emph{superpartner}, for each SM
+the need to stabilize the electroweak scale. One of the most heavily studied
+extensions is the Minimal Supersymmetric Standard Model (MSSM), which predicts
+a `supersymmetric partner', or \emph{superpartner}, for each SM
 particle\footnote{For a detailed review of the MSSM, see Ref.
@@
 determined by the mass hierarchy of the superpartners, which in turn depends on
-the mechanism of supersymmetry breaking.  However, taking into account experimental
-constraints and phenomenological considerations, \st{the lightest of the MSSM
-particles known as the neutralinos emerges as the most attractive candidate
-for the LSP}
-\Shufang{neutralino LSP emerges as the most attractive candidate for WIMP dark matter.}~\cite{Bertone:2004pz}.
+the mechanism of supersymmetry breaking.  However, taking into account
+experimental constraints and phenomenological considerations, the neutralino
+LSP emerges as the most attractive candidate for WIMP dark
+matter.~\cite{Bertone:2004pz}.
 
@@
 already around 2 TeV for prompt decay and 2.5 TeV for disappearing track
-searches~\cite{CMS-PAS-SUS-19-005}.
-\Shufang{The limits on electroweakinos with heavy scalar superparticles, however, are still relatively weak: between 150 GeV $-$ 1.0 TeV, depending on the neutralino/chargino species, decay modes, and their mass splittings~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,Sirunyan:2018ubx,  Aaboud:2018htj,Aaboud:2018zeb,
-Aad:2019qnd,Aad:2019vvf,Aad:2019vnb,Aaboud:2018ngk,Aaboud:2018sua,Aaboud:2018jiw,Aaboud:2017leg,Aaboud:2017mpt,Aaboud:2017nhr}.  In this paper, we will focus on the discovery potential of the
-neutralinos and charginos at a 100 TeV $pp$ collider. }
-{\bf Can not find Ref. 9}
+searches~\cite{CMS-PAS-SUS-19-005}. The limits on electroweakinos with
+  heavy scalar superparticles, however, are still relatively weak: between 150
+  GeV $-$ 1.0 TeV, depending on the neutralino/chargino species, decay modes,
+  and their mass splittings~\cite{ATL-PHYS-PUB-2019-022, Sirunyan:2017lae,
+    Sirunyan:2018ubx, Aaboud:2018htj, Aaboud:2018zeb, Aad:2019qnd, Aad:2019vvf,
+  Aad:2019vnb, Aaboud:2018ngk, Aaboud:2018sua, Aaboud:2018jiw, Aaboud:2017leg,
+Aaboud:2017mpt, Aaboud:2017nhr}.  In this paper, we will focus on the discovery
+potential of the neutralinos and charginos at a 100 TeV $pp$ collider. {\bf
+Can not find Ref. 9}
 
@@
 
-\Shufang{
 The optimal search strategy for finding electroweakinos is highly dependent on
-their mass spectra \cite{Han:2013kza}. There are phenomenological collider studies on
-finding electroweakinos with a small mass splitting of about 0.1 $-$ 50 GeV at the LHC~\cite{Giudice:2010wb, Gori:2013ala, Han:2013usa, Schwaller:2013baa, Baer:2014cua, Han:2014kaa} and 
-at a 100 TeV $pp$  collider~\cite{Low:2014cba, Bramante:2014tba,
-  Berlin:2015aba, Cirelli:2014dsa, Mahbubani:2017gjh, Mahbubani:2018tin,
-Fukuda:2017jmk, Saito:2019rtg,Han:2018wus}.
-For 100 TeV $pp$ collider with $30\ \text{ab}^{-1}$ of data, disappearing track search can discover Wino (Higgsino) LSP with mass up to about 4.7 TeV (1 TeV)~\cite{Low:2014cba,Cirelli:2014dsa,Mahbubani:2017gjh,Saito:2019rtg,Han:2018wus}.
-The discovery reach from Monojet, mono-$Z$, mono-photon search is weaker: about 1 TeV (600 GeV) for Wino (Higgsino)~\cite{Low:2014cba,Cirelli:2014dsa,Mahbubani:2018tin,Han:2018wus}.
-For mass splittings of about 20-30 GeV between low-lying neutralinos and charginos, soft lepton plus missing $E_T$ signal can be used~\cite{Low:2014cba,Bramante:2014tba}.
-In addition, Weak boson fusion process can discover a Wino (Higgsino) up to about 1 TeV (530 GeV)~\cite{Cirelli:2014dsa, Berlin:2015aba}.
-Note, however,  that in certain
-scenarios, light Higgsinos between 75 $-$ 100 GeV are still viable, evading LEP and LHC
-constraints \cite{Egana-Ugrinovic:2018roi}.}
+their mass spectra \cite{Han:2013kza}. There are phenomenological collider
+studies on finding electroweakinos with a small mass splitting of about 0.1 $-$
+50 GeV at the LHC~\cite{Giudice:2010wb, Gori:2013ala, Han:2013usa,
+Schwaller:2013baa, Baer:2014cua, Han:2014kaa} and at a 100 TeV $pp$
+collider~\cite{Low:2014cba, Bramante:2014tba, Berlin:2015aba, Cirelli:2014dsa,
+Mahbubani:2017gjh, Mahbubani:2018tin, Fukuda:2017jmk,
+Saito:2019rtg, Han:2018wus}. For a 100 TeV $pp$ collider with $30\
+\text{ab}^{-1}$ of data, disappearing track search can discover Wino (Higgsino)
+LSP with mass up to about 4.7 TeV (1
+TeV)~\cite{Low:2014cba, Cirelli:2014dsa, Mahbubani:2017gjh, Saito:2019rtg, Han:2018wus}.
+The discovery reaches from monojet, mono-$Z$, and mono-photon searches are weaker:
+about 1 TeV (600 GeV) for Wino
+(Higgsino)~\cite{Low:2014cba, Cirelli:2014dsa, Mahbubani:2018tin, Han:2018wus}.
+For mass splittings of about 20-30 GeV between low-lying neutralinos and
+charginos, soft leptons + missing $E_T$ signal can be
+used~\cite{Low:2014cba, Bramante:2014tba}.  In addition, weak boson fusion
+process can discover a Wino (Higgsino) up to about 1 TeV (530
+GeV)~\cite{Cirelli:2014dsa, Berlin:2015aba}.  Note, however,  that in certain
+scenarios, light Higgsinos between 75 $-$ 100 GeV are still viable, evading LEP
+and LHC constraints \cite{Egana-Ugrinovic:2018roi}.
 
@@
 Searches for pair produced nearly mass-degenerate Higgsinos  have been
-performed at ATLAS and CMS for various decay topologies
-\cite{Aaboud:2018htj,Sirunyan:2018ubx,Aaboud:2018zeb}.  
-For neutralino-chargino pair production with \emph{WZ} and \emph{Wh} topologies, the 95\%
-C.L. exclusion limits are about 650 GeV, 490 GeV, and 535 GeV for \emph{WZ}, \emph{Wh} and an equal mixture of \emph{WZ}+\emph{Wh} topology, with the strongest limits coming from
-the multi-lepton searches.
-For neutralino pair production with \emph{ZZ, Zh}, and \emph{hh} topologies\footnote{While such searches assume a gravitino LSP with Higgsino NLSPs, the limits are still relevant for our Higgsino NLSPs - Bino
-LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
-multi-$b$ jets searches, depending on the decay branching fractions of the Higgsino NLSPs.
+performed at ATLAS and CMS for various decay topologies \cite{Aaboud:2018htj,
+Sirunyan:2018ubx, Aaboud:2018zeb}.  For neutralino-chargino pair production
+with \emph{WZ} and \emph{Wh} topologies, the 95\% C.L. exclusion limits are
+about 650 GeV, 490 GeV, and 535 GeV for \emph{WZ}, \emph{Wh} and an equal
+mixture of \emph{WZ}+\emph{Wh} topology, with the strongest limits coming from
+the multi-lepton searches.  For neutralino pair production with \emph{ZZ, Zh},
+and \emph{hh} topologies\footnote{While such searches assume a gravitino LSP
+  with Higgsino NLSPs, the limits are still relevant for our Higgsino NLSPs -
+  Bino LSP scenario.}, the limits are about 650 $-$ 750 GeV via multi-lepton or
+  multi-$b$ jets searches, depending on the decay branching fractions of the
+  Higgsino NLSPs.
 
@@
 signal benchmark point with $\mu =$ 1 TeV and $M_1$ = 25 GeV.   The
-cross-sections of the backgrounds are obtained from MadEvent after performing the MLM matching procedure. Their small size reflects
-the $m_{\ell\ell}$ and $\slashed{E}_T$ cuts we imposed at the parton level. For all
-the benchmark points, we require a minimum of 3 signal events left over after
-cuts. We can see that, after applying our cuts, $tbW$ remains as the
-dominant backgrounds, followed by $tt$.   The values of the razor variable cuts were chosen to
-maximize the significance, $S/\sqrt{B}$ (calculated for an integrated luminosity
-of 3000 fb$^{-1}$), shown in the last column.
+cross-sections of the backgrounds are obtained from MadEvent after performing
+the MLM matching procedure. Their small size reflects the $m_{\ell\ell}$ and
+$\slashed{E}_T$ cuts we imposed at the parton level. For all the benchmark
+points, we require a minimum of three background events (at the MC level, i.e.
+unweighted) left over after cuts\footnote{\ap{This is inspired by the upper
+    one-sided limit for the mean of a Poisson variable given zero observed
+    events, for a confidence level of 95\% (see Table 39.3 of
+    \cite{PhysRevD.98.030001}), however, it does not reflect it exactly (since
+    we required a minimum on unweighted rather than weighted events).  We
+    observed that as we generated more unweighted background events, the
+    discovery reach of our analysis showed a steady increase. This, combined with the
+    fact that we were pushing the limits of our storage and computing capacity
+    (we generated $\approx 14$ million $tt$ events and $\approx
+    850$K $tbW$ events - both unweighted), lead us to believe that the projected reaches
+presented in this paper are conservative ones.}}. We can see that, after
+applying our cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.
+The values of the razor variable cuts were chosen to maximize the significance,
+$S/\sqrt{B}$ (calculated for an integrated luminosity of 3000 fb$^{-1}$), shown
+in the last column.
 
@@
 
-For certain values of the
+\st{For certain values of the
 cuts on kinematic variables or the score of the classifier, no events survived
@@
 number of Monte Carlo (MC) events after cuts for each background component, corresponding to
-the 95\% confidence interval for a Poisson distribution.  \Shufang{SS: Is it 3 MC events, or 3 weighted events after CS values used? Referee comment 10.}
+the 95\% confidence interval for a Poisson distribution.}\Shufang{SS: Is it 3
+MC events, or 3 weighted events after CS values used? Referee comment 10.}
+\Adarsh{I added a footnote about this - see footnote 5. I think we can remove
+this paragraph...}
 

### 2019-12-17 main.tex
Added ratios of xsections of generated bg events to 3ab-1 at 100 TeV pp collider

@@
     observed that as we generated more unweighted background events, the
-    discovery reach of our analysis showed a steady increase. This, combined with the
-    fact that we were pushing the limits of our storage and computing capacity
-    (we generated $\approx 14$ million $tt$ events and $\approx
-    850$K $tbW$ events - both unweighted), lead us to believe that the projected reaches
-presented in this paper are conservative ones.}}. We can see that, after
-applying our cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.
-The values of the razor variable cuts were chosen to maximize the significance,
+    discovery reach of our analysis showed a steady increase. This, combined
+    with the fact that we were pushing the limits of our storage and computing
+    capacity (we generated $\approx 10$ million $tt$ events, $\approx 26$
+    million $tbW$  events and $100$K $bbWW$ events - all unweighted), lead us
+    to believe that the projected reaches presented in this paper are
+conservative ones. The ratio of the cross section of the generated events to
+that expected at a 100 TeV $pp$ collider with 3 ab$^{-1}$ is $\approx 0.2$ for
+$tt$, 0.05 for $tbW$, $0.46$ for $bbWW$}}. We can see that, after applying our
+cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.  The values
+of the razor variable cuts were chosen to maximize the significance,
 $S/\sqrt{B}$ (calculated for an integrated luminosity of 3000 fb$^{-1}$), shown

### 2019-12-17 main.tex
Clarified differing train-test splits for signal and BG, added note about not using NLO generation mode, added tree depth and node size info

@@
 For the backgrounds, we allowed up to one additional jet in the final state, to
-approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
+approximate NLO QCD effects, and performed MLM matching\footnote{\ap{Although
+there are tools that support NLO generation \cite{Alwall:2014hca}, their NLO
+generation mode does not support specifying decay chains, which we require in
+order to generate enough MC events to be statistically representative of the
+backgrounds at a 100 TeV $pp$ collider.}} with the \texttt{xqcut}
 parameter set to 40 GeV. The Higgsino pair production cross sections were
@@
 that expected at a 100 TeV $pp$ collider with 3 ab$^{-1}$ is $\approx 0.2$ for
-$tt$, 0.05 for $tbW$, $0.46$ for $bbWW$}}. We can see that, after applying our
+$tt$, 0.05 for $tbW$, and $\approx0.46$ for $bbWW$.}}. We can see that, after applying our
 cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.  The values
@@
 the generated events into training and test sets, with the training set
-comprising 75\% of signal events and 30\% of background events.  \Shufang{More details here -- Referee comment 9.} We used the
+\ap{comprised of 75\% of the generated signal events and 30\% of the generated
+background events. We require a lower portion of the background events for
+training, in order to maintain adequate MC statistics to calculate significance
+using the testing split, given the extremely large background cross sections at
+a 100 TeV $pp$ collider. All the events are unweighted.}
+\Shufang{More details here -- Referee comment 9.} We used the
 \texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
 A boosted decision tree classifier was trained with 1000 weak learners and a
-learning rate of 0.025.
+learning rate of 0.025. \ap{The maximum tree depth is 3, and the minimum node
+size is 1.}
 
@@
 MC events, or 3 weighted events after CS values used? Referee comment 10.}
-\Adarsh{I added a footnote about this - see footnote 5. I think we can remove
+\Adarsh{I added a footnote about this - see footnote 6 on page 8. I think we can remove
 this paragraph...}

### 2019-12-17 main.tex
Shufang's edits

--- 2019-12-17 main.tex
@@
 Aaboud:2017mpt, Aaboud:2017nhr}.  In this paper, we will focus on the discovery
-potential of the neutralinos and charginos at a 100 TeV $pp$ collider. {\bf
-Can not find Ref. 9}
+potential of the neutralinos and charginos at a 100 TeV $pp$ collider.
 
@@
 A 100 TeV $pp$ collider would open up an immense number of physics
-opportunities not afforded to the 14 TeV LHC. \st{including exploring the most
-interesting regions of the split SUSY parameter space}~\cite{Arkani-Hamed:2015vfh}.
+opportunities not afforded to the 14 TeV LHC~\cite{Arkani-Hamed:2015vfh}.
 % Status of 100 TeV planning
@@
 For the backgrounds, we allowed up to one additional jet in the final state, to
-approximate NLO QCD effects, and performed MLM matching with the \texttt{xqcut}
+approximate NLO QCD effects, and performed MLM matching\footnote{Although
+there are tools that support NLO generation \cite{Alwall:2014hca}, their NLO
+generation mode does not support specifying decay chains, which we require in
+order to generate enough MC events to be statistically representative of the
+backgrounds at a 100 TeV $pp$ collider.} with the \texttt{xqcut}
 parameter set to 40 GeV. The Higgsino pair production cross sections were
@@
 points, we require a minimum of three background events (at the MC level, i.e.
-unweighted) left over after cuts\footnote{\ap{This is inspired by the upper
+unweighted) left over after cuts\footnote{This is inspired by the upper
     one-sided limit for the mean of a Poisson variable given zero observed
@@
 that expected at a 100 TeV $pp$ collider with 3 ab$^{-1}$ is $\approx 0.2$ for
-$tt$, 0.05 for $tbW$, $0.46$ for $bbWW$}}. We can see that, after applying our
+$tt$, 0.05 for $tbW$, and $\approx0.46$ for $bbWW$.}. We can see that, after applying our
 cuts, $tbW$ remains as the dominant backgrounds, followed by $tt$.  The values
@@
 the generated events into training and test sets, with the training set
-comprising 75\% of signal events and 30\% of background events.  \Shufang{More details here -- Referee comment 9.} We used the
+comprised of 75\% of the generated signal events and 30\% of the generated
+background events. We require a lower portion of the background events for
+training, in order to maintain adequate MC statistics to calculate significance
+using the testing split, given the extremely large background cross sections at
+a 100 TeV $pp$ collider. All the events are unweighted. We used the
 \texttt{scikit-learn} package  \cite{Pedregosa2011} to implement our analysis.
 A boosted decision tree classifier was trained with 1000 weak learners and a
-learning rate of 0.025.
+learning rate of 0.025. The maximum tree depth is 3, and the minimum node
+size is 1.
 
@@
 increase.
-
-\st{For certain values of the
-cuts on kinematic variables or the score of the classifier, no events survived
-for one or more of the background components. To guard against overly optimistic
-estimates of the significance $S/\sqrt{B}$, we set a lower bound of 3 for the
-number of Monte Carlo (MC) events after cuts for each background component, corresponding to
-the 95\% confidence interval for a Poisson distribution.}\Shufang{SS: Is it 3
-MC events, or 3 weighted events after CS values used? Referee comment 10.}
-\Adarsh{I added a footnote about this - see footnote 5. I think we can remove
-this paragraph...}
 
